
---
title: Incorrect RCA lines
subtitle: NOAA summary
format: html
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)


if (!require(librarian,quietly = T)){
  install.packages('librarian')
}

librarian::shelf(
  here,
  readxl,
  tidyverse,
  lubridate,
  data.table,
  openxlsx,
  terra,
  leaflet,
  sf,
  htmltools,
  openxlsx,
  knitr,
  kableExtra,
  quiet = T
)

sf_use_s2(FALSE)
```

```{r, echo = FALSE, results = FALSE}
# Read in our lines from Cullen's methods
# Read in data using script (this helps keeping tidy the qmd)
source(here("RCA_data_exploration/scripts/generate_rca_lines.R"))
```

```{r, echo = FALSE, results = FALSE}
# Read lines from CalPoly, approved by NOAA
# Update isolines form CalPoly gdb
feature_class <- st_read(dsn = cal_poly_fp, layer = "Master_line_feature_source")
names(feature_class)

isolines <- feature_class %>% 
  filter(CoordFileName != "NA" & CoordFileName != "")

split_isolines <- split(isolines, isolines$CoordFileName)

# function to apply the transformation
transform_isolines <- function(df) {
  df %>%
    st_combine() %>%
    st_as_sf() %>%
    st_set_geometry("geometry") %>%
    mutate(
      boundary_type = "isobath",
      boundary_name = first(df$CoordFileName),
      area_name = "not_defined",
      land_ref = "bathymetry",
      .before = geometry
    )
}

# Apply the transformation to each split dataframe and combine the results
new_isolines <- map_dfr(split_isolines, transform_isolines)
```

```{r, echo = FALSE, results = FALSE}
# Initialize an empty dataframe to store results
lines_check_df <- data.frame(boundary_name = character(),
                             area_name = character(),
                             self_intersects = logical(),
                             point_coord = character(),
                             stringsAsFactors = FALSE)
# Empty list to store map objects
maps_list <- list() 
# Create an empty sf object to store self-intersecting lines
self_intersecting_lines_gpkg <- rbind()

for (i in unique(rca_lines_sf$boundary_name)) {
  # Filter lines by boundary name
  line_vec <- rca_lines_sf %>%
    filter(boundary_name == i)

  for (j in unique(line_vec$area_name)) {
    # Filter lines by boundary name
    line_unique_vec <- line_vec %>%
      filter(area_name == j)
    # Self-intersection evaluation
    ## Check each line for simplicity (i.e., it does not cross itself)
    self_intersects <- !st_is_simple(line_unique_vec)
    
    # Append the results to the dataframe only if self_intersects is TRUE
    if(self_intersects) {
      self_intersecting_lines_gpkg <- rbind(self_intersecting_lines_gpkg, line_unique_vec)
      # Find self-intersection point
      ## Extract nodes' coordinates from line
      line_coords <- st_coordinates(line_unique_vec)[,1:2]
      ## Create individual lines from the coordinates
      individual_lines <- vector("list", nrow(line_coords) - 1)
      for(k in 1:(nrow(line_coords) - 1)) {
        individual_lines[[k]] <- st_linestring(line_coords[k:(k+1), ])
      }
      ## Convert the list of lines into an sf object
      individual_lines_sf <- st_sfc(individual_lines, crs = st_crs(line_unique_vec))
      ## Find which individual lines cross
      crosses <- suppressMessages(st_crosses(individual_lines_sf))
      crossing_lines_indices <- which(sapply(crosses, length) > 0)
      ## Create sf object from those lines
      self_intersecting_lines <- individual_lines_sf[crossing_lines_indices] %>%
        st_as_sf()
      # Get intersection point coordinates
      line_intersection <- suppressMessages(st_intersection(self_intersecting_lines))
      points_only <- line_intersection[st_geometry_type(line_intersection) == "POINT", ]
      intersection_coord <- st_coordinates(points_only)
      
      ## Check if intersection_coord contains multiple rows and store all
      if (nrow(intersection_coord) > 1) {
        # Store multiple sets of coordinates in separate brackets
        lon_lat_pairs <- apply(intersection_coord, 1, function(row) {
          paste0("(", row[1], " ", row[2], ")")
        })
        # Combine all lon_lat_pairs into a single string separated by commas
        lon_lat <- paste(lon_lat_pairs, collapse = ",")
      } else {
        # Single set of coordinates
        lon_lat <- paste("(", intersection_coord[1, 1], " ", intersection_coord[1, 2], ")", sep = "")
      }
      
      lines_check_df <- rbind(lines_check_df,
                              data.frame(
                                boundary_name = i,
                                area_name = j,
                                self_intersects = self_intersects,
                                point_coord = lon_lat
                                ))
      
      # Represent line in a map
      ## Calculate bounds for the self-intersecting lines to set map view so the map zooms to where the intersection is.
      if(length(self_intersecting_lines) > 0) {
        bounds <- st_bbox(self_intersecting_lines)
        map_bounds <- matrix(c(bounds$xmin, bounds$ymin, bounds$xmax, bounds$ymax), nrow = 2)
      } else {
        bounds <- st_bbox(line_unique_vec)
        map_bounds <- matrix(c(bounds$xmin, bounds$ymin, bounds$xmax, bounds$ymax), nrow = 2)
      }
      ## Set title to indicate with RCA is represented
      map_title <- unique(line_unique_vec$boundary_name)[1]
      ## Add equivalent CalPoly RCA line
      line_calpoly_vec <- new_isolines %>%
        filter(boundary_name == i)
      ## Create the map
      map_object <- leaflet() %>%
        addProviderTiles(providers$OpenStreetMap) %>%
        addPolylines(data = line_unique_vec, color = "blue", group = "emLab RCA line") %>%
        addPolylines(data = line_calpoly_vec, color = "orange", group = "NOAA RCA line") %>%
        addMarkers(data=points_only, group = "Intersections") %>% 
        fitBounds(lng1 = map_bounds[1,1], lat1 = map_bounds[2,1], 
                  lng2 = map_bounds[1,2], lat2 = map_bounds[2,2]) %>%
        addLegend(position = "topright", 
                  title = map_title, 
                  opacity = 0, 
                  labels = "", 
                  colors = "transparent") %>% 
        addLayersControl(overlayGroups = c("Intersections", "emLab RCA line", "NOAA RCA line"))
      
      print(map_object)
      # Store map object in the list with map_title as the key
      maps_list[[map_title]] <- map_object
      
      st_write(self_intersecting_lines_gpkg %>% 
                 mutate(self_intersects = "TRUE")
                 , "self_intersecting_lines.gpkg", driver = "GPKG",append = FALSE)
    }
  }
}
```

## Self-intersections (points out of order)

The table below includes all RCA lines based on the csv files with coordinates that contain at least one point that is out of order. These result in self-intersecting lines that in turn produce incorrect shapes. Scroll down to see all the lines.

```{r, echo = FALSE}
# Display the resulting dataframe
kable(lines_check_df) %>%
  kable_styling("striped") %>% scroll_box(width = "100%",height = "400px")
```

The maps below show the lines based on the csv files with self-intersections in blue. The pins represent the locations where the intersections occur. These are compared with lines NOAA lines (extracted from `Master_line_feature_source`), which are displayed in orange. Note that some of the NOAA lines also contain self-intersections.

```{r echo=FALSE}
html <- list()
for (i in 1:length(maps_list)) {
  html <- c(html, 
            list(h4(paste0("Map corresponding to RCA line ", names(maps_list)[i])),
                 maps_list[i]  
                 )
            )
}
tagList(html)

```


## Points inland

Here we determine whether some of the nodes are overlap with land. For this process, we used shoreline intersection as a proxy. Therefore, a selected line does not necessarily mean it has a point on land, and visual inspection is required. Further, lines whose ending points were situated on land were discarded since line endings near the shore were seen to be relatively close to the coastline and should not substantially affect the definition of RCAs. Instead, they may be caused by a problem of shoreline resolution. The shoreline that we use here is based on the shoreline feature shared by NOAA, which the EEZ boundaries removed.

```{r, echo = FALSE, results = FALSE}
coastline <- st_read( here(data_path,"/spatial_ref_files/mainland_shore.geojson")) |>
  sf::st_as_sf() |>
  tidyr::replace_na(replace = list(Name = "Shoreline")) |>
  dplyr::group_by(AreaType) |>
  dplyr::summarize(geometry = sf::st_union(geometry)) |>
  dplyr::mutate(
    boundary_type = "isobath",
    boundary_name = "shoreline",
    area_name = "shoreline",
    land_ref = ifelse(AreaType == "islands", "islands", "mainland")) |>
  dplyr::select(boundary_type, boundary_name, area_name, land_ref, geometry)
```

```{r, echo = FALSE, results = FALSE}
# Initialize an empty dataframe to store results
lines_check_df2 <- data.frame(boundary_name = character(),
                              area_name = character(),
                              land_point = logical(),
                              lon_lat =character(),
                              stringsAsFactors = FALSE
                              )
maps_list2 <- list() 

for (i in unique(rca_lines_sf$boundary_name)) {
  # Filter lines by boundary name
  line_vec <- rca_lines_sf %>%
    filter(boundary_name == i)

  for (j in unique(line_vec$area_name)) {
    # Filter lines by boundary name
    line_unique_vec <- line_vec %>%
      filter(area_name == j)
    # Shoreline evaluation
    ## Check for intersections between the line and the shoreline
    intersections_with_shoreline <- suppressMessages(st_intersects(line_unique_vec, coastline))
    any_intersections_with_shoreline <- any(lengths(intersections_with_shoreline)>0)
    # Append the results to the dataframe
    if(any_intersections_with_shoreline) {
      
      # Exclude lines where intersection only generates one point (i.e., the point inland is in the ends line which does not substantially affects the RCA definition)
      line_intersection <- st_intersection(line_unique_vec,coastline)
      coords <- st_coordinates(line_intersection)[,1:2]
      points_sf <- NULL
      if (!is.null(dim(coords))) {
        for(k in 1:nrow(coords)) {
        point_sf <- st_point(as.numeric(coords[k,])) %>% st_sfc() %>% st_sf()
        points_sf <- bind_rows(points_sf, point_sf)
        }
        
        intersection_coord <- st_coordinates(points_sf)
      
        ## Check if intersection_coord contains multiple rows and store all
        if (nrow(intersection_coord) > 1) {
          # Store multiple sets of coordinates in separate brackets
          lon_lat_pairs <- apply(intersection_coord, 1, function(row) {
            paste0("(", row[1], " ", row[2], ")")
          })
          # Combine all lon_lat_pairs into a single string separated by commas
          lon_lat <- paste(lon_lat_pairs, collapse = ",")
        } else {
          # Single set of coordinates
          lon_lat <- paste("(", intersection_coord[1, 1], " ", intersection_coord[1, 2], ")", sep = "")
        }
  
        lines_check_df2 <- rbind(lines_check_df2,
                                data.frame(
                                boundary_name = i,
                                area_name = j,
                                land_point = any_intersections_with_shoreline,
                                lon_lat = lon_lat)
                                )
        
        # Represent line in a map
        ## Calculate bounds for the self-intersecting lines to set map view so the map zooms to where the intersection is.
        if(length(points_sf) > 0) {
          bounds <- st_bbox(points_sf)
          map_bounds <- matrix(c(bounds$xmin, bounds$ymin, bounds$xmax, bounds$ymax), nrow = 2)
        } else {
          bounds <- st_bbox(line_unique_vec)
          map_bounds <- matrix(c(bounds$xmin, bounds$ymin, bounds$xmax, bounds$ymax), nrow = 2)
        }
        ## Set title to indicate with RCA is represented
        map_title <- unique(line_unique_vec$boundary_name)[1]
        ## Add equivalent CalPoly RCA line
        line_calpoly_vec <- new_isolines %>%
          filter(boundary_name == i)
        ## Create the map
        map_object <- leaflet() %>%
          addProviderTiles(providers$OpenStreetMap) %>%
          addPolylines(data = line_unique_vec, color = "blue", group = "emLab RCA line") %>%
          addPolylines(data = line_calpoly_vec, color = "orange", group = "NOAA RCA line") %>%
          fitBounds(lng1 = map_bounds[1,1], lat1 = map_bounds[2,1], 
                    lng2 = map_bounds[1,2], lat2 = map_bounds[2,2]) %>%
          addLegend(position = "topright", 
                    title = map_title, 
                    opacity = 0, 
                    labels = "", 
                    colors = "transparent") %>% 
          addLayersControl(overlayGroups = c("Intersections", "emLab RCA line", "NOAA RCA line"))
        
        print(map_object)
        # Store map object in the list with map_title as the key
        maps_list2[[map_title]] <- map_object
      }
   
      
    }
  }
}

# Display the resulting dataframe
head(lines_check_df2)
```

As seen in the table and maps below, the only line affected by points located on land is `60fm_010104.csv`. Zooming out reveals that a node is located north of Ventura. As for `75fm_012703.csv`, the script detected it only due to the shoreline intersection proxy, as the incorrect shape previously identified crosses land areas.

```{r, echo = FALSE}
# Display the resulting dataframe
kable(lines_check_df2) %>%
  kable_styling("striped") %>% scroll_box(width = "100%",height = "400px")
```

```{r, echo = FALSE}
html <- list()
for (i in 1:length(maps_list2)) {
  html <- c(html, 
            list(h4(paste0("Map corresponding to RCA line ", names(maps_list2)[i])),
                 maps_list2[i]  
                 )
            )
}
tagList(html)
```







