---
format: html
editor_options: 
  chunk_output_type: console
---

# New approach for RCA polygon creation

## Setup

```{r}
if (!require(librarian,quietly = T)){
  install.packages('librarian')
}

librarian::shelf(
  here,
  # plotly,
  readxl,
  tidyverse,
  lubridate,
  data.table,
  openxlsx,
  terra,
  leaflet,
  sf,
  openxlsx,
  rnaturalearth, 
  rnaturalearthdata,
  # foreach,
  # doParallel,
  iterators,
  quiet = T
)

sf_use_s2(FALSE)
```

```{r}
# Read in data using script (this helps keeping tidy the qmd)
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v3.R"))
source(here("RCA_data_exploration/scripts/generate_rca_objects.R"))
```

# Testing for constant longitude lines

```{r}
# Update isolines form CalPoly gdb
feature_class <- st_read(dsn = cal_poly_fp, layer = "Master_line_feature_source")
isolines <- feature_class %>% 
  filter(CoordFileName != "NA" & CoordFileName != "")

split_isolines <- split(isolines, isolines$CoordFileName)

# function to apply the transformation
transform_isolines <- function(df) {
  df %>%
    st_combine() %>%
    st_as_sf() %>%
    st_set_geometry("geometry") %>%
    mutate(
      boundary_type = "isobath",
      boundary_name = first(df$CoordFileName),
      area_name = "not_defined",
      land_ref = "bathymetry",
      .before = geometry
    )
}

# Apply the transformation to each split dataframe and combine the results
new_isolines <- map_dfr(split_isolines, transform_isolines)

isolines_testing <- new_isolines %>% 
  filter(boundary_name == "150fm_012703.csv")

selected_longitude_lines <- rbind(isolines_testing, coastline)
```

```{r}
select_random_lat_boundaries <- function(data_frame) {
  # Extract unique boundary names
  unique_boundaries <- unique(data_frame$boundary_name)
  # Ensure that there are at least 2 unique boundaries to select from
  if(length(unique_boundaries) < 2) {
    stop("Not enough unique boundary names to select two random, non-equal values.")
  }
  # Randomly select two non-equal boundary names
  selected_boundaries <- sample(unique_boundaries, 2)
  # Filter rows that match the randomly selected boundary names
  selected_rows <- data_frame %>% 
    filter(boundary_name %in% selected_boundaries)
  return(selected_rows)
}

selected_latitude_lines <- select_random_lat_boundaries(n_s_boundaries_sf)


testing_poly <- rca_lines_to_polygons_v3(selected_longitude_lines,selected_latitude_lines)
```


1. Selecting inner polygons based on area can lead to issues in regions where land areas exceed water areas, particularly when the shoreline acts as a boundary. This situation is notable in Oregon, where large estuaries can cause the polygon generation process to incorrectly focus on land areas. For instance, for the file "150fm_012703.csv," the latitude limits of "43 20.83' N" and "46 16.00' N" exemplify this issue. Additional examples include the latitudinal ranges "42 40.50' N" to "45 46.00' N".

2. The execution of the random polygon generation script show further anomalies in shapes. However, these are likely due to the absence of a longitudinal lines at certain latitudes.

# Testing with all random lines

```{r}
select_random_lon_boundaries <- function(data_frame) {
  # Extract unique boundary names
  unique_boundaries <- unique(data_frame$boundary_name)
  # Ensure that there are at least 2 unique boundaries to select from
  if(length(unique_boundaries) < 2) {
    stop("Not enough unique boundary names to select two random, non-equal values.")
  }
  # Randomly select two non-equal boundary names
  selected_boundaries <- sample(unique_boundaries, 2)
  # Filter rows that match the randomly selected boundary names
  selected_rows <- data_frame %>% 
    filter(boundary_name %in% selected_boundaries)
  return(selected_rows)
}

selected_longitude_lines <- select_random_lon_boundaries(new_isolines)
selected_latitude_lines <- select_random_lat_boundaries(n_s_boundaries_sf)


testing_poly <- rca_lines_to_polygons_v3(selected_longitude_lines,selected_latitude_lines)
```

boundary_type    boundary_name
1       isobath 100fm_030104.csv
2       isobath 150fm_010105.csv

U.S. EEZ Boundary South U.S. EEZ Boundary South 
36 00.00' N             36 00.00' N                       

For the above was detected that the islands are not clipped out if shoreline is not part of the boundary. Update that.


## Run for a subset of RCA areas

```{r}
head(polygon_df_orig)
test_sample <- polygon_df_orig[1:5,]

rca_lines_to_polygons_v3(selected_longitude_lines,selected_latitude_lines)



```

create instructions df based on cullens code

```{r}
selected_longitude_lines

## Create clean data frame of polygon metadata
polygon_instructions_df <- polygon_df_orig  %>% 
  dplyr::select(-completed)  %>% 
  dplyr::filter(shoreward_boundary != "N/A")  %>% 
  dplyr::mutate(
    shoreward_boundary = gsub("^0 fm \\(([^)]+)\\)$", "\\1", shoreward_boundary),
    southern_boundary = ifelse(southern_boundary == "U.S. EEZ Boundary", 
                               "U.S. EEZ Boundary South", 
                               southern_boundary),
    northern_boundary = ifelse(northern_boundary == "U.S. EEZ Boundary", 
                               "U.S. EEZ Boundary North", 
                               northern_boundary)) %>% 
  rename( lat_boundary1 = northern_boundary,
          lat_boundary2 = southern_boundary,
          lon_boundary1 = shoreward_boundary,
          lon_boundary2 = seaward_boundary)
  

```


```{r}
unique(polygon_instructions_df$shoreward_boundary)
unique(polygon_instructions_df$seaward_boundary)
unique(polygon_instructions_df$southern_boundary)
unique(polygon_instructions_df$northern_boundary)
```

```{r}
head(new_isolines)
head(coastline)

coastline <- st_transform(coastline, st_crs(new_isolines))
n_s_boundaries_sf <- st_transform(n_s_boundaries_sf, st_crs(new_isolines))


lon_boundary <- coastline %>% 
  mutate(boundary_name = ifelse(boundary_name == "shoreline",
                                "Shoreline",
                                boundary_name)) %>% 
  rbind(new_isolines)
  
lat_boundary <- n_s_boundaries_sf
```

```{r}
head(polygon_instructions_df)
intructions_sample <- polygon_instructions_df[1:5,]

```

```{r}
# Initialize list to store results
results <- list()

i=1
for (i in 1:nrow(intructions_sample)) {
    # For each row in intructions_sample, extract the boundary names
    lat_boundary1_name <- intructions_sample$lat_boundary1[i]
    lat_boundary2_name <- intructions_sample$lat_boundary2[i]

    lon_boundary1_name <- intructions_sample$lon_boundary1[i]
    lon_boundary2_name <- intructions_sample$lon_boundary2[i] 

    # Select latitude lines
    selected_latitude_lines <- lat_boundary[lat_boundary$boundary_name == lat_boundary1_name, ] %>% 
      rbind(lat_boundary[lat_boundary$boundary_name == lat_boundary2_name, ])
    
    # Select longitude lines
    selected_longitude_lines <- lon_boundary[lon_boundary$boundary_name == lon_boundary1_name, ] %>% 
      rbind(lon_boundary[lon_boundary$boundary_name == lon_boundary2_name, ])
    
    leaflet() %>%
      addTiles() %>%
      addPolylines(data = selected_longitude_lines, color = "red", weight=2) %>% 
      addPolylines(data = selected_latitude_lines, color = "blue", weight=2)
    
    # Process the selected lines to create polygons
    result <- rca_lines_to_polygons_v3(selected_longitude_lines, selected_latitude_lines)
    
    # Combine polygons into a multipolygons and assign the instructions df variable levels
    combined_sf <- result %>% 
      st_combine() %>% 
      st_sf() %>% 
      cbind(intructions_sample[i,])
    
    # Store each result in the results list
    results[[i]] <- combined_sf
}

```

```{r}

```

