---
format: html
editor_options: 
  chunk_output_type: console
---

## Setup

```{r}
if (!require(librarian,quietly = T)){
  install.packages('librarian')
}

librarian::shelf(
  here,
  # plotly,
  readxl,
  tidyverse,
  lubridate,
  data.table,
  openxlsx,
  terra,
  leaflet,
  sf,
  openxlsx,
  rnaturalearth, 
  rnaturalearthdata,
  # foreach,
  # doParallel,
  iterators,
  quiet = T
)

sf_use_s2(FALSE)
```

## Getting lines from Cullen's methods

### Read in data

```{r}
## directories
data_path <- here::here('rca-database/Ruttenberg et al collaboration')
coord_path <- here::here(data_path, 'RCA_Coordinate_CSV_Files_cleaned_2002_21')

## files
rca_data_fn  <- 'Historical_trawl_RCA_2002-2021_CEW_LC_01Oct2021.xlsx'
cal_poly_fn  <- 'RCA_Mapping_Project_4Cal_Poly.gdb'
eez_north_fn <- 'revised-sp/north-south-bounds/eez_north.shp'
eez_south_fn <- 'revised-sp/north-south-bounds/eez_south.shp'

## specify inputs
rca_crs <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"

mollweide <- "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs"
```

```{r}
## Regulatory boundary points
rca_legis_points_df <- coord_path |> 
  list.files(full.names = TRUE) |> 
  readr::read_csv(
    locale = locale(encoding = "ISO-8859-1"), 
    id = "boundary_name", 
    show_col_types=FALSE)  |> 
  dplyr::mutate(
    area_name = stringr::str_replace_all(area_name, "-C", "- C"),
    boundary_name = basename(boundary_name),
    boundary_type = "isobath", 
    land_ref = case_when(
      str_detect(area_name, "Coastwide") ~ "mainland",
      str_detect(area_name, "Washington") ~ "mainland",
      # str_detect(area_name, "Cordell") ~ "mainland",
      str_detect(area_name, "DBCA") ~ "mainland",
      str_detect(area_name, "Petrale") ~ "mainland",
      TRUE ~ "islands"
    )) |> 
  dplyr::rename(lat = lat_dd, lon = lon_dd) |> 
  dplyr::filter(area_name != "150-fm (274-m) Contour - Seamounts - Lasuen Knoll") 

## Create line strings for each isobath and area_name
rca_lines_sf <- rca_legis_points_df |> 
  sf::st_as_sf(coords = c("lon", "lat"), crs = 4326)  |>  
  dplyr::group_by(boundary_type, boundary_name, area_name, land_ref) |>
  dplyr::arrange(id_area) |> 
  dplyr::summarize(geometry = st_combine(geometry)) |> 
  sf::st_cast("LINESTRING") 

rca_lines_sf |> 
  tibble::as_tibble() |>
  dplyr::select(boundary_name, area_name, land_ref) |> 
  readr::write_csv(here::here(data_path, "rca_lines_names.csv"))

rca_lines_vec <- rca_lines_sf |> 
  terra::vect()

max_extent <- terra::ext(rca_lines_vec)
xmin <- terra::xmin(max_extent)
xmax <- terra::xmax(max_extent)
ymin <- terra::ymin(max_extent)
ymax <- terra::ymax(max_extent)


## Load north america shapefile for plotting
north_america <- rnaturalearth::ne_countries(scale = "medium", returnclass = "sf") |> 
  dplyr::filter(admin %in% c("United States of America", "Canada", "Mexico"))
```

```{r}
cal_poly_fp <- here::here(data_path, cal_poly_fn)
cal_poly_layers <- terra::vector_layers(cal_poly_fp)

ca_poly_rca_vect_list <- purrr::map(
  cal_poly_layers,
  ~terra::vect(cal_poly_fp, layer = .),
  .progress=TRUE
)

cal_poly_layers <- stringr::str_remove_all(cal_poly_layers, "rca")
cal_poly_layers <- stringr::str_remove_all(cal_poly_layers, "_line")

ca_poly_rca_vect_df <- tibble::tibble(
  layer_name = cal_poly_layers,
  vect_info = ca_poly_rca_vect_list
) |> 
  dplyr::filter(layer_name != "Landmark_boundary_geocoordinates_table")

shoreline_eez <- ca_poly_rca_vect_df |> 
  dplyr::filter(layer_name == "EEZ_and_shoreline_Geo") |> 
  dplyr::pull(vect_info)

shoreline <- shoreline_eez[[1]] |> 
  sf::st_as_sf() |>
  tidyr::replace_na(replace = list(Name = "Shoreline")) |> 
  dplyr::group_by(AreaType) |>
  dplyr::summarize(geometry = sf::st_union(geometry)) |> 
  dplyr::mutate(
    boundary_type = "isobath",
    boundary_name = "Shoreline",
    area_name = "Shoreline",
    land_ref = ifelse(AreaType == "water", "mainland", "islands")) |> 
  dplyr::select(boundary_type, boundary_name, area_name, land_ref, geometry)
```


### Exploring lines

One of the potential causes for the polygons not drawing properly is defects in line geometries. As annotated in the sheet "rca_line_checking," it appears that the most common problems are the existence of points on land and the points being out of order. The first issue is problematic in itself because RCA must be in territorial waters. The second can cause self-intersections, leading to errors in subsequent polygon transformations.

Below, we explore individual lines based on the CSV file name to see if these issues can be detected programmatically.

```{r}
# Assuming `rca_lines_sf` is your sf object and you're interested in plotting the first geometry
plot_rca_line <- function(rca_lines_sf) {
  # Extracting the first geometry (seems you've done this)
  geom <- rca_lines_sf$geometry
  
  # Plot using ggplot2
  ggplot() +
    geom_sf(data = geom) +
    ggtitle("Plot of MULTIPOINT Geometry") +
    theme_minimal()
}
```

From the JPG generated by Cullen's script, one the most visually noticeable error occurred for "60fm_010104.csv," where a Channel Island boundary point appears in a mainland area.

```{r}
# Filter observations where boundary_name is "60fm_010104.csv"
filtered_rca_lines_sf <- rca_lines_sf %>%
  filter(boundary_name == "60fm_010104.csv")
  # filter(boundary_name == "75fm_070104.csv")
  # filter(boundary_name == "200fm_petrale_010107.csv")

plot_rca_line(filtered_rca_lines_sf)
```

First, let's evaluate if there are intersecting lines among all the lines related to this specific sf. Presumably, there will be since an island point is inland.

```{r}
check_line_intersections <- function(filtered_rca_lines_sf) {
  # Compute intersections
  intersections <- st_intersects(filtered_rca_lines_sf)
  # Check for any intersections
  any_intersections <- any(lengths(intersections) > 1)
  # Print result
  if (any_intersections) {
    cat("There are intersecting lines.\n")
  } else {
    cat("There are no intersecting lines.\n")
  }
}

check_line_intersections(filtered_rca_lines_sf)
```

Now lets see if actually there is a line intersecting the shoreline.



```{r}
# Updated shoreline file without the EEZ
coastline <- st_read( here("rca-database/spatial_ref_files/mainland_shore.geojson")) |>
  sf::st_as_sf() |>
  tidyr::replace_na(replace = list(Name = "Shoreline")) |>
  dplyr::group_by(AreaType) |>
  dplyr::summarize(geometry = sf::st_union(geometry)) |>
  dplyr::mutate(
    boundary_type = "isobath",
    boundary_name = "shoreline",
    area_name = "shoreline",
    land_ref = ifelse(AreaType == "islands", "islands", "mainland")) |>
  dplyr::select(boundary_type, boundary_name, area_name, land_ref, geometry)
```

```{r}
# UPDATE: no EEZ but mainline shore only
check_shoreline_intersections <- function(filtered_rca_lines_sf) {
  # Check for intersections between the lines and the shoreline
  intersections_with_shoreline <- st_intersects(filtered_rca_lines_sf, coastline)
  # Check for any intersections
  any_intersections_with_shoreline <- any(lengths(intersections_with_shoreline) > 0)
  # Print result
  if (any_intersections_with_shoreline) {
    cat("There are intersections between the lines and the shoreline.\n")
  } else {
    cat("There are no intersections between the lines and the shoreline.\n")
  }
}

check_shoreline_intersections(filtered_rca_lines_sf)
```

*Note: It's important to be aware that this method assesses whether a line crosses the shoreline. This can result from an existing point inland, but also from incorrect geometry caused by self-intersections, which create segments intersecting with the shoreline.*

Let's use another approach, this time evaluating whether the nodes are outside the expected areas.

```{r}
# Get a polygon for the islands
islands_poly <-  shoreline[1,] %>% 
  st_polygonize() %>% 
  st_collection_extract("POLYGON")

# Get a polygon for the eez
eez_poly <-  shoreline[2,] %>% 
  st_polygonize() %>% 
  st_collection_extract("POLYGON")

# Get the points for a specific boundary_name
filtered_rca_points_sf <- rca_legis_points_df %>%
  filter(boundary_name == "60fm_010104.csv") %>% 
  sf::st_as_sf(coords = c("lon", "lat"), crs = 4326)

if (st_crs(eez_poly) != st_crs(islands_poly)) {
  islands_poly <- st_transform(islands_poly, st_crs(eez_poly))
}
if (st_crs(eez_poly) != st_crs(filtered_rca_points_sf)) {
  filtered_rca_points_sf <- st_transform(filtered_rca_points_sf, st_crs(eez_poly))
}


# Define a function to analyze points in relation to the polygon
check_wrong_points <- function(points_sf, eez, islands) {
  
  points_within <- st_intersects(filtered_rca_points_sf, eez_poly)
  # To get a logical vector indicating whether each point is inside the polygon
  is_within <- lengths(points_within) > 0
  # To see how many points are inside
  n_points_in_land <-sum(!is_within)
  # You can also create a subset of points that are inside the polygon if needed
  points_in_land <- filtered_rca_points_sf[!is_within, ]
  
  
  points_within <- st_intersects(filtered_rca_points_sf, islands_poly)
  # To get a logical vector indicating whether each point is inside the polygon
  is_within <- lengths(points_within) > 0
  # To see how many points are inside
  n_points_in_islands <- sum(is_within)
  # You can also create a subset of points that are inside the polygon if needed
  points_in_islands <- filtered_rca_points_sf[is_within, ]
  
  # Return a list with the counts and subsets
  return(list(
    n_points_in_land = n_points_in_land,
    points_in_land = points_in_land,
    n_points_in_islands = n_points_in_islands,
    points_in_islands = points_in_islands
  ))
}

wrong_points <- check_wrong_points(filtered_rca_points_sf, eez_poly, islands_eez_poly)
wrong_points
```

We can see that there are two points that are outside the EEZ, but only one is inland. The other is at the limit of the EEZ's northern border, which doesn't necessarily mean it is incorrectly located. In fact, if we zoom in on the leaflet map below, we see that it is almost inside the EEZ, probably due to slight changes in the spatial transformation of the northern border line. We will have to consider this when assessing the rest of the lines.

```{r}
leaflet() %>%
  addTiles() %>%
  addPolygons(data = eez_poly, color = "blue", weight = 1, fillColor = "blue", fillOpacity = 0.1) %>% 
  addCircleMarkers(data = wrong_points$points_in_land, color = "red", radius = 3, fillOpacity = 1.0, stroke = FALSE)
```

Finally, let's explore whether self-intersections may occur, potentially creating additional problems.

```{r}
check_self_intersections <- function(filtered_rca_lines_sf) {
  # Check each line for simplicity (i.e., it does not cross itself)
  is_simple <- st_is_simple(filtered_rca_lines_sf)
  # Identify lines that are not simple (i.e., have self-intersections)
  self_intersecting_lines <- filtered_rca_lines_sf[!is_simple, ]
  # Check if there are any self-intersecting lines and print result
  if (nrow(self_intersecting_lines) > 0) {
    cat("There are self-intersecting lines.\n")
  } else {
    cat("There are no self-intersecting lines.\n")
  }
}

check_self_intersections(filtered_rca_lines_sf)
```

In this case, we observe that there are no self-intersections, so the issue with this line arises only from a point being located inland. 

Let's explore another example where self-intersection actually occurs.

```{r}
# Filter observations where boundary_name is "60fm_010104.csv"
filtered_rca_lines_sf <- rca_lines_sf %>%
  filter(boundary_name == "200fm_petrale_010107.csv")

check_self_intersections(filtered_rca_lines_sf)
```

In this case, we detect self-intersection, and upon checking the associated jpg, it becomes evident that it's occurring in front of Point Conception.

With this in mind, let's create a loop to run the evaluation for all lines and automate the process. We will store the results in a dataframe containing the boundary name, the area names, and variables displaying information on whether a line self-intersects or intersects with the shoreline.

```{r}
# ## FIRST ATTEMPT ONLY CONSIDERED BOUNDARY NAMES
# # Initialize dataframe
# lines_check_df <- data.frame(boundary_name = character(),
#                                    self_intersects = logical(),
#                                    land_point = logical(),
#                                    stringsAsFactors = FALSE)
# 
# for (i in unique(rca_lines_sf$boundary_name)) {
#   # Filter lines by boundary name
#   line_vec <- rca_lines_sf %>% 
#     filter(boundary_name == i)
#   # Self-intersection evaluation
#   is_simple <- st_is_simple(line_vec) 
#   self_intersects <- any(!is_simple) 
#   # Shoreline evaluation
#   intersections_with_shoreline <- st_intersects(line_vec, shoreline)
#   any_intersections_with_shoreline <- any(lengths(intersections_with_shoreline)>0)
#   lines_check_df <- rbind(lines_check_df, 
#                                 data.frame(
#                                   boundary_name = i, 
#                                   self_intersects = self_intersects,
#                                   land_point = any_intersections_with_shoreline))
# }
```

The loop below evaluates by line intersection instead of point based.

```{r}
# Initialize an empty dataframe to store results
lines_check_df <- data.frame(boundary_name = character(),
                                   area_name = character(),
                                   self_intersects = logical(),
                                   land_point = logical(),
                                   stringsAsFactors = FALSE)

for (i in unique(rca_lines_sf$boundary_name)) {
  # Filter lines by boundary name
  line_vec <- rca_lines_sf %>%
    filter(boundary_name == i)

  for (j in unique(line_vec$area_name)) {
    # Filter lines by boundary name
    line_unique_vec <- line_vec %>%
      filter(area_name == j)
    # Self-intersection evaluation
    ## Check each line for simplicity (i.e., it does not cross itself)
    self_intersects <- !st_is_simple(line_unique_vec)
    # Shoreline evaluation
    ## Check for intersections between the line and the shoreline
    intersections_with_shoreline <- suppressMessages(st_intersects(line_unique_vec, coastline))
    any_intersections_with_shoreline <- any(lengths(intersections_with_shoreline)>0)
    # Append the results to the dataframe
    lines_check_df <- rbind(lines_check_df,
                            data.frame(
                              boundary_name = i,
                              area_name = j,
                              self_intersects = self_intersects,
                              land_point = any_intersections_with_shoreline))
  }
}

# Display the resulting dataframe
head(lines_check_df)
```

The loop below evaluates based on points location.

```{r}
# Initialize an empty dataframe to store results
lines_check_df <- data.frame(boundary_name = character(),
                                   area_name = character(),
                                   self_intersects = logical(),
                                   land_points = logical(),
                                   stringsAsFactors = FALSE)

for (i in unique(rca_lines_sf$boundary_name)) {
  # Filter lines by boundary name
  line_vec <- rca_lines_sf %>% 
    filter(boundary_name == i)
  
  point_vec <- rca_legis_points_df %>%
    filter(boundary_name == i) %>% 
    sf::st_as_sf(coords = c("lon", "lat"), crs = 4326)
  
  for (j in unique(line_vec$area_name)) {
    # Filter lines by boundary name
    line_unique_vec <- line_vec %>% 
      filter(area_name == j)
    
    point_unique_vec <- point_vec %>% 
      filter(area_name == j)
    
    # Self-intersection evaluation
    ## Check each line for simplicity (i.e., it does not cross itself)
    self_intersects <- !st_is_simple(line_unique_vec)
    
    # Inland points evaluation
    ## Mainland
    points_within <- suppressMessages(st_intersects(point_unique_vec, eez_poly))
    is_within <- lengths(points_within) > 0
    n_points_in_land <-sum(!is_within)
    ## Islands
    points_within <- suppressMessages(st_intersects(point_unique_vec, islands_poly))
    is_within <- lengths(points_within) > 0
    n_points_in_islands <- sum(is_within)
    ## Sum
    wrong_points <- n_points_in_land + n_points_in_islands

    # Append the results to the dataframe
    lines_check_df <- rbind(lines_check_df,
                            data.frame(
                              boundary_name = i, 
                              area_name = j,
                              self_intersects = self_intersects,
                              land_points = wrong_points))
  }
}

# Display the resulting dataframe
head(lines_check_df)
```

There are `r sum(lines_check_df['land_points'] | lines_check_df['self_intersects'])` lines with errors.

Store the resulting dataframe into a formatted xlsx file.

```{r}
# SAVE intersection based approach
wb <- createWorkbook() # Create a new workbook
addWorksheet(wb, "Data") # Add a worksheet to the workbook
writeData(wb, "Data", lines_check_df) # Write your dataframe to the worksheet

# Define red font style
redFontStyle <- createStyle(fontColour = "#FF0000")

# Conditional formatting for 'land_points' or 'self_intersects' being TRUE
conditionalFormatting(wb, "Data", cols = 1:ncol(lines_check_df), rows = 2:(nrow(lines_check_df) + 1), rule = "ISNUMBER(SEARCH(\"TRUE\", INDIRECT(ADDRESS(ROW(),COLUMN()))))", style = redFontStyle)

# Save the workbook
saveWorkbook(wb, "rca-database/lines_check_df.xlsx", overwrite = TRUE)
```


```{r}
# SAVE point based approach
wb <- createWorkbook() # Create a new workbook
addWorksheet(wb, "Data") # Add a worksheet to the workbook
writeData(wb, "Data", lines_check_df) # Write your dataframe to the worksheet

# Color in red those observations representing conflicted lines
nrows <- nrow(lines_check_df)
redFontStyle <- createStyle(fontColour = "#FF0000")
# Apply conditional formatting
for (i in 1:nrows) {
  if (lines_check_df$land_points[i] || lines_check_df$self_intersects[i]) {
    # Apply red font style to the entire row
    addStyle(wb, "Data", style = redFontStyle, rows = i + 1, cols = 1:ncol(lines_check_df), gridExpand = TRUE)
  }
}

# Save the workbook
saveWorkbook(wb, "rca-database/lines_check_df.xlsx", overwrite = TRUE)
```


As evident from the generated XLSX file, there appear to be more geometries with errors than those included in the "rca_line_checking" sheet. This may explain the unexpected issues that could be causing mistakes in polygon generation. Below, we explore these identified incorrect geometries and discuss why they were not easily detected with the naked eye.

An example of this is the "75fm_070104.csv" file, which, upon inspection of the related JPG, does not seem to present any issues.

```{r}
# Filter observations where boundary_name is "60fm_010104.csv"
filtered_rca_lines_sf <- rca_lines_sf %>%
  filter(boundary_name == "75fm_070104.csv")

plot_rca_line(filtered_rca_lines_sf)
```

Let's run the individual functions to check for points inland and self-intersection.

```{r}
check_shoreline_intersections(filtered_rca_lines_sf)
check_self_intersections(filtered_rca_lines_sf)

is_simple <- st_is_simple(filtered_rca_lines_sf)
filtered_rca_lines_sf[!is_simple, ]$area_name
```

From this analysis, it appears that the lines are self-intersecting, particularly the one related to Santa Catalina Island.

To further evaluate where the self-intersection is occurring, we can save the data as a shapefile and conduct the examination in QGIS, utilizing the "Check Geometries" plugin. Save the file and proceed to QGIS for the exploration.

```{r}
st_write(filtered_rca_lines_sf, here("rca-database/line_shapefile/line_shapefile.shp"))
```

The intersections seem to occur at the western vertex of the shape surrounding the island, where two nodes force that intersection.

## Read in data for polygon generation

```{r}
north_eez <- here::here(data_path, eez_north_fn) |> 
  sf::read_sf() |>
  dplyr::mutate(
    boundary_type = 'latitude',
    boundary_name = 'U.S. EEZ Boundary North',
    area_name = 'U.S. EEZ Boundary North') 

south_eez <- here::here(data_path, eez_south_fn) |> 
  sf::read_sf() |>
  dplyr::mutate(
    boundary_type = 'latitude',
    boundary_name = 'U.S. EEZ Boundary South',
    area_name = 'U.S. EEZ Boundary South') 

eez_sf <- rbind(north_eez, south_eez) |> 
  sf::st_transform(rca_crs) |>
  dplyr::filter(OBJECTID == 1)|>
  dplyr::select(boundary_type, boundary_name, area_name, geometry) |> 
  dplyr::mutate(land_ref = "mainland")
```

```{r}
## information for building polygons
polygon_df_orig <- here::here(data_path, rca_data_fn) |> 
  openxlsx::read.xlsx(sheet = 4) |> 
  janitor::clean_names() 

## Create clean data frame of polygon metadata
polygon_df <- polygon_df_orig |> 
  dplyr::select(-completed) |>
  dplyr::filter(shoreward_boundary != "N/A") |>
  dplyr::mutate(
    SiteName = paste(## Create unique site name for id
      "TrawlRCA", year_month, land_ref, northern_boundary,
      southern_boundary, shoreward_boundary, seaward_boundary,
      sep = "_")) |>
  tidyr::pivot_longer(
    northern_boundary:seaward_boundary,
    names_to = 'boundary_dir', 
    values_to = 'boundary_name') |>
  dplyr::mutate(
    boundary_dir = stringr::str_remove(boundary_dir, '_boundary'),
    boundary_name = dplyr::case_when(
      boundary_name == "U.S. EEZ boundary" ~ "U.S. EEZ Boundary",
      boundary_name == "45 46.00'N" ~ "45 46.00' N",
      boundary_name == '0 fm (100fm_010119.csv)' ~ '100fm_010119.csv',
      boundary_name == "0 fm (Shoreline)" ~ "Shoreline",
      TRUE ~ stringr::str_remove(gsub("[()]", "", boundary_name), pattern = "0 fm "))) |>
  tidyr::pivot_wider(
    names_from = boundary_dir, 
    values_from = boundary_name) |>
  dplyr::mutate(## Update unique site name for id
    SiteName = paste("TrawlRCA", year_month, land_ref, northern, 
                     southern, shoreward, seaward, sep = "_"),
    ns_bounds = paste(northern, southern, sep = "_")) |>
  tidyr::pivot_longer(
    northern:seaward, 
    names_to = 'boundary_dir', 
    values_to = 'boundary_name') |>
  dplyr::mutate(
    boundary_type = dplyr::case_when( ## add column for joining later
      boundary_dir %in% c('northern', 'southern') ~ 'latitude',
      TRUE ~ 'isobath'),
    boundary_name = dplyr::case_when(
      boundary_name == "U.S. EEZ Boundary" & boundary_dir == "northern" ~ 
        "U.S. EEZ Boundary North",
      boundary_name == "U.S. EEZ Boundary" & boundary_dir == "southern" ~ 
        "U.S. EEZ Boundary South",
      TRUE ~ boundary_name)) |>
  dplyr::select(SiteName, year_month, land_ref, ns_bounds, 
                boundary_type, boundary_dir, boundary_name)

north_south_lats <- polygon_df |> 
  dplyr::filter(
    boundary_type == 'latitude',
    !boundary_name %in% c(
      'U.S. EEZ Boundary North', 
      'U.S. EEZ Boundary South')) |> 
  dplyr::distinct(boundary_name) |> 
  dplyr::arrange(boundary_name) |> 
  dplyr::pull(boundary_name)


```

```{r}
convert_to_decimal <- function(lat_str) {
  # Split the string by space and apostrophe to extract degrees, minutes, and direction
  parts <- unlist(strsplit(lat_str, " |'"))
  degree <- as.numeric(parts[1])
  minutes <- as.numeric(parts[2])
  direction <- parts[3]
  
  # Convert to decimal degrees
  decimal_deg <- degree + (minutes / 60)
  
  # Adjust sign for southern latitudes
  if (direction == "S") {
    decimal_deg <- -decimal_deg
  }
  
  return(decimal_deg)
}


# Function to create an sf data frame of lines
create_sf_lines <- function(
    north_south_lats, 
    xmin = -130, 
    xmax = -117
) {
  # Convert latitudes to decimal degrees
  decimal_lats <- sapply(north_south_lats, convert_to_decimal)
  
  make_lat_line <- function(lat) {
    st_linestring(
      matrix(c(xmin, lat, xmax, lat),
             ncol = 2, byrow = TRUE))
  }
  # Create lines within the specified extent
  lines_list <- lapply(decimal_lats, make_lat_line)
  
  # Create an sf data frame
  sf_lines <- st_sf(
    boundary_type = "latitude", 
    boundary_name = north_south_lats, 
    area_name = north_south_lats,
    geometry = st_sfc(lines_list)
  )
  
  # Set CRS to EPSG:4326
  sf_lines <- st_set_crs(sf_lines, 4326)
  
  return(sf_lines)
}

lat_sf <- create_sf_lines(
  north_south_lats, #xmin, xmax,
) |> 
  dplyr::mutate(land_ref = "mainland")

n_s_boundaries_sf <- rbind(eez_sf, lat_sf)
```


## Further testing (not tidy)


```{r}
# Filter observations where boundary_name is "60fm_010104.csv"
filtered_rca_lines_sf <- rca_lines_sf %>%
  filter(boundary_name == "150fm_030106.csv")

plot_rca_line(filtered_rca_lines_sf)
```

```{r}
check_shoreline_intersections(filtered_rca_lines_sf)
check_self_intersections(filtered_rca_lines_sf)

is_simple <- st_is_simple(filtered_rca_lines_sf)
filtered_rca_lines_sf[!is_simple, ]$area_name
```

```{r}
st_write(eez_poly, here("rca-database/line_shapefile/shoreline.shp"))
```


```{r}
  # Check for intersections between the lines and the shoreline
  intersections_with_shoreline <- st_intersects(filtered_rca_lines_sf, shoreline)
  # Check for any intersections
  any_intersections_with_shoreline <- any(lengths(intersections_with_shoreline) > 0)
  # Print result
  if (any_intersections_with_shoreline) {
    cat("There are intersections between the lines and the shoreline.\n")
  } else {
    cat("There are no intersections between the lines and the shoreline.\n")
  }
```

```{r}
intersection <- st_intersection(filtered_rca_lines_sf, shoreline)

intersection_df <- st_as_sf(intersection)
shoreline_df <- st_as_sf(shoreline)
rca_df_line <- st_as_sf(filtered_rca_lines_sf)
# Create a leaflet map
map <- leaflet() %>%
  # Add a base map
  addTiles() %>%
  # Add shoreline to the map, assuming it's a polygon or line
  addPolylines(data = rca_df_line, color = "green", weight = 2) %>%
   addPolygons(data = shoreline_df, color = "blue", weight = 1, fillColor = "blue", fillOpacity = 0.1) %>% 
  # Add intersections as circle markers
  addCircleMarkers(data = intersection_df, color = "red", radius = 5, fillOpacity = 1.0, stroke = FALSE)

# Show the map
map

```

It seems that the intersections occur at the offshore boundaries of the shoreline polygons. Consider reconstructing the shoreline sf object to include only the coastline.

### Generating the polygons



```{r}
lines_sf <- rbind(shoreline, n_s_boundaries_sf, rca_lines_sf)
```




The code below generates the shapes. RUN IT ONLY ONCE.

```{r}
convert_site_to_title <- function(fn) {
  components <- str_split(fn, "_")[[1]]

  if (stringr::str_detect(components[5], "Shoreline")) {
    remaining_components <- str_c(components[6:length(components)], collapse=" ")
    title <- str_c(
      "Year-Month: ", components[1], "\n",
      "Reference:   ", components[2], "\n",
      "North:          ", components[3], "\n",
      "South:          ", components[4], "\n",
      "Shoreward:  ", components[5], "\n",
      "Seaward:     ", remaining_components
    )
  } else {
    remaining_components <- str_c(components[7:length(components)], collapse=" ")
    title <- str_c(
      "Year-Month: ", components[1], "\n",
      "Reference:   ", components[2], "\n",
      "North:          ", components[3], "\n",
      "South:          ", components[4], "\n",
      "Shoreward:  ", components[5], " ", components[6], "\n",
      "Seaward:     ", remaining_components
    )
  }

  return(title)
}
site1 <- "2006-03_mainland_U.S. EEZ Boundary_40 10.00' N_75fm_010105_200fm_040105"

site2 <- "2008-05_mainland_43 20.83' N_42 40.50' N_Shoreline_200fm_010107"

title1 <- convert_site_to_title(site1)

title2 <- convert_site_to_title(site2)

cat(title1, title2, sep = "\n\n")
```


```{r}

process_sites <- function(polygon_df, lines_sf, output_path) {
  # Loop over each unique site
  for (site in unique(polygon_df$SiteName)) {
  
    if (stringr::str_detect(site, "islands")) next
  
    fn <- site |>
      stringr::str_remove(pattern = "TrawlRCA_") |>
      stringr::str_remove_all(pattern = ".csv")
  
    title <- convert_site_to_title(fn)
  
    fn <- paste0(fn, ".jpg")
    fp <- here::here("plots", "polygon_plots", fn)
  
    # if (file.exists(fp)) next
  
    site_poly_sf <- polygon_df |>
      dplyr::filter(SiteName == site) |>
      dplyr::left_join(lines_sf, by = join_by(land_ref, boundary_type, boundary_name)) |>
      sf::st_as_sf()
  
    bbox_vals <- site_poly_sf |>
      summarise(
        xmin = min(st_bbox(filter(site_poly_sf, boundary_dir == "seaward"))$xmin),
        xmax = max(st_bbox(filter(site_poly_sf, boundary_dir == "shoreward"))$xmax),
        ymin = min(st_bbox(filter(site_poly_sf, boundary_dir == "southern"))$ymin),
        ymax = max(st_bbox(filter(site_poly_sf, boundary_dir == "northern"))$ymax)
      ) |>
      tibble::as_tibble() |>
      select(-geometry)
  
    bbox_sf <- st_sf(
      geometry = st_sfc(
        st_polygon(list(
          matrix(
            c(bbox_vals$xmin[1], bbox_vals$ymin[1],
              bbox_vals$xmin[1], bbox_vals$ymax[1],
              bbox_vals$xmax[1], bbox_vals$ymax[1],
              bbox_vals$xmax[1], bbox_vals$ymin[1],
              bbox_vals$xmin[1], bbox_vals$ymin[1]),
            byrow = TRUE, ncol = 2)
        )),
        crs = 4326
      )
    )
  
    # site_polygon <- site_poly_sf |>
    #   sf::st_union() |>
    #   sf::st_polygonize() |>
    #   sf::st_crop(bbox_sf) |>
    #   sf::st_as_sf()
  
    site_poly_sf <- sf::st_crop(site_poly_sf, bbox_sf)
  
    # if (is.na(sf::st_geometry_type(site_polygon)[1]) | sf::st_geometry_type(site_polygon)[1] == "LINESTRING") {
      site_polygon <- site_poly_sf |>
        sf::st_buffer(0.001) |>
        sf::st_union() |>
        sf::st_cast("MULTILINESTRING") |>
        sf::st_polygonize() |>
        sf::st_crop(bbox_sf) |>
        sf::st_buffer(-0.001)  |>
        sf::st_union() |>
        sf::st_as_sf()
    # }
  
    polygon_sf <- sf::st_sf(
      SiteName = site,
      geometry = site_polygon$x
    ) |>
      sf::st_collection_extract()
  
    if ((sf::st_geometry_type(polygon_sf)[1] == "MULTIPOLYGON") | length(polygon_sf) > 1) {
      polygon_sf <- polygon_sf |>
        sf::st_cast("POLYGON") |>
        dplyr::mutate(area = sf::st_area(geometry)) |>
        dplyr::arrange(desc(area)) |>
        dplyr::slice(1) |>
        dplyr::select(-area)
    } else next
  
    all_sites_sf <- rbind(all_sites_sf, polygon_sf)
  }
  
  
  sf::write_sf(all_sites_sf, here::here(output_path, "mainland_closures.gpkg"))
  
  return(all_sites_sf)
}
```

```{r}
process_sites <- process_sites(polygon_df, lines_sf, data_path)

```

Instead we will read it from the already generated and locally stored file

```{r}
all_sites_sf <- mainland_closures <- st_read(here::here(data_path, "mainland_closures_cullen.gpkg"))
```

### Individual testing

```{r}
filtered_sites <- all_sites_sf %>%
  filter(str_detect(SiteName, "TrawlRCA_2003-12_mainland_34 27.00' N_U.S. EEZ Boundary_Shoreline_200fm_petrale_112103.csv"))

dim(all_sites_sf)[1]-sum(st_is_simple(all_sites_sf))
dim(all_sites_sf)[1]-sum(st_is_valid(all_sites_sf))
```

Apparently all polygons have a correct geometry and are valid.

```{r}
filtered_rca_lines_sf <- rca_lines_sf %>%
  filter(boundary_name == "200fm_petrale_112103.csv")

# Get the points for a specific boundary_name
filtered_rca_points_sf <- rca_legis_points_df %>%
  filter(boundary_name == "200fm_petrale_112103.csv") %>% 
  sf::st_as_sf(coords = c("lon", "lat"), crs = 4326)

wrong_points_eval <- check_wrong_points(filtered_rca_points_sf,eez_poly,islands_poly)
wrong_points_eval

leaflet() %>%
  addTiles() %>%
  addPolygons(data = eez_poly, color = "blue", weight = 1, fillColor = "blue", fillOpacity = 0.1) %>% 
  addPolygons(data = filtered_sites, color = "yellow", weight = 1, fillColor = "yellow", fillOpacity = 0.1) %>% 
  addPolylines(data = filtered_rca_lines_sf, color = "orange") %>% 
  addCircleMarkers(data = wrong_points_eval$points_in_land, color = "red", radius = 3, fillOpacity = 1.0, stroke = FALSE)
```

```{r}
lines_sf <- rbind(shoreline, n_s_boundaries_sf, filtered_rca_lines_sf)
```

removing the loop. individual evaluation

```{r}

site2 <- polygon_df %>%
  filter(str_detect(SiteName, "TrawlRCA_2003-12_mainland_34 27.00' N_U.S. EEZ Boundary_Shoreline_200fm_petrale_112103.csv"))

site <- site2$SiteName


all_sites_sf <- st_sf(
  SiteName = character(), 
  geometry = st_sfc(crs = st_crs(4326))
)

fn <- site |> 
  stringr::str_remove(pattern = "TrawlRCA_") |> 
  stringr::str_remove_all(pattern = ".csv")

title <- convert_site_to_title(fn)

fn <- paste0(fn, ".jpg")
fp <- here::here("plots", "polygon_plots", fn)

# if (file.exists(fp)) next

site_poly_sf <- polygon_df |>
  dplyr::filter(SiteName == site) |>
  dplyr::left_join(lines_sf, by = join_by(land_ref, boundary_type, boundary_name)) |>
  sf::st_as_sf() 

bbox_vals <- site_poly_sf |>
  summarise(
    xmin = min(st_bbox(filter(site_poly_sf, boundary_dir == "seaward"))$xmin),
    xmax = max(st_bbox(filter(site_poly_sf, boundary_dir == "shoreward"))$xmax),
    ymin = min(st_bbox(filter(site_poly_sf, boundary_dir == "southern"))$ymin),
    ymax = max(st_bbox(filter(site_poly_sf, boundary_dir == "northern"))$ymax)
  ) |>
  tibble::as_tibble() |>
  select(-geometry) 

bbox_sf <- st_sf(
  geometry = st_sfc(
    st_polygon(list(
      matrix(
        c(bbox_vals$xmin[1], bbox_vals$ymin[1],
          bbox_vals$xmin[1], bbox_vals$ymax[1],
          bbox_vals$xmax[1], bbox_vals$ymax[1],
          bbox_vals$xmax[1], bbox_vals$ymin[1],
          bbox_vals$xmin[1], bbox_vals$ymin[1]), 
        byrow = TRUE, ncol = 2)
    )),
    crs = 4326
  )
)

# site_polygon <- site_poly_sf |>
#   sf::st_union() |>
#   sf::st_polygonize() |>
#   sf::st_crop(bbox_sf) |>
#   sf::st_as_sf()

site_poly_sf <- sf::st_crop(site_poly_sf, bbox_sf) 

# if (is.na(sf::st_geometry_type(site_polygon)[1]) | sf::st_geometry_type(site_polygon)[1] == "LINESTRING") {
  site_polygon <- site_poly_sf |>
    sf::st_buffer(0.001) |>
    sf::st_union() |>
    sf::st_cast("MULTILINESTRING") |>
    sf::st_polygonize() |> 
    sf::st_crop(bbox_sf) |> 
    sf::st_buffer(-0.001)  |>
    sf::st_union() |> 
    sf::st_as_sf()
# }

polygon_sf <- sf::st_sf(
  SiteName = site,
  geometry = site_polygon$x
) |> 
  sf::st_collection_extract()

if ((sf::st_geometry_type(polygon_sf)[1] == "MULTIPOLYGON") | length(polygon_sf) > 1) {
  polygon_sf <- polygon_sf |>
    sf::st_cast("POLYGON") |> 
    dplyr::mutate(area = sf::st_area(geometry)) |>  
    dplyr::arrange(desc(area)) |> 
    dplyr::slice(1) |> 
    dplyr::select(-area)
} else next

all_sites_sf <- rbind(all_sites_sf, polygon_sf)
  

leaflet() %>%
  addTiles() %>%
  addPolygons(data = eez_poly, color = "blue", weight = 1, fillColor = "blue", fillOpacity = 0.1) %>% 
  addPolygons(data = all_sites_sf, color = "yellow", weight = 1, fillColor = "yellow", fillOpacity = 0.1) %>% 
  addPolylines(data = filtered_rca_lines_sf_short, color = "orange") %>% 
  addCircleMarkers(data = wrong_points_eval$points_in_land, color = "red", radius = 3, fillOpacity = 1.0, stroke = FALSE)
  
```


filtered_rca_lines_sf goes beyond the southern border. testing whether this may be influencing.
Also could be the shoreline if it is intersected farther in the west (same area example in point conception)

```{r}
st_write(filtered_rca_lines_sf, here("rca-database/line_shapefile/filtered_rca_lines_sf.geojson"))

filtered_rca_lines_sf_short <- st_read( here("rca-database/line_shapefile/filtered_rca_lines_sf.geojson"))
mainland_shore <- st_read( here("rca-database/line_shapefile/mainland_shore.geojson"))

```

Evaluating the influence of liens going beyond the borders, this has to be discarded as the cause of the problem.

```{r}
leaflet() %>%
  addTiles() %>%
  addPolylines(data = site_poly_sf, color = "orange")

```

```{r}
st_write(site_poly_sf, here("rca-database/line_shapefile/bounding_lines.geojson"))

```

```{r}
# mainland_shore <- st_read( here("rca-database/line_shapefile/mainland_shore.geojson")) |> 
mainland_shore <- st_read( here("rca-database/line_shapefile/shoreline_all.geojson")) |> 
  sf::st_as_sf() |>
  tidyr::replace_na(replace = list(Name = "Shoreline")) |> 
  dplyr::group_by(AreaType) |>
  dplyr::summarize(geometry = sf::st_union(geometry)) |> 
  dplyr::mutate(
    boundary_type = "isobath",
    boundary_name = "Shoreline",
    area_name = "Shoreline",
    land_ref = ifelse(AreaType == "water", "mainland", "islands")) |> 
  dplyr::select(boundary_type, boundary_name, area_name, land_ref, geometry)



lines_sf <- rbind(mainland_shore, n_s_boundaries_sf, filtered_rca_lines_sf)
```

Excluding the wester border of the EEZ we see that the shape is generated correctly. below we will apply that procedure to all of the shapes.

