---
format: html
editor_options: 
  chunk_output_type: console
---

# New approach for RCA polygon creation

## Setup

```{r}
if (!require(librarian,quietly = T)){
  install.packages('librarian')
}

librarian::shelf(
  here,
  # plotly,
  readxl,
  glue,
  tidyverse,
  lubridate,
  data.table,
  openxlsx,
  terra,
  leaflet,
  sf,
  openxlsx,
  rnaturalearth, 
  rnaturalearthdata,
  # foreach,
  # doParallel,
  iterators,
  quiet = T
)

sf_use_s2(FALSE)
```

```{r}
# Read in data using script (this helps keeping tidy the qmd)
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v4.R"))
source(here("RCA_data_exploration/scripts/generate_rca_objects.R"))
```

# Functions testing

## Testing for constant longitude lines

```{r}
eez_poly <-  st_read(here("RCA_data_exploration", "Ruttenberg et al collaboration", "spatial_ref_files", "eez.geojson"))

# The new approach considers the coastline independently than the EEZ
coastline <- st_read( here(data_path,"spatial_ref_files/all_shoreline_main_comb.geojson")) %>% 
  rename(
    land_ref = area_name,
    area_name = AreaType_2) %>% 
  mutate(
    boundary_type = "isobath",
    boundary_name = "shoreline")



# Update isolines form CalPoly gdb
feature_class <- st_read(dsn = cal_poly_fp, layer = "Master_line_feature_source")
isolines <- feature_class %>% 
  filter(CoordFileName != "NA" & CoordFileName != "")

split_isolines <- split(isolines, isolines$CoordFileName)

# function to apply the transformation
transform_isolines <- function(df) {
  df %>%
    st_combine() %>%
    st_as_sf() %>%
    st_set_geometry("geometry") %>%
    mutate(
      boundary_type = "isobath",
      boundary_name = first(df$CoordFileName),
      area_name = "not_defined",
      land_ref = "bathymetry",
      .before = geometry
    )
}

# Apply the transformation to each split dataframe and combine the results
new_isolines <- map_dfr(split_isolines, transform_isolines)

isolines_testing <- new_isolines %>% 
  filter(boundary_name == "150fm_012703.csv")

selected_longitude_lines <- rbind(isolines_testing, coastline)
```

```{r}
select_random_lat_boundaries <- function(data_frame) {
  # Extract unique boundary names
  unique_boundaries <- unique(data_frame$boundary_name)
  # Ensure that there are at least 2 unique boundaries to select from
  if(length(unique_boundaries) < 2) {
    stop("Not enough unique boundary names to select two random, non-equal values.")
  }
  # Randomly select two non-equal boundary names
  selected_boundaries <- sample(unique_boundaries, 2)
  # Filter rows that match the randomly selected boundary names
  selected_rows <- data_frame %>% 
    filter(boundary_name %in% selected_boundaries)
  return(selected_rows)
}

selected_latitude_lines <- select_random_lat_boundaries(n_s_boundaries_sf)


testing_poly <- rca_lines_to_polygons_v4(selected_longitude_lines,selected_latitude_lines,eez_poly)
```

**Errors detected:**

1. Selecting inner polygons based on area can lead to issues in regions where land areas exceed water areas, particularly when the shoreline acts as a boundary. This situation is notable in Oregon, where large estuaries can cause the polygon generation process to incorrectly focus on land areas. For instance, for the file "150fm_012703.csv," the latitude limits of "43 20.83' N" and "46 16.00' N" exemplify this issue. Additional examples include the latitudinal ranges "42 40.50' N" to "45 46.00' N".

2. The execution of the random polygon generation script show further anomalies in shapes. However, these are likely due to the absence of a longitudinal lines at certain latitudes.

## Testing with all random lines

```{r}
select_random_lon_boundaries <- function(data_frame) {
  # Extract unique boundary names
  unique_boundaries <- unique(data_frame$boundary_name)
  # Ensure that there are at least 2 unique boundaries to select from
  if(length(unique_boundaries) < 2) {
    stop("Not enough unique boundary names to select two random, non-equal values.")
  }
  # Randomly select two non-equal boundary names
  selected_boundaries <- sample(unique_boundaries, 2)
  # Filter rows that match the randomly selected boundary names
  selected_rows <- data_frame %>% 
    filter(boundary_name %in% selected_boundaries)
  return(selected_rows)
}

selected_longitude_lines <- select_random_lon_boundaries(new_isolines)
selected_latitude_lines <- select_random_lat_boundaries(n_s_boundaries_sf)


testing_poly <- rca_lines_to_polygons_v3(selected_longitude_lines,selected_latitude_lines)
```

**Errors detected:**

1. After some testing we detected that the islands are not clipped out if shoreline is not part of the boundary. (e.g., 36 00.00' N - U.S. EEZ Boundary South - 100fm_030104.csv - 150fm_010105.csv).


# Function implementation

## Input data

Although this was already done in the testing section, we will include the read-in code to be evaluated here as well.

```{r}
source(here("RCA_data_exploration/scripts/generate_rca_objects.R"))

# EEZ polygon, though it will only be used in v5 of the fuction exclusively applyed to those polygons neighboring the EEZ
eez_poly <-  st_read(here("RCA_data_exploration", "Ruttenberg et al collaboration", "spatial_ref_files", "eez.geojson"))

# Coastline shape that will define the shoreline layer as an extra isoline. As described earlier, the new approach considers the coastline independently than the EEZ
coastline <- st_read( here(data_path,"spatial_ref_files/all_shoreline_main_comb.geojson")) %>% 
  rename(
    land_ref = area_name,
    area_name = AreaType_2) %>% 
  mutate(
    boundary_type = "isobath",
    boundary_name = "shoreline") %>% 
  mutate(boundary_name = ifelse(boundary_name == "shoreline", # Matching with instructiosn df
                                "Shoreline",
                                boundary_name)) 

# RCA lines  form CalPoly gdb
feature_class <- st_read(dsn = cal_poly_fp, layer = "Master_line_feature_source")

isolines <- feature_class %>% 
  filter(CoordFileName != "NA" & CoordFileName != "") 
split_isolines <- split(isolines, isolines$CoordFileName)

transform_isolines <- function(df) {
  df %>%
    st_combine() %>%
    st_as_sf() %>%
    st_set_geometry("geometry") %>%
    mutate(
      boundary_type = "isobath",
      boundary_name = first(df$CoordFileName),
      area_name = "not_defined",
      land_ref = "bathymetry",
      .before = geometry
    )
}

new_isolines <- map_dfr(split_isolines, transform_isolines)

# Combine coastline with isolines to have them all in a single object
coastline <- st_transform(coastline, st_crs(new_isolines))
lon_boundary <-  rbind(coastline,new_isolines)

# Reference Cullen's sf with the latitudinal borders for each RCA
n_s_boundaries_sf <- st_transform(n_s_boundaries_sf, st_crs(new_isolines))
lat_boundary <- n_s_boundaries_sf
```


## Instructions dataframe

First, we will create an instructions data frame based on Cullen's code. Some updates need to be made so the contents of the instructions data frame match those from the `sf` objects. The instructions file contains the characteristics of each resulting polygon, which include the RCA date plus the line references that contain them.

```{r}
## Create clean data frame of polygon metadata
polygon_instructions_df <- polygon_df_orig  %>% 
  dplyr::select(-completed)  %>% 
  dplyr::filter(shoreward_boundary != "N/A")  %>% 
  dplyr::mutate(
    shoreward_boundary = gsub("^0 fm \\(([^)]+)\\)$", "\\1", shoreward_boundary),
    southern_boundary = ifelse(southern_boundary == "U.S. EEZ Boundary", 
                               "U.S. EEZ Boundary South", 
                               southern_boundary),
    northern_boundary = ifelse(northern_boundary == "U.S. EEZ Boundary", 
                               "U.S. EEZ Boundary North", 
                               northern_boundary),
    northern_boundary = ifelse(northern_boundary == "U.S. EEZ boundary", 
                               "U.S. EEZ Boundary North", 
                               northern_boundary)) %>% 
  rename( lat_boundary1 = northern_boundary,
          lat_boundary2 = southern_boundary,
          lon_boundary1 = shoreward_boundary,
          lon_boundary2 = seaward_boundary)


# If we check the latitude variables levels we see an error where "45 46.00'N" should be "45 46.00' N"
unique(polygon_instructions_df$lat_boundary2)
# Update "45 46.00'N" to "45 46.00' N"
polygon_instructions_df <- polygon_instructions_df %>% 
  mutate(lat_boundary1 = ifelse(lat_boundary1 == "45 46.00'N",
                                "45 46.00' N",
                                lat_boundary1),
         lat_boundary2 = ifelse(lat_boundary2 == "45 46.00'N",
                                "45 46.00' N",
                                lat_boundary2))
```

m¡Make sure that the instructions contents are correct.

```{r}
unique(polygon_instructions_df$lat_boundary1)
unique(polygon_instructions_df$lat_boundary2)
unique(polygon_instructions_df$lon_boundary1)
unique(polygon_instructions_df$lon_boundary2)
```

## Running for inner RCAs

After some testing, it was seen that the problems associated with inner RCAs and those neighboring the north and south limits of the EEZ are distinct. Therefore, we will apply two different function versions for each type of RCA.

For the inner RCAs, after an initial run using version 4, we encountered issues due to the lack of code addressing "no contact with border points" issue at both latitude borders. This oversight led to errors for the unique lines generated (i.e., `unique_geometries_sf`) in version 4, specifically for objects 74, 75, 89, 97, 98, 99, and 104. The same version 4 function also produced an empty geometry for object 69, which we will further discussion.

These issues were addressed in version 4.2. However, additional problems were identified. An anomaly was detected northwest of San Francisco, in front of the Greater Farallones National Marine Sanctuary, concerning the line "100fm_010107.csv." This anomaly is present in both NOAA lines and our generated lines, where a section of the line splits into two. Upon a detailed inspection of the line using QGIS, it was observed that this shape contains several redundant vertices.

```{r, echo = FALSE}
source(here("RCA_data_exploration/scripts/generate_rca_lines.R"))
filtered_rca_lines_sf <- rca_lines_sf %>%
  filter(boundary_name == "100fm_010107.csv")

filtered_rca_noaa_lines_sf <- new_isolines %>%
  filter(boundary_name == "100fm_010107.csv")
```

```{r, echo = FALSE}
leaflet() %>%
     addTiles() %>%
     addPolylines(data = filtered_rca_noaa_lines_sf, color = "orange", weight=2, group = "NOAA RCA line") %>%
     addPolylines(data = filtered_rca_lines_sf, color = "blue", weight=2, group = "emLab RCA line")%>%
  fitBounds(lng1 = -123.57, lat1 = 38.14, 
                    lng2 = -123.33, lat2 = 37.89) %>%
          addLegend(position = "topright", 
                    title = "100fm_010107.csv", 
                    opacity = 0, 
                    labels = "", 
                    colors = "transparent") %>% 
          addLayersControl(overlayGroups = c( "emLab RCA line", "NOAA RCA line"))
```

This issue is the cause of the empty geometry for object 69 and has led to additional anomalies with the new code, affecting 3 unique geometries and 24 total RCA polygons. Since the erroneous line is difficult to interpret and decisions must be made regarding the points that define it, we will exclude it until NOAA determines how to proceed with it.

```{r}
intructions_sample <- polygon_instructions_df %>% 
  # Exclude EEZ boundaries
  filter(lat_boundary1 != "U.S. EEZ Boundary North",
         lat_boundary2 != "U.S. EEZ Boundary South") %>% 
  # Remove instructions where 100fm_010107.csv is a problem
  filter(!(lat_boundary1 == "40 10.00' N" &
           lat_boundary2 == "38 00.00' N" &
           lon_boundary1 == "100fm_010107.csv" &
           lon_boundary2 == "150fm_010107.csv")) %>%
  filter(!(lat_boundary1 == "38 00.00' N" &
           lat_boundary2 == "34 27.00' N" &
           lon_boundary1 == "100fm_010107.csv" &
           lon_boundary2 == "150fm_010107.csv")) %>%
   filter(!(lat_boundary1 == "40 10.00' N" &
           lat_boundary2 == "38 00.00' N" &
           lon_boundary1 == "100fm_010107.csv" &
           lon_boundary2 == "200fm_petrale_010107.csv"))
```

Once we have defined the updated instructions, we will apply v4.2 for all RCAs of interest.

```{r}
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v4.2.R"))
```

```{r}
# Initialize list to store results
results <- list()
results_df <- data.frame(date = character(), area = character(), execution = logical(), stringsAsFactors = FALSE)

# Loop that evaluates each instruction line and applies v4.2 to it
for (i in 1:nrow(intructions_sample)) {
    # For each row in intructions_sample, extract the boundary names
    lat_boundary1_name <- intructions_sample$lat_boundary1[i]
    lat_boundary2_name <- intructions_sample$lat_boundary2[i]

    lon_boundary1_name <- intructions_sample$lon_boundary1[i]
    lon_boundary2_name <- intructions_sample$lon_boundary2[i] 

    # Select latitude lines
    selected_latitude_lines <- lat_boundary[lat_boundary$boundary_name == lat_boundary1_name, ] %>% 
      rbind(lat_boundary[lat_boundary$boundary_name == lat_boundary2_name, ])
    
    # Select longitude lines
    selected_longitude_lines <- lon_boundary[lon_boundary$boundary_name == lon_boundary1_name, ] %>% 
      rbind(lon_boundary[lon_boundary$boundary_name == lon_boundary2_name, ])
    
    # Process the selected lines to create polygons
    result <- suppressMessages(
      rca_lines_to_polygons_v4.2(selected_longitude_lines, selected_latitude_lines,eez_poly)
    )
    
    # Extracting boundary_name from each
    boundary_name_longitude1 = selected_longitude_lines$boundary_name[1] 
    boundary_name_longitude2 = selected_longitude_lines$boundary_name[2] 
    boundary_name_latitude1 = selected_latitude_lines$boundary_name[1] 
    boundary_name_latitude2 = selected_latitude_lines$boundary_name[2] 
    
    # Constructing the string with `glue`
    final_string <- glue("{lon_boundary1_name}-{lon_boundary2_name}-{lat_boundary1_name}-{lat_boundary2_name}")
    final_string <- gsub(" ", "", final_string)
    
    if (is.null(result) || all(st_is_empty(result))) {
        execution_status <- "empty geometry"
    } else {
        execution_status <- "successful"
    }
    
    print(paste0(as.character(intructions_sample$year_month[i]),"-", final_string, ": ",i,"/",nrow(intructions_sample),"...", execution_status))
    # Append to the results dataframe
    results_df <- rbind(results_df, data.frame(date = intructions_sample$year_month[i], area = final_string, execution = execution_status))
    
    # Combine polygons into a multipolygons and assign the instructions df variable levels
    combined_sf <- result %>% 
      st_combine() %>% 
      st_sf() %>% 
      cbind(intructions_sample[i,])
    
    # Store each result in the results list
    results[[i]] <- combined_sf
}

# Summary results
table(results_df$execution)
# Combine resulting list into a single sf object
combined_results_sf <- do.call(rbind, results)
# Export as a geopackage 
st_write(combined_results_sf, here("RCA_data_exploration","outputs","rca_poly","inner_rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```

Additionally, to visually explore the validity of the generated polygons, we can extract the unique polygons, significantly reducing the manual effort involved.


```{r}
# Initialize a logical vector to mark duplicates; FALSE means no duplicate found yet
is_duplicate <- rep(FALSE, length(combined_results_sf))

# Loop over all geometries
for (i in 1:length(combined_results_sf$geometry)) {
  # Skip if this geometry has already been marked as a duplicate
  if (!is_duplicate[i]) {
    # Compare the current geometry with all others
    duplicates = sapply(combined_results_sf$geometry, function(x) identical(x, combined_results_sf$geometry[[i]]))
    # Mark duplicates, but keep the first occurrence
    is_duplicate <- is_duplicate | (duplicates & !is_duplicate)
    is_duplicate[i] <- FALSE  # Ensure the first instance is not marked as duplicate
  }
}

# Filter out duplicates
unique_geometries <- combined_results_sf[!is_duplicate, ]
```


```{r}
st_write(unique_geometries, here("RCA_data_exploration","outputs","rca_poly","unique_inner_rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```

## Running for border RCAs


Select border RCAs

```{r}
intructions_sample <- polygon_instructions_df %>% 
  filter(lat_boundary1 == "U.S. EEZ Boundary North" |
         lat_boundary2 == "U.S. EEZ Boundary South")
```

```{r}
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.R"))
```


### Testing with shoreline RCAs

```{r}
intructions_sample <- intructions_sample %>% 
  filter(lon_boundary1 == "Shoreline")
```

```{r}
# Initialize list to store results
results <- list()
results_df <- data.frame(date = character(), area = character(), execution = logical(), stringsAsFactors = FALSE)

# Loop that evaluates each instruction line and applies v4.2 to it
for (i in 1:nrow(intructions_sample)) {
    # For each row in intructions_sample, extract the boundary names
    lat_boundary1_name <- intructions_sample$lat_boundary1[i]
    lat_boundary2_name <- intructions_sample$lat_boundary2[i]

    lon_boundary1_name <- intructions_sample$lon_boundary1[i]
    lon_boundary2_name <- intructions_sample$lon_boundary2[i] 

    # Select latitude lines
    selected_latitude_lines <- lat_boundary[lat_boundary$boundary_name == lat_boundary1_name, ] %>% 
      rbind(lat_boundary[lat_boundary$boundary_name == lat_boundary2_name, ])
    
    # Select longitude lines
    selected_longitude_lines <- lon_boundary[lon_boundary$boundary_name == lon_boundary1_name, ] %>% 
      rbind(lon_boundary[lon_boundary$boundary_name == lon_boundary2_name, ])
    
    # Process the selected lines to create polygons
    result <- suppressMessages(
      rca_lines_to_polygons_v5(selected_longitude_lines, selected_latitude_lines,eez_poly)
    )
    
  
    
    # Constructing the string with `glue`
    final_string <- glue("{lon_boundary1_name}-{lon_boundary2_name}-{lat_boundary1_name}-{lat_boundary2_name}")
    final_string <- gsub(" ", "", final_string)
    
    if (is.null(result) || all(st_is_empty(result))) {
        execution_status <- "empty geometry"
    } else {
        execution_status <- "successful"
    }
    
    print(paste0(as.character(intructions_sample$year_month[i]),"-", final_string, ": ",i,"/",nrow(intructions_sample),"...", execution_status))
    # Append to the results dataframe
    results_df <- rbind(results_df, data.frame(date = intructions_sample$year_month[i], area = final_string, execution = execution_status))
    
    # Combine polygons into a multipolygons and assign the instructions df variable levels
    combined_sf <- result %>% 
      st_combine() %>% 
      st_sf() %>% 
      cbind(intructions_sample[i,])
    
    # Store each result in the results list
    results[[i]] <- combined_sf
}

# Summary results
table(results_df$execution)
```

```{r}
# Combine resulting list into a single sf object
combined_results_sf <- do.call(rbind, results)
# Export as a geopackage 
st_write(combined_results_sf, here("RCA_data_exploration","outputs","rca_poly","border_rca_polygons_shoreline_test.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```

```{r}
combined_results_sf$geometry_wkt <- st_as_text(combined_results_sf$geometry)

unique_geometries_sf <- combined_results_sf %>%
  distinct(geometry_wkt, .keep_all = TRUE) %>%
  select(-geometry_wkt) %>% 
  st_as_sf()
```

```{r}
st_write(unique_geometries_sf, here("RCA_data_exploration","outputs","rca_poly","unique_border_rca_polygons_shoreline.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```

### Apply to all Border RCAs

```{r}
instructions_sample <- polygon_instructions_df %>% 
  filter(lat_boundary1 == "U.S. EEZ Boundary North" |
         lat_boundary2 == "U.S. EEZ Boundary South") 
```
697
```{r}
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.R"))
```

```{r}
library(parallel)
library(doParallel)
library(foreach)
library(dplyr)
library(sf)
library(glue)

# Register parallel backend to use multiple cores
numCores <- detectCores() -1
registerDoParallel(cores = numCores)

# Assuming 'instructions_sample', 'lat_boundary', 'lon_boundary', and necessary functions are already defined

# Initialize list to store results from each iteration
results <- list()

# Parallel loop using foreach. Note the changes in the loop's structure
results <- foreach(i = 1:nrow(instructions_sample), .packages = c("dplyr", "sf", "glue")) %dopar% {
  tryCatch({
  # Extracting boundary names
  lat_boundary1_name <- instructions_sample$lat_boundary1[i]
  lat_boundary2_name <- instructions_sample$lat_boundary2[i]
  lon_boundary1_name <- instructions_sample$lon_boundary1[i]
  lon_boundary2_name <- instructions_sample$lon_boundary2[i]

  # Selecting latitude and longitude lines
  selected_latitude_lines <- lat_boundary[lat_boundary$boundary_name == lat_boundary1_name, ] %>% 
    rbind(lat_boundary[lat_boundary$boundary_name == lat_boundary2_name, ])
  selected_longitude_lines <- lon_boundary[lon_boundary$boundary_name == lon_boundary1_name, ] %>% 
    rbind(lon_boundary[lon_boundary$boundary_name == lon_boundary2_name, ])

  # Process to create polygons (assuming rca_lines_to_polygons_v5 is a predefined function)
  result <- suppressMessages(
    rca_lines_to_polygons_v5(selected_longitude_lines, selected_latitude_lines, eez_poly)
  )
  
  combined_sf <- result %>% 
      st_combine() %>% 
      st_sf() %>% 
      cbind(instructions_sample[i,])

  # Return the sf object directly
  combined_sf
  
  }, error = function(e) {
      # Log or return the error along with the iteration number
      list(error = e, iteration = i)
    })
}

# Don't forget to stop the cluster if you're done with parallel operations
stopImplicitCluster()

```


```{r}
results_clean <- Filter(function(x) !is.list(x$error), results)

# Extract errors and their iterations into a list
errors_list <- lapply(results, function(x) {
  if (is.list(x) && !is.null(x$error)) {
    return(list(error_message = as.character(x$error$message), iteration = x$iteration))
  } else {
    return(NULL)
  }
})

# Remove NULL elements
errors_list <- Filter(Negate(is.null), errors_list)

iterations_vector <- sapply(errors_list, function(x) x$iteration)

# Check the objects
instructions_sample[iterations_vector,]

```
errors in 698, 699 and 700

```{r}
# Combine resulting list into a single sf object
combined_results_sf <- do.call(rbind, results_clean)
# Export as a geopackage 
st_write(combined_results_sf, here("RCA_data_exploration","outputs","rca_poly","border_rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```


```{r}
# Initialize a logical vector to mark duplicates; FALSE means no duplicate found yet
is_duplicate <- rep(FALSE, length(combined_results_sf))

# Loop over all geometries
for (i in 1:length(combined_results_sf$geometry)) {
  # Skip if this geometry has already been marked as a duplicate
  if (!is_duplicate[i]) {
    # Compare the current geometry with all others
    duplicates = sapply(combined_results_sf$geometry, function(x) identical(x, combined_results_sf$geometry[[i]]))
    # Mark duplicates, but keep the first occurrence
    is_duplicate <- is_duplicate | (duplicates & !is_duplicate)
    is_duplicate[i] <- FALSE  # Ensure the first instance is not marked as duplicate
  }
}

# Filter out duplicates
unique_geometries <- combined_results_sf[!is_duplicate, ]
```

```{r}
st_write(unique_geometries, here("RCA_data_exploration","outputs","rca_poly","unique_border_rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```


## Running for all

```{r}
instructions_sample <- polygon_instructions_df
```
697
```{r}
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.R"))
```


```{r}
# Register parallel backend to use multiple cores
numCores <- detectCores() -1
registerDoParallel(cores = numCores)

# Assuming 'instructions_sample', 'lat_boundary', 'lon_boundary', and necessary functions are already defined

# Initialize list to store results from each iteration
results <- list()

# Parallel loop using foreach. Note the changes in the loop's structure
results <- foreach(i = 1:nrow(instructions_sample), .packages = c("dplyr", "sf", "glue")) %dopar% {
  tryCatch({
  # Extracting boundary names
  lat_boundary1_name <- instructions_sample$lat_boundary1[i]
  lat_boundary2_name <- instructions_sample$lat_boundary2[i]
  lon_boundary1_name <- instructions_sample$lon_boundary1[i]
  lon_boundary2_name <- instructions_sample$lon_boundary2[i]

  # Selecting latitude and longitude lines
  selected_latitude_lines <- lat_boundary[lat_boundary$boundary_name == lat_boundary1_name, ] %>% 
    rbind(lat_boundary[lat_boundary$boundary_name == lat_boundary2_name, ])
  selected_longitude_lines <- lon_boundary[lon_boundary$boundary_name == lon_boundary1_name, ] %>% 
    rbind(lon_boundary[lon_boundary$boundary_name == lon_boundary2_name, ])

  # Process to create polygons (assuming rca_lines_to_polygons_v5 is a predefined function)
  result <- suppressMessages(
    rca_lines_to_polygons_v5(selected_longitude_lines, selected_latitude_lines, eez_poly)
  )
  
  combined_sf <- result %>% 
      st_combine() %>% 
      st_sf() %>% 
      cbind(instructions_sample[i,])

  # Return the sf object directly
  combined_sf
  
  }, error = function(e) {
      # Log or return the error along with the iteration number
      list(error = e, iteration = i)
    })
}

# Don't forget to stop the cluster if you're done with parallel operations
stopImplicitCluster()

```


```{r}
results_clean <- Filter(function(x) !is.list(x$error), results)

# Extract errors and their iterations into a list
errors_list <- lapply(results, function(x) {
  if (is.list(x) && !is.null(x$error)) {
    return(list(error_message = as.character(x$error$message), iteration = x$iteration))
  } else {
    return(NULL)
  }
})

# Remove NULL elements
errors_list <- Filter(Negate(is.null), errors_list)

iterations_vector <- sapply(errors_list, function(x) x$iteration)

# Check the objects
instructions_sample[iterations_vector,]

incorrect_lines <- instructions_sample[iterations_vector,] %>%
  group_by(land_ref, lat_boundary1, lat_boundary2, lon_boundary1, lon_boundary2) %>%
  slice(1) %>%
  ungroup()
```

```{r}
# Combine resulting list into a single sf object
combined_results_sf <- do.call(rbind, results_clean)
# Export as a geopackage 
st_write(combined_results_sf, here("RCA_data_exploration","outputs","rca_poly","rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```


```{r}
# Initialize a logical vector to mark duplicates; FALSE means no duplicate found yet
is_duplicate <- rep(FALSE, length(combined_results_sf))

# Loop over all geometries
for (i in 1:length(combined_results_sf$geometry)) {
  # Skip if this geometry has already been marked as a duplicate
  if (!is_duplicate[i]) {
    # Compare the current geometry with all others
    duplicates = sapply(combined_results_sf$geometry, function(x) identical(x, combined_results_sf$geometry[[i]]))
    # Mark duplicates, but keep the first occurrence
    is_duplicate <- is_duplicate | (duplicates & !is_duplicate)
    is_duplicate[i] <- FALSE  # Ensure the first instance is not marked as duplicate
  }
}

# Filter out duplicates
unique_geometries <- combined_results_sf[!is_duplicate, ]
```

```{r}
st_write(unique_geometries, here("RCA_data_exploration","outputs","rca_poly","unique_rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```
