---
format: html
editor_options: 
  chunk_output_type: console
---

## Setup

```{r}
if (!require(librarian,quietly = T)){
  install.packages('librarian')
}

librarian::shelf(
  here,
  # plotly,
  readxl,
  tidyverse,
  lubridate,
  data.table,
  openxlsx,
  terra,
  leaflet,
  sf,
  openxlsx,
  rnaturalearth, 
  rnaturalearthdata,
  # foreach,
  # doParallel,
  iterators,
  quiet = T
)

sf_use_s2(FALSE)
```

## Getting lines from Cullen's methods

### Read in data

```{r}
# Read in data using script (this helps keeping tidy the qmd)
source(here("RCA_data_exploration/scripts/generate_rca_lines.R"))
```

### Exploring lines

One of the potential causes for the polygons not drawing properly is defects in line geometries. As annotated in the sheet "rca_line_checking," it appears that the most common problems are the existence of points on land and the points being out of order. The first issue is problematic in itself because RCA must be in territorial waters. The second can cause self-intersections, leading to errors in subsequent polygon transformations.

Below, we explore individual lines based on the CSV file name to see if these issues can be detected programmatically.

From the JPGs generated by Cullen's script, one the most visually noticeable error occurred for "60fm_010104.csv," where a Channel Island boundary point appears in a mainland area.

```{r}
# Filter observations where boundary_name is "60fm_010104.csv"
filtered_rca_lines_sf <- rca_lines_sf %>%
  filter(boundary_name == "60fm_010104.csv")
```

First, let's evaluate if there are intersecting lines among all the lines related to this specific sf. Presumably, there will be since an island point is inland.

```{r}
check_line_intersections <- function(filtered_rca_lines_sf) {
  # Compute intersections
  intersections <- st_intersects(filtered_rca_lines_sf)
  # Check for any intersections
  any_intersections <- any(lengths(intersections) > 1)
  # Print result
  if (any_intersections) {
    cat("There are intersecting lines.\n")
  } else {
    cat("There are no intersecting lines.\n")
  }
}

check_line_intersections(filtered_rca_lines_sf)
```

Now lets see if actually there is a line intersecting the shoreline. 

*NOTE: Shoreline files stored at spatial_ref_files have been generated from the EEZ file used in 'polygonize.qmd' using QGIS.*

```{r}
# Updated shoreline file without the EEZ
coastline <- st_read( here(data_path,"/spatial_ref_files/mainland_shore.geojson")) |>
  sf::st_as_sf() |>
  tidyr::replace_na(replace = list(Name = "Shoreline")) |>
  dplyr::group_by(AreaType) |>
  dplyr::summarize(geometry = sf::st_union(geometry)) |>
  dplyr::mutate(
    boundary_type = "isobath",
    boundary_name = "shoreline",
    area_name = "shoreline",
    land_ref = ifelse(AreaType == "islands", "islands", "mainland")) |>
  dplyr::select(boundary_type, boundary_name, area_name, land_ref, geometry)
```

```{r}
# UPDATE: no EEZ but mainline shore only
check_shoreline_intersections <- function(filtered_rca_lines_sf) {
  # Check for intersections between the lines and the shoreline
  intersections_with_shoreline <- st_intersects(filtered_rca_lines_sf, coastline)
  # Check for any intersections
  any_intersections_with_shoreline <- any(lengths(intersections_with_shoreline) > 0)
  # Print result
  if (any_intersections_with_shoreline) {
    cat("There are intersections between the lines and the shoreline.\n")
  } else {
    cat("There are no intersections between the lines and the shoreline.\n")
  }
}

check_shoreline_intersections(filtered_rca_lines_sf)
```

*Note: It's important to be aware that this method assesses whether a line crosses the shoreline. This can result from an existing point inland, but also from incorrect geometry caused by self-intersections, which create segments intersecting with the shoreline.*

Let's use another approach, this time evaluating whether the nodes are outside the expected areas.

```{r}
# Get a polygon for the islands
islands_poly <-  shoreline[1,] %>% 
  st_polygonize() %>% 
  st_collection_extract("POLYGON")

# Get a polygon for the eez
eez_poly <-  shoreline[2,] %>% 
  st_polygonize() %>% 
  st_collection_extract("POLYGON")

# Get the points for a specific boundary_name
filtered_rca_points_sf <- rca_legis_points_df %>%
  filter(boundary_name == "60fm_010104.csv") %>% 
  sf::st_as_sf(coords = c("lon", "lat"), crs = 4326)

if (st_crs(eez_poly) != st_crs(islands_poly)) {
  islands_poly <- st_transform(islands_poly, st_crs(eez_poly))
}
if (st_crs(eez_poly) != st_crs(filtered_rca_points_sf)) {
  filtered_rca_points_sf <- st_transform(filtered_rca_points_sf, st_crs(eez_poly))
}


# Define a function to analyze points in relation to the polygon
check_wrong_points <- function(points_sf, eez, islands) {
  
  points_within <- st_intersects(filtered_rca_points_sf, eez_poly)
  # To get a logical vector indicating whether each point is inside the polygon
  is_within <- lengths(points_within) > 0
  # To see how many points are inside
  n_points_in_land <-sum(!is_within)
  # You can also create a subset of points that are inside the polygon if needed
  points_in_land <- filtered_rca_points_sf[!is_within, ]
  
  
  points_within <- st_intersects(filtered_rca_points_sf, islands_poly)
  # To get a logical vector indicating whether each point is inside the polygon
  is_within <- lengths(points_within) > 0
  # To see how many points are inside
  n_points_in_islands <- sum(is_within)
  # You can also create a subset of points that are inside the polygon if needed
  points_in_islands <- filtered_rca_points_sf[is_within, ]
  
  # Return a list with the counts and subsets
  return(list(
    n_points_in_land = n_points_in_land,
    points_in_land = points_in_land,
    n_points_in_islands = n_points_in_islands,
    points_in_islands = points_in_islands
  ))
}

wrong_points <- check_wrong_points(filtered_rca_points_sf, eez_poly, islands_eez_poly)
wrong_points
```

We can see that there are two points that are outside the EEZ, but only one is inland. The other is at the limit of the EEZ's northern border, which doesn't necessarily mean it is incorrectly located. In fact, if we zoom in on the leaflet map below, we see that it is almost inside the EEZ, probably due to slight changes in the spatial transformation of the northern border line. We will have to consider this when assessing the rest of the lines.

```{r}
leaflet() %>%
  addTiles() %>%
  addPolygons(data = eez_poly, color = "blue", weight = 1, fillColor = "blue", fillOpacity = 0.1) %>% 
  addCircleMarkers(data = wrong_points$points_in_land, color = "red", radius = 3, fillOpacity = 1.0, stroke = FALSE)
```

Finally, let's explore whether self-intersections may occur, potentially creating additional problems.

```{r}
check_self_intersections <- function(filtered_rca_lines_sf) {
  # Check each line for simplicity (i.e., it does not cross itself)
  is_simple <- st_is_simple(filtered_rca_lines_sf)
  # Identify lines that are not simple (i.e., have self-intersections)
  self_intersecting_lines <- filtered_rca_lines_sf[!is_simple, ]
  # Check if there are any self-intersecting lines and print result
  if (nrow(self_intersecting_lines) > 0) {
    cat("There are self-intersecting lines.\n")
  } else {
    cat("There are no self-intersecting lines.\n")
  }
}

check_self_intersections(filtered_rca_lines_sf)
```

In this case, we observe that there are no self-intersections, so the issue with this line arises only from a point being located inland. 

Let's explore another example where self-intersection actually occurs.

```{r}
# Filter observations where boundary_name is "200fm_petrale_010107.csv"
filtered_rca_lines_sf <- rca_lines_sf %>%
  filter(boundary_name == "200fm_petrale_010107.csv")

check_self_intersections(filtered_rca_lines_sf)
```

In this case, we detect self-intersection, and upon checking the associated JPG, it becomes evident that it's occurring in front of Point Conception.

With this in mind, let's create a loop to run the evaluation for all lines and automate the process. We will store the results in a dataframe containing the boundary name, the area names, and variables displaying information on whether a line self-intersects or intersects with the shoreline.

```{r}
# ## FIRST ATTEMPT ONLY CONSIDERED BOUNDARY NAMES
# # Initialize dataframe
# lines_check_df <- data.frame(boundary_name = character(),
#                                    self_intersects = logical(),
#                                    land_point = logical(),
#                                    stringsAsFactors = FALSE)
# 
# for (i in unique(rca_lines_sf$boundary_name)) {
#   # Filter lines by boundary name
#   line_vec <- rca_lines_sf %>% 
#     filter(boundary_name == i)
#   # Self-intersection evaluation
#   is_simple <- st_is_simple(line_vec) 
#   self_intersects <- any(!is_simple) 
#   # Shoreline evaluation
#   intersections_with_shoreline <- st_intersects(line_vec, shoreline)
#   any_intersections_with_shoreline <- any(lengths(intersections_with_shoreline)>0)
#   lines_check_df <- rbind(lines_check_df, 
#                                 data.frame(
#                                   boundary_name = i, 
#                                   self_intersects = self_intersects,
#                                   land_point = any_intersections_with_shoreline))
# }
```

The loop below evaluates based on points location, which may not be the best approach.

```{r}
# Initialize an empty dataframe to store results
# lines_check_df <- data.frame(boundary_name = character(),
#                                    area_name = character(),
#                                    self_intersects = logical(),
#                                    land_points = logical(),
#                                    stringsAsFactors = FALSE)
# 
# for (i in unique(rca_lines_sf$boundary_name)) {
#   # Filter lines by boundary name
#   line_vec <- rca_lines_sf %>% 
#     filter(boundary_name == i)
#   
#   point_vec <- rca_legis_points_df %>%
#     filter(boundary_name == i) %>% 
#     sf::st_as_sf(coords = c("lon", "lat"), crs = 4326)
#   
#   for (j in unique(line_vec$area_name)) {
#     # Filter lines by boundary name
#     line_unique_vec <- line_vec %>% 
#       filter(area_name == j)
#     
#     point_unique_vec <- point_vec %>% 
#       filter(area_name == j)
#     
#     # Self-intersection evaluation
#     ## Check each line for simplicity (i.e., it does not cross itself)
#     self_intersects <- !st_is_simple(line_unique_vec)
#     
#     # Inland points evaluation
#     ## Mainland
#     points_within <- suppressMessages(st_intersects(point_unique_vec, eez_poly))
#     is_within <- lengths(points_within) > 0
#     n_points_in_land <-sum(!is_within)
#     ## Islands
#     points_within <- suppressMessages(st_intersects(point_unique_vec, islands_poly))
#     is_within <- lengths(points_within) > 0
#     n_points_in_islands <- sum(is_within)
#     ## Sum
#     wrong_points <- n_points_in_land + n_points_in_islands
# 
#     # Append the results to the dataframe
#     lines_check_df <- rbind(lines_check_df,
#                             data.frame(
#                               boundary_name = i, 
#                               area_name = j,
#                               self_intersects = self_intersects,
#                               land_points = wrong_points))
#   }
# }
# 
# # Display the resulting dataframe
# head(lines_check_df)
```

The loop below evaluates by lines intersection with the shoreline instead of point based.

```{r}
# Initialize an empty dataframe to store results
lines_check_df <- data.frame(boundary_name = character(),
                                   area_name = character(),
                                   self_intersects = logical(),
                                   land_point = logical(),
                                   stringsAsFactors = FALSE)

for (i in unique(rca_lines_sf$boundary_name)) {
  # Filter lines by boundary name
  line_vec <- rca_lines_sf %>%
    filter(boundary_name == i)

  for (j in unique(line_vec$area_name)) {
    # Filter lines by boundary name
    line_unique_vec <- line_vec %>%
      filter(area_name == j)
    # Self-intersection evaluation
    ## Check each line for simplicity (i.e., it does not cross itself)
    self_intersects <- !st_is_simple(line_unique_vec)
    # Shoreline evaluation
    ## Check for intersections between the line and the shoreline
    intersections_with_shoreline <- suppressMessages(st_intersects(line_unique_vec, coastline))
    any_intersections_with_shoreline <- any(lengths(intersections_with_shoreline)>0)
    # Append the results to the dataframe
    lines_check_df <- rbind(lines_check_df,
                            data.frame(
                              boundary_name = i,
                              area_name = j,
                              self_intersects = self_intersects,
                              land_point = any_intersections_with_shoreline))
  }
}

# Display the resulting dataframe
head(lines_check_df)
```



There are `r sum(lines_check_df['land_points'] | lines_check_df['self_intersects'])` lines with errors.

Store the resulting dataframe into a formatted xlsx file.

```{r}
# SAVE intersection based approach
wb <- createWorkbook() # Create a new workbook
addWorksheet(wb, "Data") # Add a worksheet to the workbook
writeData(wb, "Data", lines_check_df) # Write your dataframe to the worksheet

# Define red font style
redFontStyle <- createStyle(fontColour = "#FF0000")

# Conditional formatting for 'land_points' or 'self_intersects' being TRUE
conditionalFormatting(wb, "Data", cols = 1:ncol(lines_check_df), rows = 2:(nrow(lines_check_df) + 1), rule = "ISNUMBER(SEARCH(\"TRUE\", INDIRECT(ADDRESS(ROW(),COLUMN()))))", style = redFontStyle)

# Save the workbook
saveWorkbook(wb, here("RCA_data_exploration/outputs/lines_check_shore_intersect.xlsx"), overwrite = TRUE)
```


```{r}
# SAVE point based approach
# wb <- createWorkbook() # Create a new workbook
# addWorksheet(wb, "Data") # Add a worksheet to the workbook
# writeData(wb, "Data", lines_check_df) # Write your dataframe to the worksheet
# 
# # Color in red those observations representing conflicted lines
# nrows <- nrow(lines_check_df)
# redFontStyle <- createStyle(fontColour = "#FF0000")
# # Apply conditional formatting
# for (i in 1:nrows) {
#   if (lines_check_df$land_points[i] || lines_check_df$self_intersects[i]) {
#     # Apply red font style to the entire row
#     addStyle(wb, "Data", style = redFontStyle, rows = i + 1, cols = 1:ncol(lines_check_df), gridExpand = TRUE)
#   }
# }
# 
# # Save the workbook
# saveWorkbook(wb, here("RCA_data_exploration/outputs/lines_check_land_points.xlsx"), overwrite = TRUE)
```

As seen from the generated XLSX file, there appear to be more geometries with errors than those included in the "rca_line_checking" sheet. This may explain the unexpected issues that could be causing mistakes in polygon generation. Below, we explore these identified incorrect geometries and discuss why they were not easily visually detected.

An example of this is the "75fm_070104.csv" file, which, upon inspection of the related JPG, does not seem to present any issues.

```{r}
# Filter observations where boundary_name is "75fm_070104.csv"
filtered_rca_lines_sf <- rca_lines_sf %>%
  filter(boundary_name == "75fm_070104.csv")
```

Let's run the individual functions to check for points inland and self-intersection.

```{r}
check_shoreline_intersections(filtered_rca_lines_sf)
check_self_intersections(filtered_rca_lines_sf)

# Check which object is affected
is_simple <- st_is_simple(filtered_rca_lines_sf)
filtered_rca_lines_sf[!is_simple, ]$area_name
```

From this analysis, it appears that the lines are self-intersecting, particularly the one related to Santa Catalina Island.

To further evaluate where the self-intersection is occurring, we can save the data as a shapefile and conduct the examination in QGIS, utilizing the "Check Geometries" plugin. Save the file and proceed to QGIS for the exploration.

```{r}
st_write(filtered_rca_lines_sf, here("RCA_data_exploration/line_shapefile.shp"))
```

The intersections seem to occur at the western vertex of the shape surrounding the island, where two nodes force that intersection.

### Next steps

The errors identified in the RCA lines impact only a limited number of lines, indicating that the primary cause of incorrect polygon generation is likely attributed to the polygon generation process itself. Regardless of this, the erroneous lines need to be assessed to inform NOAA, since ultimately represents a legislative issue concerning how areas are legally and geographically interpreted. Therefore, the subsequent steps will include:

- Plot the incorrect lines alongside the lines provided by NOAA, accessible at 'Master_line_feature_source'. Use Leaflet to enable a detailed examination of the lines.

- Programmatically compare the NOAA lines with our lines, initially focusing on those that exhibit issues before proceeding to assess the remaining lines.

## Polygons assessment

After visually inspecting the polygons generated from the polygonize.qmd and conducting tests in QGIS and R (though a tidy and functional version is not available), we've determined that the incorrect polygons mainly result from the generation process, rather than the presence of incorrect RCA lines—which are only a few. Through testing, it was seen that employing the entire EEZ as a polygon contributed to some issues. Also, small features in the shoreline may be interfering when splited. Additionally, problems were identified with isolines near the borders not intersecting the border lines precisely. 

As a first step, we separated the coastline from the rest of the EEZ and tested it with minor modifications to the original code. This approach prevented the generation of major incorrect areas in the southern section of the RCA areas but introduced new issues related to the shoreline of the Northern part. Consequently, we decided to recycle to the original code and explore a new approach as discussed in rca_poly_new_approach.qmd.

*Note: The shoreline files mentioned are stored in the 'spatial_ref_files' folder inside the 'Ruttenberg et al collaboration' directory in the DRIVE, and were generated from the original EEZ file included in polygonize.qmd using QGIS. These files were created by removing nodes not pertaining to the shoreline, such as the exterior EEZ border and the U.S. maritime border with Canada and Mexico. Several files with distinct features were created and stored as geojson.*

## Lines from NOAA

Lines facilitated by CalPoly are approved by NOAA, therefore we have decided to use them for the polygon generation instead of the previous ones. These lines where generated upt o 2022. For the rest we should use the original procedure.

```{r}

# Read the feature class
feature_class <- st_read(dsn = cal_poly_fp, layer = "Master_line_feature_source")

# Check the first few records to confirm
names(feature_class)

```


```{r}
# Use a regular expression to extract the date part (mmddyy) from the filenames
date_strings <- sub(".*_(\\d{4}\\d{2}).csv$", "\\1", feature_class$CoordFileName)

# Convert the extracted strings to date objects
# Note: The dates are in the format mmddyy, so we use the format "%m%d%y"
dates <- as.Date(date_strings, format = "%m%d%y")
standard_dates <- format(dates, "%Y-%m-%d")

min(na.omit(standard_dates))
max(na.omit(standard_dates))
```

We can see that the RCA lines available range from "2002-09-10" to "2021-03-16". Any date onwards will have to be generated from the original .csv files.

Now lets select only those objects corresponding to the longitude boundary lines (i.e., isobaths related)

```{r}
head(unique(feature_class$CoordFileName))

isolines <- feature_class %>% 
  filter(CoordFileName != "NA" & CoordFileName != "")

head(unique(isolines$CoordFileName))
```

It seems that for each unique CoordFileName there are several lines. Let's explore that.

```{r}
count_rows <- isolines %>%
  group_by(CoordFileName) %>%
  summarise(Count = n()) %>% 
  arrange(Count)

count_rows
```

explore in more detail an example line in QGIS
```{r}
isolines_selection <- isolines %>% 
  filter(CoordFileName == "10fm_010107.csv")

st_write(isolines_selection, here("RCA_data_exploration/line_shapefile.shp"))
```

After exploring it seems that each isoline is constituted by several segments. We'll have to potentially st_combine the lines. 






