---
format: html
editor_options: 
  chunk_output_type: console
---

# New approach for RCA polygon creation

## Setup

```{r}
if (!require(librarian,quietly = T)){
  install.packages('librarian')
}

librarian::shelf(
  here,
  # plotly,
  readxl,
  glue,
  tidyverse,
  lubridate,
  data.table,
  openxlsx,
  terra,
  leaflet,
  sf,
  openxlsx,
  rnaturalearth, 
  rnaturalearthdata,
  # foreach,
  # doParallel,
  iterators,
  quiet = T
)

sf_use_s2(FALSE)
```

```{r}
# Read in data using script (this helps keeping tidy the qmd)
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v4.R"))
source(here("RCA_data_exploration/scripts/generate_rca_objects.R"))
```

# Functions testing
## Testing for constant longitude lines

```{r}
eez_poly <-  st_read(here("RCA_data_exploration", "Ruttenberg et al collaboration", "spatial_ref_files", "eez.geojson"))

# The new approach considers the coastline independently than the EEZ
coastline <- st_read( here(data_path,"spatial_ref_files/all_shoreline_main_comb.geojson")) %>% 
  rename(
    land_ref = area_name,
    area_name = AreaType_2) %>% 
  mutate(
    boundary_type = "isobath",
    boundary_name = "shoreline")



# Update isolines form CalPoly gdb
feature_class <- st_read(dsn = cal_poly_fp, layer = "Master_line_feature_source")
isolines <- feature_class %>% 
  filter(CoordFileName != "NA" & CoordFileName != "")

split_isolines <- split(isolines, isolines$CoordFileName)

# function to apply the transformation
transform_isolines <- function(df) {
  df %>%
    st_combine() %>%
    st_as_sf() %>%
    st_set_geometry("geometry") %>%
    mutate(
      boundary_type = "isobath",
      boundary_name = first(df$CoordFileName),
      area_name = "not_defined",
      land_ref = "bathymetry",
      .before = geometry
    )
}

# Apply the transformation to each split dataframe and combine the results
new_isolines <- map_dfr(split_isolines, transform_isolines)

isolines_testing <- new_isolines %>% 
  filter(boundary_name == "150fm_012703.csv")

selected_longitude_lines <- rbind(isolines_testing, coastline)
```

```{r}
select_random_lat_boundaries <- function(data_frame) {
  # Extract unique boundary names
  unique_boundaries <- unique(data_frame$boundary_name)
  # Ensure that there are at least 2 unique boundaries to select from
  if(length(unique_boundaries) < 2) {
    stop("Not enough unique boundary names to select two random, non-equal values.")
  }
  # Randomly select two non-equal boundary names
  selected_boundaries <- sample(unique_boundaries, 2)
  # Filter rows that match the randomly selected boundary names
  selected_rows <- data_frame %>% 
    filter(boundary_name %in% selected_boundaries)
  return(selected_rows)
}

selected_latitude_lines <- select_random_lat_boundaries(n_s_boundaries_sf)


testing_poly <- rca_lines_to_polygons_v4(selected_longitude_lines,selected_latitude_lines,eez_poly)
```


1. Selecting inner polygons based on area can lead to issues in regions where land areas exceed water areas, particularly when the shoreline acts as a boundary. This situation is notable in Oregon, where large estuaries can cause the polygon generation process to incorrectly focus on land areas. For instance, for the file "150fm_012703.csv," the latitude limits of "43 20.83' N" and "46 16.00' N" exemplify this issue. Additional examples include the latitudinal ranges "42 40.50' N" to "45 46.00' N".

2. The execution of the random polygon generation script show further anomalies in shapes. However, these are likely due to the absence of a longitudinal lines at certain latitudes.

## Testing with all random lines

```{r}
select_random_lon_boundaries <- function(data_frame) {
  # Extract unique boundary names
  unique_boundaries <- unique(data_frame$boundary_name)
  # Ensure that there are at least 2 unique boundaries to select from
  if(length(unique_boundaries) < 2) {
    stop("Not enough unique boundary names to select two random, non-equal values.")
  }
  # Randomly select two non-equal boundary names
  selected_boundaries <- sample(unique_boundaries, 2)
  # Filter rows that match the randomly selected boundary names
  selected_rows <- data_frame %>% 
    filter(boundary_name %in% selected_boundaries)
  return(selected_rows)
}

selected_longitude_lines <- select_random_lon_boundaries(new_isolines)
selected_latitude_lines <- select_random_lat_boundaries(n_s_boundaries_sf)


testing_poly <- rca_lines_to_polygons_v3(selected_longitude_lines,selected_latitude_lines)
```


After some testing we detected that the islands are not clipped out if shoreline is not part of the boundary. (e.g., 36 00.00' N - U.S. EEZ Boundary South - 100fm_030104.csv - 150fm_010105.csv).


# Function implementation

## Input data

Althought this was already done in the testing section, we will include the read in code for the main object to be evaluated here as well.

```{r}
source(here("RCA_data_exploration/scripts/generate_rca_objects.R"))

# EEZ polygon, though it will only be used in v5 of the fuction exclusively applyed to those polygons neighboring the EEZ
eez_poly <-  st_read(here("RCA_data_exploration", "Ruttenberg et al collaboration", "spatial_ref_files", "eez.geojson"))

# Coastline shape that will define the shoreline layer as an extra isoline. As described earlier, the new approach considers the coastline independently than the EEZ
coastline <- st_read( here(data_path,"spatial_ref_files/all_shoreline_main_comb.geojson")) %>% 
  rename(
    land_ref = area_name,
    area_name = AreaType_2) %>% 
  mutate(
    boundary_type = "isobath",
    boundary_name = "shoreline") %>% 
  mutate(boundary_name = ifelse(boundary_name == "shoreline", # Matching with instructiosn df
                                "Shoreline",
                                boundary_name)) 

# RCA lines  form CalPoly gdb
feature_class <- st_read(dsn = cal_poly_fp, layer = "Master_line_feature_source")

isolines <- feature_class %>% 
  filter(CoordFileName != "NA" & CoordFileName != "") 
split_isolines <- split(isolines, isolines$CoordFileName)

transform_isolines <- function(df) {
  df %>%
    st_combine() %>%
    st_as_sf() %>%
    st_set_geometry("geometry") %>%
    mutate(
      boundary_type = "isobath",
      boundary_name = first(df$CoordFileName),
      area_name = "not_defined",
      land_ref = "bathymetry",
      .before = geometry
    )
}

new_isolines <- map_dfr(split_isolines, transform_isolines)

# Combine coastline with isolines to have them all in a single object
coastline <- st_transform(coastline, st_crs(new_isolines))
lon_boundary <-  rbind(coastline,new_isolines)

# Reference Cullen's sf with the latitudinal borders for each RCA
n_s_boundaries_sf <- st_transform(n_s_boundaries_sf, st_crs(new_isolines))
lat_boundary <- n_s_boundaries_sf
```


## Instructions dataframe

First we will create instructions data frame based on Cullen's code. Some updates need to be made so the instructions df contents matches the ones from the sf objects. The instructiins files contains the characteristcs of each resulting polygon which are the RCA date plus the lines references that contains them.

```{r}
## Create clean data frame of polygon metadata
polygon_instructions_df <- polygon_df_orig  %>% 
  dplyr::select(-completed)  %>% 
  dplyr::filter(shoreward_boundary != "N/A")  %>% 
  dplyr::mutate(
    shoreward_boundary = gsub("^0 fm \\(([^)]+)\\)$", "\\1", shoreward_boundary),
    southern_boundary = ifelse(southern_boundary == "U.S. EEZ Boundary", 
                               "U.S. EEZ Boundary South", 
                               southern_boundary),
    northern_boundary = ifelse(northern_boundary == "U.S. EEZ Boundary", 
                               "U.S. EEZ Boundary North", 
                               northern_boundary),
    northern_boundary = ifelse(northern_boundary == "U.S. EEZ boundary", 
                               "U.S. EEZ Boundary North", 
                               northern_boundary)) %>% 
  rename( lat_boundary1 = northern_boundary,
          lat_boundary2 = southern_boundary,
          lon_boundary1 = shoreward_boundary,
          lon_boundary2 = seaward_boundary)


# If we check the latitude variables levels we see an error where "45 46.00'N" should be "45 46.00' N"
unique(polygon_instructions_df$lat_boundary2)
# Update "45 46.00'N" to "45 46.00' N"
polygon_instructions_df <- polygon_instructions_df %>% 
  mutate(lat_boundary1 = ifelse(lat_boundary1 == "45 46.00'N",
                                "45 46.00' N",
                                lat_boundary1),
         lat_boundary2 = ifelse(lat_boundary2 == "45 46.00'N",
                                "45 46.00' N",
                                lat_boundary2))
```

Let's make sure the instructions contents are as we want.

```{r}
unique(polygon_instructions_df$lat_boundary1)
unique(polygon_instructions_df$lat_boundary2)
unique(polygon_instructions_df$lon_boundary1)
unique(polygon_instructions_df$lon_boundary2)
```

## Running for inner RCA

After some testing it has been seen that the problems associated with inner RCAs and those RCA neighboring the north and south limits of the EEZ are different, therefore two different function versions will be applied for each type of RCA.

After an initial run using v4 we got some issues associated with the lack of code dealing with the "no contact with border points" occurring in both latitude borders. This generated errors for the unique lines generated (i.e., `unique_geometries_sf`) in v4, objects 74, 75, 89, 97, 98, 99, 104. The same v4 function also generated and empty geometry for object 69, which we will discuss further.

We fixed this in v4.2. However additional problems where detected. These are related to an anomaly detected northwest of San Francisco, in front of the Greater Farallones National Marine Sanctuary, for the line "100fm_010107.csv". This anomaly occurred in both NOAA lines and our generated lines. There is a section where the line splits into two. Upon inspecting the line in more detail using QGIS, we can observe that this shape is composed of several redundant vertices.

```{r, echo = FALSE}
source(here("RCA_data_exploration/scripts/generate_rca_lines.R"))
filtered_rca_lines_sf <- rca_lines_sf %>%
  filter(boundary_name == "100fm_010107.csv")

filtered_rca_noaa_lines_sf <- new_isolines %>%
  filter(boundary_name == "100fm_010107.csv")
```

```{r, echo = FALSE}
leaflet() %>%
     addTiles() %>%
     addPolylines(data = filtered_rca_noaa_lines_sf, color = "orange", weight=2, group = "NOAA RCA line") %>%
     addPolylines(data = filtered_rca_lines_sf, color = "blue", weight=2, group = "emLab RCA line")%>%
  fitBounds(lng1 = -123.57, lat1 = 38.14, 
                    lng2 = -123.33, lat2 = 37.89) %>%
          addLegend(position = "topright", 
                    title = "100fm_010107.csv", 
                    opacity = 0, 
                    labels = "", 
                    colors = "transparent") %>% 
          addLayersControl(overlayGroups = c( "emLab RCA line", "NOAA RCA line"))
```

This is the cause of the 69 empty geometry and caused additional anomalies with the new code affecting 3 unique geometries and 24 total RCA polygons.  Since the error line is hard to interpret, and decisions will have to be made retarding the points that define it, we will exclude it until NOAA decides what to do with ti.

```{r}
intructions_sample <- polygon_instructions_df %>% 
  # Exclude EEZ boundaries
  filter(lat_boundary1 != "U.S. EEZ Boundary North",
         lat_boundary2 != "U.S. EEZ Boundary South") %>% 
  # Remove instructions where 100fm_010107.csv is a problem
  filter(!(lat_boundary1 == "40 10.00' N" &
           lat_boundary2 == "38 00.00' N" &
           lon_boundary1 == "100fm_010107.csv" &
           lon_boundary2 == "150fm_010107.csv")) %>%
  filter(!(lat_boundary1 == "38 00.00' N" &
           lat_boundary2 == "34 27.00' N" &
           lon_boundary1 == "100fm_010107.csv" &
           lon_boundary2 == "150fm_010107.csv")) %>%
   filter(!(lat_boundary1 == "40 10.00' N" &
           lat_boundary2 == "38 00.00' N" &
           lon_boundary1 == "100fm_010107.csv" &
           lon_boundary2 == "200fm_petrale_010107.csv"))
```

Once we have defined the instructions, we will apply v4.2 for al RCA of interest.

```{r}
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v4.2.R"))
```

```{r}
# Initialize list to store results
results <- list()
results_df <- data.frame(date = character(), area = character(), execution = logical(), stringsAsFactors = FALSE)

# Loop that evaluates each instruction line and applies v4.2 to it
for (i in 1:nrow(intructions_sample)) {
    # For each row in intructions_sample, extract the boundary names
    lat_boundary1_name <- intructions_sample$lat_boundary1[i]
    lat_boundary2_name <- intructions_sample$lat_boundary2[i]

    lon_boundary1_name <- intructions_sample$lon_boundary1[i]
    lon_boundary2_name <- intructions_sample$lon_boundary2[i] 

    # Select latitude lines
    selected_latitude_lines <- lat_boundary[lat_boundary$boundary_name == lat_boundary1_name, ] %>% 
      rbind(lat_boundary[lat_boundary$boundary_name == lat_boundary2_name, ])
    
    # Select longitude lines
    selected_longitude_lines <- lon_boundary[lon_boundary$boundary_name == lon_boundary1_name, ] %>% 
      rbind(lon_boundary[lon_boundary$boundary_name == lon_boundary2_name, ])
    
    # Process the selected lines to create polygons
    result <- suppressMessages(
      rca_lines_to_polygons_v4.2(selected_longitude_lines, selected_latitude_lines,eez_poly)
    )
    
    # Extracting boundary_name from each
    boundary_name_longitude1 = selected_longitude_lines$boundary_name[1] 
    boundary_name_longitude2 = selected_longitude_lines$boundary_name[2] 
    boundary_name_latitude1 = selected_latitude_lines$boundary_name[1] 
    boundary_name_latitude2 = selected_latitude_lines$boundary_name[2] 
    
    # Constructing the string with `glue`
    final_string <- glue("{lon_boundary1_name}-{lon_boundary2_name}-{lat_boundary1_name}-{lat_boundary2_name}")
    final_string <- gsub(" ", "", final_string)
    
    if (is.null(result) || all(st_is_empty(result))) {
        execution_status <- "empty geometry"
    } else {
        execution_status <- "successful"
    }
    
    print(paste0(as.character(intructions_sample$year_month[i]),"-", final_string, ": ",i,"/",nrow(intructions_sample),"...", execution_status))
    # Append to the results dataframe
    results_df <- rbind(results_df, data.frame(date = intructions_sample$year_month[i], area = final_string, execution = execution_status))
    
    # Combine polygons into a multipolygons and assign the instructions df variable levels
    combined_sf <- result %>% 
      st_combine() %>% 
      st_sf() %>% 
      cbind(intructions_sample[i,])
    
    # Store each result in the results list
    results[[i]] <- combined_sf
}

# Summary results
table(results_df$execution)
# Combine resulting list into a single sf object
combined_results_sf <- do.call(rbind, results)
# Export as a geopackage 
st_write(combined_results_sf, here("RCA_data_exploration","outputs","rca_poly","inner_rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```

Additionally, in order to visually explore the validity of the generated polygons, we can extract the unique polygons, which will consistently reduce the manual effort.

```{r}
combined_results_sf$geometry_wkt <- st_as_text(combined_results_sf$geometry)
unique_geometries_sf <- combined_results_sf %>%
  distinct(geometry_wkt, .keep_all = TRUE) %>%
  select(-geometry_wkt) %>% 
  st_as_sf()
```

```{r}
st_write(unique_geometries_sf, here("RCA_data_exploration","outputs","rca_poly","unique_inner_rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```



### testing function v4

```{r}
longitude_lines <- selected_longitude_lines
latitude_lines <- selected_latitude_lines

  # Clip RCA boundary lines based on latitude delimitation lines.
  ## Find min and max latitude values from latitude lines.
  coords = st_coordinates(st_geometry(latitude_lines))
  latitudes = coords[,2] # The latitude values are in the second column of 'coords'
  min_latitude = min(latitudes)
  max_latitude = max(latitudes)
  ## Create a bbox that will intersect the RCA lines.
  bbox <- st_as_sfc(st_bbox(c(xmin = -180, xmax = 180, 
                              ymin = min_latitude, ymax = max_latitude), 
                            crs = st_crs(longitude_lines)))
  
  # eez_poly <- st_polygonize(shoreline[2,]) %>% 
  #   st_collection_extract("POLYGON")
  
  # difference <- st_intersection(eez_poly,bbox)
  
  clipped_lines <- st_intersection(longitude_lines, bbox)
  
  MultilineFromIntersections <- function(latitude_lines, clipped_lines) {
    # Perform intersection
    coastline_intersect <- st_intersection(latitude_lines, clipped_lines)
    
    # Extract points from intersection geometries
    # print("Extracting points from intersection geometries")
    extract_points <- function(coastline_intersect) {
      # Extract points from intersection geometries
      all_points_list <- lapply(1:length(coastline_intersect$geometry), function(i) {
        geom <- coastline_intersect$geometry[i]
        # Extract coordinates depending on geometry type
        coords <- st_coordinates(geom)
        # Select only the X and Y columns
        coords_df <- data.frame(X = coords[, "X"], Y = coords[, "Y"])
        # Create an sf object of points for each geometry
        st_as_sf(x = coords_df, coords = c("X", "Y"), crs = st_crs(coastline_intersect))
      })
      
      points_sf <- do.call(rbind, all_points_list)
      return(points_sf)
    }
    
    # Combine all sf objects into one
    points_sf <- extract_points(coastline_intersect)
    
    # Evaluate cases where latitude borders are not intersected based on intersection points
    # print("Evaluating lack of intersections")
    
    ## Extract latitudes
    latitudes <- st_coordinates(points_sf)[,2]
    
    if (length(latitudes) %% 2 != 0 | !any(duplicated(latitudes))) {
      lat_counts <- table(latitudes)
      odd_even <- ifelse(lat_counts %% 2 == 1, "odd", "even")
      unique_lats <- unique(latitudes)
      ## Identify max and min latitude
      max_lat <- max(unique_lats)
      min_lat <- min(unique_lats)
      ## Check if max and/or min latitude have odd occurrences
      max_lat_odd <- odd_even[as.character(max_lat)] == "odd"
      min_lat_odd <- odd_even[as.character(min_lat)] == "odd"
      ## Get latitude border presenting the problem
      find_matching_latitude_indices <- function(sf_object, latitude) {
        
        row_indices <- points_sf %>%
          st_coordinates() %>%
          {which(.[, "Y"] == latitude, arr.ind = TRUE)}
        
        point_to_fix <- points_sf[row_indices,]
        
        matching_indices <- st_intersects(st_buffer(point_to_fix, 1e-6),sf_object) %>% 
          as.numeric()
        
        return(matching_indices)
      }
      
      # Below we solve the intersection issue on the border presenting the problem by searching the
      # nearest points between the lines
      # print("Lack of intersections detected. Solving problem...")
      process_latitude_lines <- function(latitude_lines, latitude) {
        ## Selecting latitude line affected
        matching_indices <- find_matching_latitude_indices(latitude_lines, latitude)
        selected_row <- latitude_lines[matching_indices,]
        ## Searching closest lines for all objects
        nearest_points <- st_nearest_points(longitude_lines,selected_row) %>%
          st_as_sf()
        
        lengths <- as.vector(st_length(nearest_points))
        # Filter out zero-length lines
        non_zero_lengths <- lengths[lengths > 0]
        # Find the shortest non-zero length
        shortest_non_zero_length <- min(non_zero_lengths)
        # Find the index(es) of the LINESTRING(s) with the shortest non-zero length
        shortest_index <- which(lengths == shortest_non_zero_length)
        # Select the shortest non-zero length LINESTRING from the collection
        shortest_line <- nearest_points[shortest_index, ]
        
        ## Add shortest line to our latitude line so intersection occurs
        latitude_intersect <- selected_row %>%
          st_union(shortest_line)
        ## Update latitude lines
        latitude_lines <- rbind(latitude_lines[-matching_indices,],
                                latitude_intersect %>% st_cast("LINESTRING"))
        return(latitude_lines)
      }
      
    
      
      # Now, we will evaluate the affected latitude lines and apply the fuctions defined above
      if (max_lat_odd & min_lat_odd) {
        # Both the maximum and minimum latitudes have an odd number of points
        updated_max_latitude_lines <- process_latitude_lines(latitude_lines, max_lat)
        
        is_max_lat_in_line <- function(line, max_lat) {
          coords <- st_coordinates(line)
          lat_min <- min(coords[,2])
          lat_max <- max(coords[,2])
          return(max_lat >= lat_min && max_lat <= lat_max)
        }
        
        # Apply the function to filter rows
        updated_max_latitude_lines_filtered <- updated_max_latitude_lines %>%
          filter(sapply(geometry, is_max_lat_in_line, max_lat = max_lat))

        
        updated_min_latitude_lines <- process_latitude_lines(latitude_lines, min_lat)
        
        is_min_lat_in_line <- function(line, min_lat) {
          coords <- st_coordinates(line)
          lat_min <- min(coords[,2])
          return(min_lat >= lat_min)
        }
        
        # Apply the function to filter rows
        updated_min_latitude_lines_filtered <- updated_min_latitude_lines %>%
          filter(sapply(geometry, is_min_lat_in_line, min_lat = min_lat)) 
        
        updated_latitude_lines <- rbind(updated_min_latitude_lines_filtered,
                                           updated_max_latitude_lines_filtered)
        
        ## Regenerate points_sf
        coastline_intersect <- st_intersection(updated_latitude_lines, clipped_lines)
        points_sf <- extract_points(coastline_intersect)

        
      } else if (max_lat_odd == TRUE & min_lat_odd == FALSE) { # The maximum latitude has an odd number of points
        updated_latitude_lines <- process_latitude_lines(latitude_lines, max_lat)
        ## Regenerate points_sf
        coastline_intersect <- st_intersection(updated_latitude_lines, clipped_lines)
        points_sf <- extract_points(coastline_intersect)
        
      } else if (min_lat_odd == TRUE & max_lat_odd == FALSE) { # The minimum latitude has an odd number of points.
        updated_latitude_lines <- process_latitude_lines(latitude_lines, min_lat)
        ## Regenerate points_sf
        coastline_intersect <- st_intersection(updated_latitude_lines, clipped_lines)
        points_sf <- extract_points(coastline_intersect)
        
      } else {
        # Do nothing if both counts are even
      }
    }
    
    
    # Once we have the intersection points in the latitude borders, we can transform them into lines
    # print("Transforming points into lines")
    ## Sort points by longitude to guaranty they construct according to the vertices to fill
    coords <- st_coordinates(points_sf)
    sorted_coords <- coords[order(coords[, 'X']), ]
    sorted_coords <- sorted_coords[order(sorted_coords[, 'Y']), ] # Get X sorting by each latitude value
    ## Recreate sorted points as an sf object
    sorted_points_sf <- st_sf(geometry = st_sfc(lapply(1:nrow(sorted_coords), function(i) {
      st_point(sorted_coords[i, ])
    }), crs = st_crs(points_sf)))
    ## Get updated coordinates after sorting
    coords <- st_coordinates(sorted_points_sf)
    ## Create LINESTRINGs from pairs of sorted points
    lines_list <- vector("list", length = nrow(sorted_points_sf) / 2) # Initialize
    for (i in seq(1, nrow(sorted_points_sf), by = 2)) {
      if (i < nrow(sorted_points_sf)) {
        lines_list[[i]] <- st_linestring(coords[i:(i+1), ])
      }
    }
    lines_list <- lines_list[!sapply(lines_list, is.null)]  # Filter out any NULL elements
    ## Combine into a single MULTILINESTRING
    multiline <- st_sfc(lines_list, crs = st_crs(points_sf))
    multiline_sf <- st_sf(geometry = multiline)
    
    return(multiline_sf)
  }
  
  lat_shorelines <- MultilineFromIntersections(latitude_lines, clipped_lines)
  # Create polygon from lines
  # print("Creating polygons from lines")
  ## Combine into a MULTILINESTRING
  multilinestring <- st_union(lat_shorelines$geometry)
  target_geometry <- clipped_lines %>%
    # filter(area_name == "mainland" & land_ref == "mainland") %>%
    .$geometry
  combined_geometry <- st_union(target_geometry, multilinestring)
  ## Update the geometry with the combined geometry
  # clipped_lines$geometry[clipped_lines$area_name == "mainland" & clipped_lines$land_ref == "mainland"] <- combined_geometry
  ## Polygonize the combined MULTILINESTRINGs
  polygon_sf <- st_combine(st_union(combined_geometry)) %>% 
    st_polygonize() %>% 
    st_collection_extract("POLYGON") %>% 
    st_as_sf() %>% 
    rename(geometry = x) %>% 
    mutate(id = row_number(),.before=geometry)
  
  # # Clip out any inner polygon
  # print("First inner polygons clip out")
  # # To do it we will evaluate relationships between polygons based on whether they intersect and then exclude the smaller polygons within those associations
  # ## Get information on intersection polygons
  # intersections <- st_intersects(polygon_sf, sparse = TRUE)
  # ## Get areas
  # print("1")
  # areas <- st_area(polygon_sf)
  # print("2")
  # area_df <- data.frame(area = areas)
  # print("3")
  # 
  # # area_df$id <- 1:nrow(area_df)
  # area_df$id <- as.numeric(rownames(area_df))
  # print("4")
  # 
  # keep_ids <- numeric()
  # print("5")
  # ## For each polygon, find the one with the biggest area among those it intersects with
  # for (i in 1:length(intersections)) {
  #   if(length(intersections[[i]]) > 0) {
  #     # Find the intersecting polygons and their areas
  #     intersecting_areas <- area_df[area_df$id %in% intersections[[i]], ]
  #     # Find the polygon(s) with the maximum area
  #     max_area_id <- intersecting_areas[which.max(intersecting_areas$area), "id"]
  #     # Add to keep_ids
  #     keep_ids <- unique(c(keep_ids, max_area_id))
  #   }
  # }
  # print("6")
  # ## Keep only the polygons with the largest area in their intersection groups
  # rca_coastline_polygons_filtered <- polygon_sf[keep_ids, ]
  
  # print("Generating outputs")
   leaflet() %>%
     addTiles() %>%
     addPolygons(data = polygon_sf, color = "red", weight=1) %>%
     addPolylines(data = selected_latitude_lines, color = "blue", weight=2) %>%
     addPolylines(data = clipped_lines, color = "orange", weight=2)

 
```

