---
format: html
editor_options: 
  chunk_output_type: console
---

# New approach for RCA polygon creation

## Setup


```{r}
if (!require(librarian,quietly = T)){
  install.packages('librarian')
}

librarian::shelf(
  knitr,
  here,
  readxl,
  glue,
  parallel,
  doParallel,
  tidyverse,
  lubridate,
  data.table,
  openxlsx,
  terra,
  leaflet,
  sf,
  openxlsx,
  rnaturalearth, 
  rnaturalearthdata,
  iterators,
  kableExtra,
  quiet = T
)

sf_use_s2(FALSE)
```

## Run the RCA creation function

### Read in data

The script that builds the RCA polygons relies on several objects created by Cullen. Below, we read those objects and adapt some others so that they can be processed by function v6.

```{r}
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v6.R"))
source(here("RCA_data_exploration/scripts/generate_rca_objects.R"))

# EEZ polygon, though it will only be used in v5 of the fuction exclusively applyed to those polygons neighboring the EEZ
eez_poly <-  st_read(here("RCA_data_exploration", "Ruttenberg et al collaboration", "spatial_ref_files", "eez.geojson"))

# Coastline shape that will define the shoreline layer as an extra isoline. As described earlier, the new approach considers the coastline independently than the EEZ
coastline <- st_read( here(data_path,"spatial_ref_files/all_shoreline_main_comb.geojson")) %>% 
  rename(
    land_ref = area_name,
    area_name = AreaType_2) %>% 
  mutate(
    boundary_type = "isobath",
    boundary_name = "shoreline") %>% 
  mutate(boundary_name = ifelse(boundary_name == "shoreline", # Matching with instructiosn df
                                "Shoreline",
                                boundary_name)) 

# RCA NOAA lines
feature_class <- st_read(dsn = cal_poly_fp, layer = "Master_line_feature_source")
isolines <- feature_class %>% 
  filter(CoordFileName != "NA" & CoordFileName != "") 
split_isolines <- split(isolines, isolines$CoordFileName)
transform_isolines <- function(df) {
  df %>%
    st_combine() %>%
    st_as_sf() %>%
    st_set_geometry("geometry") %>%
    mutate(
      boundary_type = "isobath",
      boundary_name = first(df$CoordFileName),
      area_name = "not_defined",
      land_ref = "bathymetry",
      .before = geometry
    )
}
new_isolines <- map_dfr(split_isolines, transform_isolines)

# Combine coastline with isolines to have them all in a single object
coastline <- st_transform(coastline, st_crs(new_isolines))
lon_boundary <-  rbind(coastline,new_isolines)

# Reference Cullen's sf with the latitudinal borders for each RCA
n_s_boundaries_sf <- st_transform(n_s_boundaries_sf, st_crs(new_isolines))
lat_boundary <- n_s_boundaries_sf
```


### Instructions dataframe

We will create an instructions data frame based on Cullen's code. Some updates need to be made so the contents of the instructions data frame match those from the `sf` objects. The instructions file contains the characteristics of each resulting polygon, which include the RCA date plus the line references that contain them.

```{r}
## Create clean data frame of polygon metadata
polygon_instructions_df <- polygon_df_orig  %>% 
  dplyr::select(-completed)  %>% 
  dplyr::filter(shoreward_boundary != "N/A")  %>% 
  dplyr::mutate(
    shoreward_boundary = gsub("^0 fm \\(([^)]+)\\)$", "\\1", shoreward_boundary),
    southern_boundary = ifelse(southern_boundary == "U.S. EEZ Boundary", 
                               "U.S. EEZ Boundary South", 
                               southern_boundary),
    northern_boundary = ifelse(northern_boundary == "U.S. EEZ Boundary", 
                               "U.S. EEZ Boundary North", 
                               northern_boundary),
    northern_boundary = ifelse(northern_boundary == "U.S. EEZ boundary", 
                               "U.S. EEZ Boundary North", 
                               northern_boundary)) %>% 
  rename( lat_boundary1 = northern_boundary,
          lat_boundary2 = southern_boundary,
          lon_boundary1 = shoreward_boundary,
          lon_boundary2 = seaward_boundary)

# If we check the latitude variables levels we see an error where "45 46.00'N" should be "45 46.00' N"
# unique(polygon_instructions_df$lat_boundary2)
# Update "45 46.00'N" to "45 46.00' N"
polygon_instructions_df <- polygon_instructions_df %>% 
  mutate(lat_boundary1 = ifelse(lat_boundary1 == "45 46.00'N",
                                "45 46.00' N",
                                lat_boundary1),
         lat_boundary2 = ifelse(lat_boundary2 == "45 46.00'N",
                                "45 46.00' N",
                                lat_boundary2))
```

### Running function

We run the function using parallel processing so that we can simultaneously construct several polygons, making use of most of our computational power and speeding up the process. The chunk below reads the instructions df for each RCA and generates the polygons.

```{r}
instructions_sample <- polygon_instructions_df
# Register parallel backend to use multiple cores
numCores <- detectCores() -1
registerDoParallel(cores = numCores)

# Initialize list to store results from each iteration
results <- list()

# Parallel loop using foreach.
results <- foreach(i = 1:nrow(instructions_sample), .packages = c("dplyr", "sf", "glue")) %dopar% {
  tryCatch({
  # Extracting boundary names
  lat_boundary1_name <- instructions_sample$lat_boundary1[i]
  lat_boundary2_name <- instructions_sample$lat_boundary2[i]
  lon_boundary1_name <- instructions_sample$lon_boundary1[i]
  lon_boundary2_name <- instructions_sample$lon_boundary2[i]

  # Selecting latitude and longitude lines
  selected_latitude_lines <- lat_boundary[lat_boundary$boundary_name == lat_boundary1_name, ] %>% 
    rbind(lat_boundary[lat_boundary$boundary_name == lat_boundary2_name, ])
  selected_longitude_lines <- lon_boundary[lon_boundary$boundary_name == lon_boundary1_name, ] %>% 
    rbind(lon_boundary[lon_boundary$boundary_name == lon_boundary2_name, ])

  # Process to create polygons
  result <- suppressMessages(
    rca_lines_to_polygons_v6(selected_longitude_lines, selected_latitude_lines, eez_poly)
  )
  
  combined_sf <- result %>% 
      st_combine() %>% 
      st_sf() %>% 
      cbind(instructions_sample[i,])

  # Return the sf object directly
  combined_sf
  
  }, error = function(e) {
      # Log or return the error along with the iteration number
      list(error = e, iteration = i)
    })
}

# Stop the cluster
stopImplicitCluster()
```


### Results

Results are stored in a list. Therefore, we must extract them and combine them into a single `sf` object.

```{r}
# Remove errors form output list
results_clean <- Filter(function(x) !is.list(x$error), results)
# Combine resulting list into a single sf object
combined_results_sf <- do.call(rbind, results_clean)
```

The resulting spatial object contains `r dim(combined_results_sf)[1]` polygons. However, it's important to note that some of these polygons may share the same geometry. If we wish to individually inspect the resulting shapes, it's convenient to exclude those polygons with repeated geometries.

```{r}
# Initialize a logical vector to mark duplicates; FALSE means no duplicate found yet
is_duplicate <- rep(FALSE, length(combined_results_sf))

# Loop over all geometries
for (i in 1:length(combined_results_sf$geometry)) {
  # Skip if this geometry has already been marked as a duplicate
  if (!is_duplicate[i]) {
    # Compare the current geometry with all others
    duplicates = sapply(combined_results_sf$geometry, function(x) identical(x, combined_results_sf$geometry[[i]]))
    # Mark duplicates, but keep the first occurrence
    is_duplicate <- is_duplicate | (duplicates & !is_duplicate)
    is_duplicate[i] <- FALSE  # Ensure the first instance is not marked as duplicate
  }
}

# Filter out duplicates
unique_geometries <- combined_results_sf[!is_duplicate, ]
unique_geometries <- unique_geometries %>% 
  select(!land_ref)
```

After performing this exclusion, we obtain `r dim(unique_geometries)[1]` unique geometries.

## Validation

### Unique identification

As highlighted above, it's important to distinguish between RCA polygons and unique polygons. A single area can represent different RCAs defined for various months and years. Although this may not be relevant for the method we will be using to store the resulting shapes, as described in the next section, any future attempts to tidy the storage and access of spatial data from a spatial database would benefit from adding unique tags to those existing unique polygons. Below, we propose such ID labeling scheme.

```{r}
generateUniqueID <- function(lat1, lat2, lon1, lon2) {
  # Convert latitude values
  convertLat <- function(lat) {
    if(lat == "U.S. EEZ Boundary North") return("N")
    if(lat == "U.S. EEZ Boundary South") return("S")
    parts <- unlist(strsplit(lat, "[^0-9]+"))
    paste0(parts[1], sprintf("%02d", as.integer(parts[2])))
  }
  
  # Convert longitude values
  convertLon <- function(lon) {
    if(lon == "Shoreline") return("0")
    if(grepl("fm", lon)) {
      return(sub("fm.*", "", lon))
    }
    return(lon)
  }
  
  lat1Converted <- convertLat(lat1)
  lat2Converted <- convertLat(lat2)
  lon1Converted <- convertLon(lon1)
  lon2Converted <- convertLon(lon2)
  
  paste(lat1Converted, lat2Converted, lon1Converted, lon2Converted, sep="_")
}
```

The above functions would transform an area constituted by borders such as `"45 46.00' N"`, `"U.S. EEZ Boundary South"`, `"100fm_010119.csv"`, and `"150fm_010119.csv"` into `r generateUniqueID("45 46.00' N", "U.S. EEZ Boundary South", "100fm_010119.csv", "150fm_010119.csv")`. Then, we will append a subindex letter to distinguish those unique geometries that share an ID scheme, and we will update all the resulting sf objects before exporting them.

```{r}
# Updated function to handle duplicates by appending letters from the start
handleDuplicates <- function(unique_ids) {
  letter_suffix <- letters
  count_table <- table(unique_ids)
  duplicated_ids <- names(count_table[count_table > 1])
  
  updated_ids <- unique_ids
  for(dup_id in duplicated_ids) {
    dup_indices <- which(unique_ids == dup_id)
    updated_ids[dup_indices] <- paste0(dup_id, letter_suffix[seq_along(dup_indices)])
  }
  return(updated_ids)
}

# Applying the functions to unique geometries sf object
processGeometries <- function(unique_geometries) {
  unique_geometries %>%
    rowwise() %>%
    mutate(uniqueRCAid = generateUniqueID(lat_boundary1, lat_boundary2, lon_boundary1, lon_boundary2)) %>%
    ungroup() %>%
    mutate(uniqueRCAid = handleDuplicates(uniqueRCAid)) %>%
    relocate(uniqueRCAid, .before = year_month)
}

unique_geometries_updated <- processGeometries(unique_geometries)

```

Once defined the polygons unique IDs, we will export them to all the RCAs for reference.

```{r}
no_cores <- detectCores() - 2

# Define a function to be parallelized
assign_ids <- function(i, combined_sf, unique_geometries_updated) {
  for (j in seq_len(nrow(unique_geometries_updated))) {
    if (isTRUE(any(st_equals(combined_sf$geometry[i], unique_geometries_updated$geometry[j])))) {
      return(unique_geometries_updated$uniqueRCAid[j])
    }
  }
  return(NA) # Return NA if no match is found
}

# Split the combined_results_sf into chunks to be distributed across cores
chunks <- split(seq_len(nrow(combined_results_sf)), ceiling(seq_len(nrow(combined_results_sf)) / no_cores))

# Use mclapply to apply the function in parallel
uniqueids <- mclapply(chunks, function(chunk) {
  sapply(chunk, assign_ids, combined_sf = combined_results_sf, unique_geometries_updated = unique_geometries_updated)
}, mc.cores = no_cores)

# Combine the results back into a single vector
combined_results_sf$uniqueRCAid <- unlist(uniqueids)
combined_results_sf<- combined_results_sf %>%
  relocate(uniqueRCAid, .before = year_month) %>% 
  select(!land_ref)
```

### Saving results

We will export the resulting spatial objects into Geopackage (GPKG) format, with one file containing all the RCAs and another file containing the unique areas. Each observation in the resulting files will be defined by `r length(names(combined_results_sf))` variables. Four of these defining the latitude and longitude borders of the polygon, also encapsulated in the fifth variable, the `uniqueRCAid`. Additionally, the variable `year_month` will inform on the date to which the RCA was in effect

```{r}
st_write(combined_results_sf, here("RCA_data_exploration","outputs","rca_poly","rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```

```{r}
st_write(unique_geometries, here("RCA_data_exploration","outputs","rca_poly","unique_rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```

### Errors evaluation

In line with the report, several incorrect features have been detected when analyzing the RCA lines and polygons. While the script processing the lines and generating the polygons handles most of the exceptions and potential errors derived from incorrect lines, some other lines prevented the proper generation of the polygons. Below, we analyze such polygon errors and discuss their causes.

```{r}
# Extract errors and their iterations into a list
errors_list <- lapply(results, function(x) {
  if (is.list(x) && !is.null(x$error)) {
    return(list(error_message = as.character(x$error$message), iteration = x$iteration))
  } else {
    return(NULL)
  }
})

errors_list <- Filter(Negate(is.null), errors_list)
iterations_vector <- sapply(errors_list, function(x) x$iteration)
incorrect_lines <- instructions_sample[iterations_vector,] %>%
  group_by(land_ref, lat_boundary1, lat_boundary2, lon_boundary1, lon_boundary2) %>%
  slice(1) %>%
  ungroup()
```

Based on the code errors, there are `r dim(incorrect_lines)[1]` unique incorrect areas, corresponding to `r dim(instructions_sample[iterations_vector, ])[1]` RCA polygons. The details of these unique incorrect areas are provided below.

```{r}
kable(incorrect_lines[,-c(1,2)]) %>% 
  kable_styling("striped")
```

Three errors are associated with the line error for "100fm_010107.csv" as described in the lines report. The fourth error, related to "100fm_091002.csv," is due to the line ending well before the northern border. The code is designed to handle the absence of intersections with latitude borders when these are separated by distances of less than a few meters. However, for this line, the distance is larger than usual, and any extrapolation without a defined criteria could result in substantial area modification. Therefore, it requires review.

Additionally, we will evaluate whether any of the generated areas yield an empty geometry. As observed, this is the case for areas including the northern end of line "50fm_052803.csv," which presents an error already described in the lines report.

```{r}
# Filter for items with empty geometries
items_with_empty_geometry <- combined_results_sf %>% 
  filter(sapply(st_geometry(.), function(g) any(st_is_empty(g))))

combined_df_with_empty_geometries <- items_with_empty_geometry %>%
  st_set_geometry(NULL) %>%
  bind_rows()

unique_land_refs <- combined_df_with_empty_geometries %>%
  distinct(uniqueRCAid, .keep_all = TRUE) %>%
  select(lat_boundary1, lat_boundary2, lon_boundary1, lon_boundary2)

kable(unique_land_refs[,-1]) %>% 
  kable_styling("striped")
```

The line in "50fm_052803.csv" intersects with the shoreline at its northern end. Currently, the code is not ready to handle the inclusion of a third longitudinal line border, in this case, the shoreline, when defining the RCA. If this shoreline should not be included, then the issue becomes similar to that for "50fm_052803.csv," where a significant distance from the northern border is not extrapolated to prevent modifications to the area. A decision needs to be made regarding the validity of this line, as an intersection with the shoreline is not logical.

To sum up, there are `r dim(incorrect_lines)[1] + dim(unique_land_refs)[1]` unique areas, corresponding to `r dim(instructions_sample[iterations_vector, ])[1] + dim(combined_df_with_empty_geometries)[1]` RCA polygons, that shows errors. These errors must be addressed and resolved before generating any final associated RCA.

### Polygons inspection

```{r}
unique_areas <- read_geometries <- st_read(dsn = here("RCA_data_exploration", "outputs", "rca_poly", "unique_rca_polygons.gpkg"), layer = "polygons_layer")
```

```{r}
display_polygons_one_by_one <- function(sf_object) {
  for (i in 1:nrow(sf_object)) {
    # Extract the current polygon
    current_polygon <- sf_object[i, ]
    
    # Extracting boundary names
    lat_boundary1_name <- current_polygon$lat_boundary1
    lat_boundary2_name <- current_polygon$lat_boundary2
    lon_boundary1_name <- current_polygon$lon_boundary1
    lon_boundary2_name <- current_polygon$lon_boundary2
  
    # Selecting latitude and longitude lines
    selected_latitude_lines <- lat_boundary[lat_boundary$boundary_name == lat_boundary1_name, ] %>% 
      rbind(lat_boundary[lat_boundary$boundary_name == lat_boundary2_name, ])
    selected_longitude_lines <- lon_boundary[lon_boundary$boundary_name == lon_boundary1_name, ] %>% 
      rbind(lon_boundary[lon_boundary$boundary_name == lon_boundary2_name, ])
    
    # Get min and max latitude 
    coords <- do.call(rbind, lapply(current_polygon$geom, function(g) {
      st_coordinates(g)
    }))
    min_latitude <- min(coords[,2])
    max_latitude <- max(coords[,2])
    min_longitude <- min(coords[,1])
    max_longitude <- max(coords[,1])
    
    # Create a leaflet map and add the current polygon
    map <- leaflet() %>%
      addTiles() %>%
      addPolygons(data = current_polygon, color = "red", weight=1) %>%
      addPolylines(data = selected_latitude_lines, color = "blue", weight=2) %>%
      addPolylines(data = selected_longitude_lines, color = "orange", weight=2) %>% 
      fitBounds(lng1 = min_longitude, lat1 =  max_latitude,
                lng2 = max_longitude, lat2 = min_latitude) %>% 
      addLegend(position = "topright",
                title = paste(lat_boundary1_name,"<br>",
                              lat_boundary2_name,"<br>",
                              lon_boundary1_name,"<br>",
                              lon_boundary2_name,"<br>",
                              " (",i,"/",nrow(sf_object),")"), 
                opacity = 0, 
                labels = "", 
                colors = "transparent")

    print(map)
    
    # Print the map
    print(map)
    
    # Wait for user input to continue
    cat("Press Enter to display the next polygon, or type 'quit' to stop: ")
    answer <- readline()
    
    # Break the loop if the answer is 'quit'
    if (tolower(answer) == "quit") {
      break
    }
  }
}

empty_geoms <- st_is_empty(unique_areas)
unique_areas_non_empty <- unique_areas[!empty_geoms, ]
display_polygons_one_by_one(unique_areas_non_empty)
```


