---
format: html
editor_options: 
  chunk_output_type: console
---

# New approach for RCA polygon creation

## Setup

```{r}
if (!require(librarian,quietly = T)){
  install.packages('librarian')
}

librarian::shelf(
  here,
  # plotly,
  readxl,
  tidyverse,
  lubridate,
  data.table,
  openxlsx,
  terra,
  leaflet,
  sf,
  openxlsx,
  rnaturalearth, 
  rnaturalearthdata,
  # foreach,
  # doParallel,
  iterators,
  quiet = T
)

sf_use_s2(FALSE)
```

## Read in data

```{r}
# Read in data using script (this helps keeping tidy the qmd)
source(here("RCA_data_exploration/scripts/generate_rca_objects.R"))
```

## Prepare testing data

```{r}
# Read in data
## From the original Cullen's code. If rca_lines_sf not available, run polygonize.qmd
longitude_lines <- rca_lines_sf
## Latitude lines
### Can be extracted from the n_s_boundaries_sf object from Cullen's code.
### For individual testing purposes here we will limit the lines to two.
latitude_lines <- n_s_boundaries_sf %>% 
  filter(boundary_name %in% c(#"34 27.00' N", 
                              "36 00.00' N"))
### Alternatively we can generate custom lines, to have more exploratory capacity through this approach testing
longitude_start = -130.36
longitude_end = -117.36
constant_latitude = 34.15
horizontal_line = st_sfc(st_linestring(matrix(c(longitude_start, constant_latitude, longitude_end, constant_latitude), ncol = 2, byrow = TRUE)), crs = 4326)
horizontal_line_sf <- st_sf(geometry = horizontal_line) %>% 
  mutate(boundary_type = "latitude",
         boundary_name = "34.17",
         area_name = "34.17",
         land_ref = "mainland",
         geometry = geometry )

latitude_lines <- rbind(horizontal_line_sf,latitude_lines)

# Select two lines from each object
selected_longitude_lines <- longitude_lines[c(10,105), ]
selected_latitude_lines <- latitude_lines
```

## New approach pipelane.

```{r}
rca_lines_to_polygons_v1 <- function(longitude_lines, latitude_lines) {
    
  # Clip RCA boundary lines based on latitude delimitation lines.
  ## Find min and max latitude values from latitude lines.
  coords = st_coordinates(st_geometry(latitude_lines))
  latitudes = coords[,2] # The latitude values are in the second column of 'coords'
  min_latitude = min(latitudes)
  max_latitude = max(latitudes)
  ## Create a bbox that will intersect the RCA lines.
  bbox <- st_as_sfc(st_bbox(c(xmin = -180, xmax = 180, 
                              ymin = min_latitude, ymax = max_latitude), 
                            crs = st_crs(longitude_lines)))
  clipped_lines <- st_intersection(longitude_lines, bbox)
  print(clipped_lines)
  
  # NOTE: depending on the region the previous clip can generate MULTILINESTRING, instead of simple LINESTRING. This is due, for example, to the existence of islands.
  
  # Below we convert MULTILINESTRING to multiple LINESTRINGs with independent iteration numbers per boundary_name. This is important as later, we will need to associate strings by iterations.
  expanded_clipped_lines <- function(sfc) {
    expanded_features <- list()
    boundary_counters <- list() # To store counters for each boundary_name
    
    for (i in seq_len(nrow(sfc))) {
      feature <- sfc[i, ]
      geometry <- st_geometry(feature)
      boundary_name <- feature$boundary_name
      
      ## Initialize or increment the counter for the current boundary_name
      if (!boundary_name %in% names(boundary_counters)) {
        boundary_counters[[boundary_name]] <- 1 # Initialize if not present
      } else {
        boundary_counters[[boundary_name]] <- boundary_counters[[boundary_name]] + 1 # Increment if already present
      }
      
      if (inherits(geometry, "sfc_MULTILINESTRING")) {
        linestrings <- st_cast(geometry, "LINESTRING")
        
        for (j in seq_len(length(linestrings))) {
          new_feature <- feature
          st_geometry(new_feature) <- linestrings[j]
          new_feature$iteration <- boundary_counters[[boundary_name]] # Set iteration number from boundary-specific counter
          expanded_features[[length(expanded_features) + 1]] <- new_feature
          boundary_counters[[boundary_name]] <- boundary_counters[[boundary_name]] + 1 # Increment for next linestring
        }
      } else {
        feature$iteration <- boundary_counters[[boundary_name]] # Set iteration for original linestrings
        expanded_features[[length(expanded_features) + 1]] <- feature
      }
    }
    
    do.call(rbind, expanded_features)
  }
  
  # Apply the function to the clipped RCA lines
  expanded_clipped_lines <- expanded_clipped_lines(clipped_lines)
  print(expanded_clipped_lines)
  
  
  # NOTE: In some cases the latitude lines can generate two or more independent polygons. As a result we need to treat each o the generated lines associated with those polygons independently. Besides, to facilitate the polygon generation, the nodes coordinates stored in the geometry variable must follow a certain order. The code below, takes one of the two associated lines of the polygon and reverse the coordinates sequence.
  
  # The following code does that for each unique iteration (i.e. for each independent polygon). Here we are assuming that polygons can originate from one or two lines. (TO BE CONFIRMED)
  unique_iterations <- unique(expanded_clipped_lines$iteration)
  ## Loop through each unique iteration number
  for(iteration in unique_iterations) {
    # Filter lines by iteration number
    lines_in_iteration <- expanded_clipped_lines[expanded_clipped_lines$iteration == iteration, ]
    # Check if there are at least two lines to work with
    if(nrow(lines_in_iteration) > 1) {
      # Select the second line
      geom <- st_geometry(lines_in_iteration)[[2]]
      # Perform the reversing procedure on this second line
      coords <- st_coordinates(geom)
      reversed_coords <- coords[nrow(coords):1, ][,1:2]
      reversed_linestring <- st_linestring(as.matrix(reversed_coords))
      reversed_geom <- st_sfc(reversed_linestring, crs = 4326)
      # Update the original sf object
      which_to_replace <- which(expanded_clipped_lines$iteration == iteration)[2]
      st_geometry(expanded_clipped_lines)[which_to_replace] <- reversed_geom
    }
  }
  print(expanded_clipped_lines)
  
  # Now it is the moment to combine strings by iteration value
  sf_data_combined <- expanded_clipped_lines %>%
    group_by(iteration) %>%
    summarize(
      geometry = st_combine(geometry),
      ## VARIABLE VALUES MUST BE RETHINKED
      boundary_type = paste(unique(boundary_type), collapse=", "),
      boundary_name = paste(unique(boundary_name), collapse=", "),
      area_name = paste(unique(area_name), collapse=", "),
      land_ref = paste(unique(land_ref), collapse=", "),
      .groups = 'drop') %>%
    mutate(geometry = st_cast(geometry, "MULTILINESTRING"))
  
  # Finally the function below will generate the polygon or polygons based on each existing row in the sf, converting the MULTILINESTRING into a POLYGON
  line_to_polygon <- function(line) {
    # Extract coordinates
    coords <- st_coordinates(line) 
    coords <- coords[,1:2]
    # Ensure the polygon is closed by repeating the first point at the end if necessary
    if (!identical(coords[1,], coords[nrow(coords),])) {
      coords <- rbind(coords, coords[1,])
    }
    # Create a POLYGON from coordinates
    polygon <- st_polygon(list(coords))
    return(polygon)
  }
  
  # Apply the function to each MULTILINESTRING in the expanded_clipped_lines object
  polygons <- st_sfc(lapply(sf_data_combined$geometry, line_to_polygon), crs = st_crs(sf_data_combined))
  # Create a new sf object for the  polygons
  polygon_sf <- st_sf(data.frame(id = 1:length(polygons)), geometry = polygons)
  print(polygon_sf)
  
  # Visualize in leaflet to explore result
  map <- leaflet() %>%
    addTiles() %>%
    addPolygons(data = polygon_sf, color = "red", weight=0) %>% 
    addPolylines(data = expanded_clipped_lines, color = "red", weight=1) %>% 
    addPolylines(data = selected_latitude_lines, color = "blue", weight=2)
  
  print(map)
  
  return((polygon_sf))
}
```

```{r}
rca_polygons <- rca_lines_to_polygons_v1(selected_longitude_lines, selected_latitude_lines)
```

## Testing results

So far, this approach was successfully tested under three different conditions:

1. Isobath to isobath (II) simple clip: This occurs when two isobaths are intersected by the latitude lines in a section where the resulting area forms a single polygon. This case was successfully implemented using Cullen's code. To view the results, test the code by assigning a constant_latitude = 34.27.

2. II complex clip: This arises when the two isobaths are intersected and one or both generate spatially independent clips. This can lead to the creation of two or more separate polygons originating from one or two lines, adding complexity to the polygon generation process. This may be the cause of the shape issues detected with the previous code. To view the results, test the code by assigning a constant_latitude = 34.17.

3. II simple or complex clip beyond borders: Although not all of them, some of the isobaths may have endpoints that do not intersect with the latitude delimitation lines. As observed in the previous code, this could result in anomalies when using the entire EEZ line. Despite not utilizing the EEZ in this approach, the methods have been tested against these conditions, and the results are good. To view the results, test the code by assigning a constant_latitude = 32.27.

## Next steps

1. Include meta data to the resulting polygon.
2. Investigate why some isolines are absent for the islands. For instance, with the tested isobaths used here, the Channel Islands do not have the shallowest one, causing the RCA to extend over land. This could be easily solved by clipping out the islands' shape, but then the RCA around the area would not accurately represent the area between isolines but between an isoline and the shoreline.
3. Test methods against mainland coastlines.
4. Test methods against islands.
5. Run the code at higher latitudes where estuaries add complexity to the coastline.

NOTE: Santa Rosa Island shoreline file has an error related to MULTILINESTRING coordinates order.

## Testing Coastline

As we can see if we run the script for coastline-isobath lines, the polygons are generated correctly. However, while mainland is automatically discarded, islands shores are considered part of that polygon as well. This needs to be fixed.

Potential solutions: (1) the easy way would be to clip out the islands after the analysis. (2) include a subroutine in the script to prevent that. Below we develop the second approach.

*NOTE: Shoreline files stored at spatial_ref_files have been generated from the EEZ file used in 'polygonize.qmd' using QGIS.*

```{r}
# Read in data
# The new approach considers the coastline independently than the EEZ
coastline <- st_read( here(data_path,"spatial_ref_files/all_shoreline_main_comb.geojson")) %>% 
  rename(
    land_ref = area_name,
    area_name = AreaType_2) %>% 
  mutate(
    boundary_type = "isobath",
    boundary_name = "shoreline")

```

```{r}
# Alternative shoreline files for testing purposes

# coastline <- st_read( here(data_path,"spatial_ref_files/mainland_shore.geojson")) |>
#   sf::st_as_sf() |>
#   tidyr::replace_na(replace = list(Name = "Shoreline")) |>
#   dplyr::group_by(AreaType) |>
#   dplyr::summarize(geometry = sf::st_union(geometry)) |>
#   dplyr::mutate(
#     boundary_type = "isobath",
#     boundary_name = "shoreline",
#     area_name = "shoreline",
#     land_ref = ifelse(AreaType == "islands", "islands", "mainland")) |>
#   dplyr::select(boundary_type, boundary_name, area_name, land_ref, geometry)

# coastline <- st_read( here("rca-database/spatial_ref_files/all_shoreline_not_comb.geojson")) %>% 
#   rename(
#     land_ref = area_name) %>% 
#   sf::st_as_sf() |>
#   dplyr::group_by(land_ref) |>
#   dplyr::summarize(geometry = sf::st_union(geometry)) |> 
#   mutate(
#     boundary_type = "isobath",
#     boundary_name = "shoreline",
#     area_name = ifelse(land_ref == "mainland", "mainland", "islands"))

# coastline <- st_read( here("rca-database/spatial_ref_files/all_shoreline.geojson")) |>
#   sf::st_as_sf() |>
#   tidyr::replace_na(replace = list(Name = "Shoreline")) |>
#   dplyr::group_by(AreaType) |>
#   dplyr::summarize(geometry = sf::st_union(geometry)) |>
#   dplyr::mutate(
#     boundary_type = "isobath",
#     boundary_name = "shoreline",
#     area_name = "shoreline",
#     land_ref = ifelse(AreaType == "islands", "islands", "mainland")) |>
#   dplyr::select(boundary_type, boundary_name, area_name, land_ref, geometry)
```

```{r}
### Alternatively we can generate custom lines, to have more exploratory capacity through this approach testing
longitude_start = -130.36
longitude_end = -110.36
constant_latitude = 33.00
horizontal_line = st_sfc(st_linestring(matrix(c(longitude_start, constant_latitude, longitude_end, constant_latitude), ncol = 2, byrow = TRUE)), crs = 4326)
horizontal_line_sf <- st_sf(geometry = horizontal_line) %>%
  mutate(boundary_type = "latitude",
         boundary_name = "34.17",
         area_name = "34.17",
         land_ref = "mainland",
         geometry = geometry )

latitude_lines <- rbind() # reset
latitude_lines <- n_s_boundaries_sf %>%
  filter(boundary_name %in% c(#"34 27.00' N",
                              "36 00.00' N"))

# latitude_lines <- rbind() # reset
# latitude_lines <- n_s_boundaries_sf %>%
#   filter(boundary_name %in% c("34 27.00' N",
#                               # "U.S. EEZ Boundary South"
#                               ))

latitude_lines <- rbind(horizontal_line_sf,latitude_lines)

# Select two lines from each object
selected_longitude_lines <- rbind(longitude_lines[105, ], coastline)
selected_latitude_lines <- latitude_lines
```

```{r}
rca_coastline_polygons <- rca_lines_to_polygons_v1(selected_longitude_lines, selected_latitude_lines)
```

Below we have the code to extract the islands from the final file. This is important, so later we can associate geographical metadata to each polygon, such as area or perimeter length.

```{r}
st_is_valid(rca_coastline_polygons)
rca_coastline_polygons <- st_make_valid(rca_coastline_polygons)

# Calculate the 'within' relationships using st_within
within_matrix <- st_within(rca_coastline_polygons, rca_coastline_polygons, sparse = TRUE)
# Convert the sparse matrix to a regular matrix
regular_matrix <- as.matrix(within_matrix)
# Now, find the indices of polygons that contain other polygons by checking
# where the row sum is greater than 1 (indicating containment beyond just itself)
outer_polygons_indices <- which(colSums(regular_matrix) > 1)
rca_coastline_polygons_clean <- st_difference(rca_coastline_polygons[outer_polygons_indices, ],
                                              st_combine(rca_coastline_polygons[-outer_polygons_indices, ]))

 leaflet() %>%
    addTiles() %>%
    addPolygons(data = rca_coastline_polygons_clean, color = "red", weight=1) %>% 
    addPolylines(data = selected_latitude_lines, color = "blue", weight=2)
```


## Solving geometry error

Above, we successfully generated RCA polygons in relatively simple scenarios concerning the complexity and relationships of associated lines through polygon generation. In this section, we evaluated two complex problems and successfully resolved them.

1. Isobath/Shoreline Latitude Split: Despite the west coast's predominantly N-S direction, latitude lines can divide isobaths or the shoreline into multiple segments. This can result in incorrect polygon geometries, with nodes not arranged in spatial order. An example is the latitude line at 34º17', which divides the SB coast into multiple segments. Although there is no RCA latitude border intersecting the islands, this also can create irregular shapes when forcing island intersection. Error example below:


2. Shoreline 'MULTILINESTRING' Structure: The shoreline file consists of various linestring objects, including natural shorelines, wetlands, estuaries, and human-made structures like harbors, piers, and breakwaters. These are sometimes isolated from the main shape. Generally, splitting the shoreline file by latitude lines does not cause errors. However, if the split affects any of these isolated objects, it can disrupt node order and lead to unexpected polygonal features.

The function below constitutes the 2.0 version allowing to generate polygons in the two cases described above.

```{r}
rca_lines_to_polygons_v2 <- function(longitude_lines, latitude_lines) {
    
  # Clip RCA boundary lines based on latitude delimitation lines.
  ## Find min and max latitude values from latitude lines.
  coords = st_coordinates(st_geometry(latitude_lines))
  latitudes = coords[,2] # The latitude values are in the second column of 'coords'
  min_latitude = min(latitudes)
  max_latitude = max(latitudes)
  ## Create a bbox that will intersect the RCA lines.
  bbox <- st_as_sfc(st_bbox(c(xmin = -180, xmax = 180, 
                              ymin = min_latitude, ymax = max_latitude), 
                            crs = st_crs(longitude_lines)))
  clipped_lines <- st_intersection(longitude_lines, bbox)
  print(clipped_lines)
  
  MultilineFromIntersections <- function(lat_line, clipped_lines) {
    # Perform intersection
    coastline_intersect <- st_intersection(lat_line, clipped_lines)
    
    # Extract points from intersection geometries
    all_points_list <- lapply(1:length(coastline_intersect$geometry), function(i) {
      geom <- coastline_intersect$geometry[i]
      # Extract coordinates depending on geometry type
      coords <- st_coordinates(geom)
      # Select only the X and Y columns
      coords_df <- data.frame(X = coords[, "X"], Y = coords[, "Y"])
      # Create an sf object of points for each geometry
      st_as_sf(x = coords_df, coords = c("X", "Y"), crs = st_crs(coastline_intersect))
    })
    
    # Combine all sf objects into one
    points_sf <- do.call(rbind, all_points_list)
    
    # Sort points by longitude (X coordinate)
    coords <- st_coordinates(points_sf)
    sorted_coords <- coords[order(coords[, 'X']), ]
    sorted_coords <- sorted_coords[order(sorted_coords[, 'Y']), ]
  
    
    # Recreate sorted points as an sf object
    sorted_points_sf <- st_sf(geometry = st_sfc(lapply(1:nrow(sorted_coords), function(i) {
      st_point(sorted_coords[i, ])
    }), crs = st_crs(points_sf)))
    
    # Get updated coordinates after sorting
    coords <- st_coordinates(sorted_points_sf)
    
    # Initialize an empty list for line segments
    lines_list <- vector("list", length = nrow(sorted_points_sf) / 2)
    
    # Create LINESTRINGs from pairs of sorted points
    for (i in seq(1, nrow(sorted_points_sf), by = 2)) {
      if (i < nrow(sorted_points_sf)) {
        lines_list[[i]] <- st_linestring(coords[i:(i+1), ])
      }
    }
    
    # Filter out any NULL elements
    lines_list <- lines_list[!sapply(lines_list, is.null)]
    
    # Combine into a single MULTILINESTRING
    multiline <- st_sfc(lines_list, crs = st_crs(points_sf))
    
    # Store the MULTILINESTRING in an sf object
    multiline_sf <- st_sf(geometry = multiline)
    
    return(multiline_sf)
  }
  
  lat_shorelines <- MultilineFromIntersections(selected_latitude_lines, clipped_lines)
  
  
  ### Add to multilinestring mainland
  
  multilinestring <- st_union(lat_shorelines$geometry)
  
  target_geometry <- clipped_lines %>%
    filter(area_name == "mainland" & land_ref == "mainland") %>%
    .$geometry
  
  combined_geometry <- st_union(target_geometry, multilinestring)
  
  
  # Update the geometry in `selected_longitude_lines` with the combined geometry
  clipped_lines$geometry[clipped_lines$area_name == "mainland" & clipped_lines$land_ref == "mainland"] <- combined_geometry
  
  polygon_sf <- st_combine(st_union(clipped_lines)) %>% 
    st_polygonize() %>% 
    st_collection_extract("POLYGON") %>% 
    st_as_sf() %>% 
    rename(geometry = x) %>% 
    mutate(id = row_number(),.before=geometry)
  
    
  map <- leaflet() %>%
      addTiles() %>%
      addPolygons(data = polygon_sf[1,], color = "red", weight=1) %>% 
      addPolylines(data = selected_latitude_lines, color = "blue", weight=2)
  
  print(map)
  return(polygon_sf)
}
```

Testing validity below.

```{r}
constant_latitude = 33.80
horizontal_line = st_sfc(st_linestring(matrix(c(longitude_start, constant_latitude, longitude_end, constant_latitude), ncol = 2, byrow = TRUE)), crs = 4326)
horizontal_line_sf <- st_sf(geometry = horizontal_line) %>%
  mutate(boundary_type = "latitude",
         boundary_name = "34.17",
         area_name = "34.17",
         land_ref = "mainland",
         geometry = geometry )


latitude_lines <- rbind() # reset 
latitude_lines <- n_s_boundaries_sf %>% 
  filter(boundary_name %in% c(#"36 00.00' N"
                              "34 27.00' N"
                              ))

latitude_lines <- rbind(horizontal_line_sf,latitude_lines)

# Select two lines from each object
selected_longitude_lines <- rbind(longitude_lines[105, ], coastline)
selected_latitude_lines <- latitude_lines


testing_poly <- rca_lines_to_polygons_v2(selected_longitude_lines,selected_latitude_lines)
```

## US Border issues (IN PROGRESS)

It seems that some isolines do not intersect with the borders. Therefore, the updated approach that resolved the previous issues cannot be applied in this context. To solve this we have updated the script so it assesses whether there are missing intersection points between latitude and longitude lines. If a missing point exist, then it searches for the closes distance between lines and fills the gap.

Below you have the updated function, which was tested for the southern borther.

```{r}
rca_lines_to_polygons_v3 <- function(longitude_lines, latitude_lines) {


  # Clip RCA boundary lines based on latitude delimitation lines.
  ## Find min and max latitude values from latitude lines.
  coords = st_coordinates(st_geometry(latitude_lines))
  latitudes = coords[,2] # The latitude values are in the second column of 'coords'
  min_latitude = min(latitudes)
  max_latitude = max(latitudes)
  ## Create a bbox that will intersect the RCA lines.
  bbox <- st_as_sfc(st_bbox(c(xmin = -180, xmax = 180, 
                              ymin = min_latitude, ymax = max_latitude), 
                            crs = st_crs(longitude_lines)))
  clipped_lines <- st_intersection(longitude_lines, bbox)
  print(clipped_lines)
  
  
  MultilineFromIntersections <- function(lat_line, clipped_lines) {
    # Perform intersection
    coastline_intersect <- st_intersection(latitude_lines, clipped_lines)
    
    # Extract points from intersection geometries
    extract_points <- function(coastline_intersect) {
      # Extract points from intersection geometries
      all_points_list <- lapply(1:length(coastline_intersect$geometry), function(i) {
        geom <- coastline_intersect$geometry[i]
        # Extract coordinates depending on geometry type
        coords <- st_coordinates(geom)
        # Select only the X and Y columns
        coords_df <- data.frame(X = coords[, "X"], Y = coords[, "Y"])
        # Create an sf object of points for each geometry
        st_as_sf(x = coords_df, coords = c("X", "Y"), crs = st_crs(coastline_intersect))
      })
      
      points_sf <- do.call(rbind, all_points_list)
      return(points_sf)
    }
    
    # Combine all sf objects into one
    points_sf <- extract_points(coastline_intersect)
    
    
    # Evaluate cases where latitude borders are not intersected based on intersection points
    ## Extract latitudes
    latitudes <- st_coordinates(points_sf)[,2]
    lat_counts <- table(latitudes)
    odd_even <- ifelse(lat_counts %% 2 == 1, "odd", "even")
    unique_lats <- as.numeric(names(lat_counts))
    ## Identify max and min latitude
    max_lat <- max(unique_lats)
    min_lat <- min(unique_lats)
    ## Check if max and/or min latitude have odd occurrences
    max_lat_odd <- odd_even[as.character(max_lat)] == "odd"
    min_lat_odd <- odd_even[as.character(min_lat)] == "odd"
    ## Get latitude border presenting the problem
    find_matching_latitude_indices <- function(sf_object, latitude) {
      matching_indices <- integer(0) # Initialize an empty vector for indices
      # Iterate over each geometry
      for (i in seq_along(sf_object$geometry)) {
        coords <- st_coordinates(sf_object$geometry[i])
        # Check if any latitude matches latitude within floating-point precision
        if (any(abs(coords[, 2] - latitude) < .Machine$double.eps)) {
          matching_indices <- c(matching_indices, i) # Append index if a match is found
        }
      }
      return(matching_indices)
    }
    
    # Below we solve the intersection issue on the border presenting the problem by searching the
    # nearest points between the lines
    process_latitude_lines <- function(latitude_lines, min_latitude) {
      ## Selecting latitude line affected
      matching_indices <- find_matching_latitude_indices(latitude_lines, min_latitude)
      selected_row <- latitude_lines[matching_indices,]
      ## Searching closest lines for all objects
      nearest_points <- st_nearest_points(longitude_lines,selected_row) %>% 
        st_as_sf()
      ## Selecting shortest line which presumably will correspond to the one of interest
      lengths <- as.vector(st_length(nearest_points))
      lengths <- lengths[lengths != 0]
      index_of_shortest <- which.min(lengths)
      shortest_line <- nearest_points[index_of_shortest, ]
      ## Add shortest line to our latitude line so intersection occurs
      latitude_intersect <- selected_row %>% 
        st_union(shortest_line)
      ## Update latitude lines
      latitude_lines <- rbind(latitude_lines[-matching_indices,],
                                       latitude_intersect %>% st_cast("LINESTRING"))
      return(latitude_lines)
    }
    
    # Now, we will evaluate the affected latitude lines and apply the fuctions defined above
    if (max_lat_odd & min_lat_odd) {
      # Both the maximum and minimum latitudes have an odd number of points
    } else if (max_lat_odd) { # The maximum latitude has an odd number of points
      latitude_lines <- process_latitude_lines(latitude_lines, max_latitude)
      ## Regenerate points_sf
      coastline_intersect <- st_intersection(latitude_lines, clipped_lines)
      points_sf <- extract_points(coastline_intersect)

    } else if (min_lat_odd) { # The minimum latitude has an odd number of points.
      latitude_lines <- process_latitude_lines(latitude_lines, min_latitude)
      ## Regenerate points_sf
      coastline_intersect <- st_intersection(latitude_lines, clipped_lines)
      points_sf <- extract_points(coastline_intersect)

    } else {
      # Do nothing if both counts are even
    }
    
    # Once we have the intersection points in the latitude borders, we can transform them into lines
    ## Sort points by longitude to guaranty they construct according to the vertices to fill
    coords <- st_coordinates(points_sf)
    sorted_coords <- coords[order(coords[, 'X']), ]
    sorted_coords <- sorted_coords[order(sorted_coords[, 'Y']), ] # Get X sorting by each latitude value
    ## Recreate sorted points as an sf object
    sorted_points_sf <- st_sf(geometry = st_sfc(lapply(1:nrow(sorted_coords), function(i) {
      st_point(sorted_coords[i, ])
    }), crs = st_crs(points_sf)))
    ## Get updated coordinates after sorting
    coords <- st_coordinates(sorted_points_sf)
    ## Create LINESTRINGs from pairs of sorted points
    lines_list <- vector("list", length = nrow(sorted_points_sf) / 2) # Initialize
    for (i in seq(1, nrow(sorted_points_sf), by = 2)) {
      if (i < nrow(sorted_points_sf)) {
        lines_list[[i]] <- st_linestring(coords[i:(i+1), ])
      }
    }
    lines_list <- lines_list[!sapply(lines_list, is.null)]  # Filter out any NULL elements
    ## Combine into a single MULTILINESTRING
    multiline <- st_sfc(lines_list, crs = st_crs(points_sf))
    multiline_sf <- st_sf(geometry = multiline)
    
  return(multiline_sf)
  }
  
  lat_shorelines <- MultilineFromIntersections(latitude_lines, clipped_lines)
  
  # Create polygon from lines
  ## Combine into a MULTILINESTRING
  multilinestring <- st_union(lat_shorelines$geometry)
  target_geometry <- clipped_lines %>%
    filter(area_name == "mainland" & land_ref == "mainland") %>%
    .$geometry
  combined_geometry <- st_union(target_geometry, multilinestring)
  ## Update the geometry with the combined geometry
  clipped_lines$geometry[clipped_lines$area_name == "mainland" & clipped_lines$land_ref == "mainland"] <- combined_geometry
  ## Polygonize the combined MULTILINESTRINGs
  polygon_sf <- st_combine(st_union(clipped_lines)) %>% 
    st_polygonize() %>% 
    st_collection_extract("POLYGON") %>% 
    st_as_sf() %>% 
    rename(geometry = x) %>% 
    mutate(id = row_number(),.before=geometry)
  
  # Clip out any inner polygon
  # To do it we will evaluate relationships between polygons based on whether they intersect and then exclude the smaller polygons within those associations
  ## Get information on intersection polygons
  intersections <- st_intersects(polygon_sf, sparse = TRUE)
  ## Get areas
  areas <- st_area(polygon_sf)
  area_df <- data.frame(area = areas)
  area_df$id <- 1:nrow(area_df)
  keep_ids <- numeric()
  ## For each polygon, find the one with the biggest area among those it intersects with
  for (i in 1:length(intersections)) {
    if(length(intersections[[i]]) > 0) {
      # Find the intersecting polygons and their areas
      intersecting_areas <- area_df[area_df$id %in% intersections[[i]], ]
      # Find the polygon(s) with the maximum area
      max_area_id <- intersecting_areas[which.max(intersecting_areas$area), "id"]
      # Add to keep_ids
      keep_ids <- unique(c(keep_ids, max_area_id))
    }
  }
  ## Keep only the polygons with the largest area in their intersection groups
  rca_coastline_polygons_filtered <- polygon_sf[keep_ids, ]
  
  
  
 map <- leaflet() %>%
      addTiles() %>%
      addPolygons(data = rca_coastline_polygons_filtered, color = "red", weight=1) %>% 
      addPolylines(data = selected_latitude_lines, color = "blue", weight=2)
  
  print(map)
  return(rca_coastline_polygons_filtered)
}

```


```{r}
constant_latitude = 36
horizontal_line = st_sfc(st_linestring(matrix(c(longitude_start, constant_latitude, longitude_end, constant_latitude), ncol = 2, byrow = TRUE)), crs = 4326)
horizontal_line_sf <- st_sf(geometry = horizontal_line) %>%
  mutate(boundary_type = "latitude",
         boundary_name = "34.17",
         area_name = "34.17",
         land_ref = "mainland",
         geometry = geometry )

latitude_lines <- rbind() # reset 
latitude_lines <- n_s_boundaries_sf %>% 
  filter(boundary_name %in% c(#"36 00.00' N"
                              "U.S. EEZ Boundary South"
                              ))

latitude_lines <- rbind(horizontal_line_sf,latitude_lines)

# Update isolines form CalPoly gdb
feature_class <- st_read(dsn = cal_poly_fp, layer = "Master_line_feature_source")
isolines <- feature_class %>% 
  filter(CoordFileName != "NA" & CoordFileName != "")

# emulating structure form longitude_lines[105, ]

isolines_testing <- isolines %>% 
  filter(CoordFileName == "150fm_012703.csv") %>% 
  st_combine() %>% 
  st_as_sf() %>% 
  st_set_geometry("geometry") %>% 
  mutate(boundary_type = "isobath",
         boundary_name = "150fm_012703.csv",
         area_name = "not_defined",
         land_ref = "bathymetry", .before= geometry)


selected_longitude_lines <- rbind(isolines_testing, coastline)
selected_latitude_lines <- latitude_lines

testing_poly <- rca_lines_to_polygons_v3(selected_longitude_lines,selected_latitude_lines)
```


