---
format: html
editor_options: 
  chunk_output_type: console
---

# New approach for RCA polygon creation

## Setup

```{r}
if (!require(librarian,quietly = T)){
  install.packages('librarian')
}

librarian::shelf(
  here,
  # plotly,
  readxl,
  glue,
  parallel,
  doParallel,
  tidyverse,
  lubridate,
  data.table,
  openxlsx,
  terra,
  leaflet,
  sf,
  openxlsx,
  rnaturalearth, 
  rnaturalearthdata,
  # foreach,
  # doParallel,
  iterators,
  quiet = T
)

sf_use_s2(FALSE)
```

```{r}
# Read in data using script (this helps keeping tidy the qmd)
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v4.R"))
source(here("RCA_data_exploration/scripts/generate_rca_objects.R"))
```

# Functions testing

## Testing for constant longitude lines

```{r}
eez_poly <-  st_read(here("RCA_data_exploration", "Ruttenberg et al collaboration", "spatial_ref_files", "eez.geojson"))

# The new approach considers the coastline independently than the EEZ
coastline <- st_read( here(data_path,"spatial_ref_files/all_shoreline_main_comb.geojson")) %>% 
  rename(
    land_ref = area_name,
    area_name = AreaType_2) %>% 
  mutate(
    boundary_type = "isobath",
    boundary_name = "shoreline")



# Update isolines form CalPoly gdb
feature_class <- st_read(dsn = cal_poly_fp, layer = "Master_line_feature_source")
isolines <- feature_class %>% 
  filter(CoordFileName != "NA" & CoordFileName != "")

split_isolines <- split(isolines, isolines$CoordFileName)

# function to apply the transformation
transform_isolines <- function(df) {
  df %>%
    st_combine() %>%
    st_as_sf() %>%
    st_set_geometry("geometry") %>%
    mutate(
      boundary_type = "isobath",
      boundary_name = first(df$CoordFileName),
      area_name = "not_defined",
      land_ref = "bathymetry",
      .before = geometry
    )
}

# Apply the transformation to each split dataframe and combine the results
new_isolines <- map_dfr(split_isolines, transform_isolines)

isolines_testing <- new_isolines %>% 
  filter(boundary_name == "150fm_012703.csv")

selected_longitude_lines <- rbind(isolines_testing, coastline)
```

```{r}
select_random_lat_boundaries <- function(data_frame) {
  # Extract unique boundary names
  unique_boundaries <- unique(data_frame$boundary_name)
  # Ensure that there are at least 2 unique boundaries to select from
  if(length(unique_boundaries) < 2) {
    stop("Not enough unique boundary names to select two random, non-equal values.")
  }
  # Randomly select two non-equal boundary names
  selected_boundaries <- sample(unique_boundaries, 2)
  # Filter rows that match the randomly selected boundary names
  selected_rows <- data_frame %>% 
    filter(boundary_name %in% selected_boundaries)
  return(selected_rows)
}

selected_latitude_lines <- select_random_lat_boundaries(n_s_boundaries_sf)


testing_poly <- rca_lines_to_polygons_v4(selected_longitude_lines,selected_latitude_lines,eez_poly)
```

**Errors detected:**

1. Selecting inner polygons based on area can lead to issues in regions where land areas exceed water areas, particularly when the shoreline acts as a boundary. This situation is notable in Oregon, where large estuaries can cause the polygon generation process to incorrectly focus on land areas. For instance, for the file "150fm_012703.csv," the latitude limits of "43 20.83' N" and "46 16.00' N" exemplify this issue. Additional examples include the latitudinal ranges "42 40.50' N" to "45 46.00' N".

2. The execution of the random polygon generation script show further anomalies in shapes. However, these are likely due to the absence of a longitudinal lines at certain latitudes.

## Testing with all random lines

```{r}
select_random_lon_boundaries <- function(data_frame) {
  # Extract unique boundary names
  unique_boundaries <- unique(data_frame$boundary_name)
  # Ensure that there are at least 2 unique boundaries to select from
  if(length(unique_boundaries) < 2) {
    stop("Not enough unique boundary names to select two random, non-equal values.")
  }
  # Randomly select two non-equal boundary names
  selected_boundaries <- sample(unique_boundaries, 2)
  # Filter rows that match the randomly selected boundary names
  selected_rows <- data_frame %>% 
    filter(boundary_name %in% selected_boundaries)
  return(selected_rows)
}

selected_longitude_lines <- select_random_lon_boundaries(new_isolines)
selected_latitude_lines <- select_random_lat_boundaries(n_s_boundaries_sf)


testing_poly <- rca_lines_to_polygons_v3(selected_longitude_lines,selected_latitude_lines)
```

**Errors detected:**

1. After some testing we detected that the islands are not clipped out if shoreline is not part of the boundary. (e.g., 36 00.00' N - U.S. EEZ Boundary South - 100fm_030104.csv - 150fm_010105.csv).


# Function implementation

## Input data

Although this was already done in the testing section, we will include the read-in code to be evaluated here as well.

```{r}
source(here("RCA_data_exploration/scripts/generate_rca_objects.R"))

# EEZ polygon, though it will only be used in v5 of the fuction exclusively applyed to those polygons neighboring the EEZ
eez_poly <-  st_read(here("RCA_data_exploration", "Ruttenberg et al collaboration", "spatial_ref_files", "eez.geojson"))

# Coastline shape that will define the shoreline layer as an extra isoline. As described earlier, the new approach considers the coastline independently than the EEZ
coastline <- st_read( here(data_path,"spatial_ref_files/all_shoreline_main_comb.geojson")) %>% 
  rename(
    land_ref = area_name,
    area_name = AreaType_2) %>% 
  mutate(
    boundary_type = "isobath",
    boundary_name = "shoreline") %>% 
  mutate(boundary_name = ifelse(boundary_name == "shoreline", # Matching with instructiosn df
                                "Shoreline",
                                boundary_name)) 

# RCA lines  form CalPoly gdb
feature_class <- st_read(dsn = cal_poly_fp, layer = "Master_line_feature_source")

isolines <- feature_class %>% 
  filter(CoordFileName != "NA" & CoordFileName != "") 
split_isolines <- split(isolines, isolines$CoordFileName)

transform_isolines <- function(df) {
  df %>%
    st_combine() %>%
    st_as_sf() %>%
    st_set_geometry("geometry") %>%
    mutate(
      boundary_type = "isobath",
      boundary_name = first(df$CoordFileName),
      area_name = "not_defined",
      land_ref = "bathymetry",
      .before = geometry
    )
}

new_isolines <- map_dfr(split_isolines, transform_isolines)

# Combine coastline with isolines to have them all in a single object
coastline <- st_transform(coastline, st_crs(new_isolines))
lon_boundary <-  rbind(coastline,new_isolines)

# Reference Cullen's sf with the latitudinal borders for each RCA
n_s_boundaries_sf <- st_transform(n_s_boundaries_sf, st_crs(new_isolines))
lat_boundary <- n_s_boundaries_sf
```


## Instructions dataframe

First, we will create an instructions data frame based on Cullen's code. Some updates need to be made so the contents of the instructions data frame match those from the `sf` objects. The instructions file contains the characteristics of each resulting polygon, which include the RCA date plus the line references that contain them.

```{r}
## Create clean data frame of polygon metadata
polygon_instructions_df <- polygon_df_orig  %>% 
  dplyr::select(-completed)  %>% 
  dplyr::filter(shoreward_boundary != "N/A")  %>% 
  dplyr::mutate(
    shoreward_boundary = gsub("^0 fm \\(([^)]+)\\)$", "\\1", shoreward_boundary),
    southern_boundary = ifelse(southern_boundary == "U.S. EEZ Boundary", 
                               "U.S. EEZ Boundary South", 
                               southern_boundary),
    northern_boundary = ifelse(northern_boundary == "U.S. EEZ Boundary", 
                               "U.S. EEZ Boundary North", 
                               northern_boundary),
    northern_boundary = ifelse(northern_boundary == "U.S. EEZ boundary", 
                               "U.S. EEZ Boundary North", 
                               northern_boundary)) %>% 
  rename( lat_boundary1 = northern_boundary,
          lat_boundary2 = southern_boundary,
          lon_boundary1 = shoreward_boundary,
          lon_boundary2 = seaward_boundary)


# If we check the latitude variables levels we see an error where "45 46.00'N" should be "45 46.00' N"
unique(polygon_instructions_df$lat_boundary2)
# Update "45 46.00'N" to "45 46.00' N"
polygon_instructions_df <- polygon_instructions_df %>% 
  mutate(lat_boundary1 = ifelse(lat_boundary1 == "45 46.00'N",
                                "45 46.00' N",
                                lat_boundary1),
         lat_boundary2 = ifelse(lat_boundary2 == "45 46.00'N",
                                "45 46.00' N",
                                lat_boundary2))
```

m¡Make sure that the instructions contents are correct.

```{r}
unique(polygon_instructions_df$lat_boundary1)
unique(polygon_instructions_df$lat_boundary2)
unique(polygon_instructions_df$lon_boundary1)
unique(polygon_instructions_df$lon_boundary2)
```

## Running for inner RCAs

After some testing, it was seen that the problems associated with inner RCAs and those neighboring the north and south limits of the EEZ are distinct. Therefore, we will apply two different function versions for each type of RCA.

For the inner RCAs, after an initial run using version 4, we encountered issues due to the lack of code addressing "no contact with border points" issue at both latitude borders. This oversight led to errors for the unique lines generated (i.e., `unique_geometries_sf`) in version 4, specifically for objects 74, 75, 89, 97, 98, 99, and 104. The same version 4 function also produced an empty geometry for object 69, which we will further discussion.

These issues were addressed in version 4.2. However, additional problems were identified. An anomaly was detected northwest of San Francisco, in front of the Greater Farallones National Marine Sanctuary, concerning the line "100fm_010107.csv." This anomaly is present in both NOAA lines and our generated lines, where a section of the line splits into two. Upon a detailed inspection of the line using QGIS, it was observed that this shape contains several redundant vertices.

```{r, echo = FALSE}
source(here("RCA_data_exploration/scripts/generate_rca_lines.R"))
filtered_rca_lines_sf <- rca_lines_sf %>%
  filter(boundary_name == "100fm_010107.csv")

filtered_rca_noaa_lines_sf <- new_isolines %>%
  filter(boundary_name == "100fm_010107.csv")
```

```{r, echo = FALSE}
leaflet() %>%
     addTiles() %>%
     addPolylines(data = filtered_rca_noaa_lines_sf, color = "orange", weight=2, group = "NOAA RCA line") %>%
     addPolylines(data = filtered_rca_lines_sf, color = "blue", weight=2, group = "emLab RCA line")%>%
  fitBounds(lng1 = -123.57, lat1 = 38.14, 
                    lng2 = -123.33, lat2 = 37.89) %>%
          addLegend(position = "topright", 
                    title = "100fm_010107.csv", 
                    opacity = 0, 
                    labels = "", 
                    colors = "transparent") %>% 
          addLayersControl(overlayGroups = c( "emLab RCA line", "NOAA RCA line"))
```


This issue is the cause of the empty geometry for object 69 and has led to additional anomalies with the new code, affecting 3 unique geometries and 24 total RCA polygons. Since the erroneous line is difficult to interpret and decisions must be made regarding the points that define it, we will exclude it until NOAA determines how to proceed with it.

```{r}
instructions_sample <- polygon_instructions_df %>% 
  # Exclude EEZ boundaries
  filter(lat_boundary1 != "U.S. EEZ Boundary North",
         lat_boundary2 != "U.S. EEZ Boundary South") %>% 
  # Remove instructions where 100fm_010107.csv is a problem
  filter(!(lat_boundary1 == "40 10.00' N" &
           lat_boundary2 == "38 00.00' N" &
           lon_boundary1 == "100fm_010107.csv" &
           lon_boundary2 == "150fm_010107.csv")) %>%
  filter(!(lat_boundary1 == "38 00.00' N" &
           lat_boundary2 == "34 27.00' N" &
           lon_boundary1 == "100fm_010107.csv" &
           lon_boundary2 == "150fm_010107.csv")) %>%
   filter(!(lat_boundary1 == "40 10.00' N" &
           lat_boundary2 == "38 00.00' N" &
           lon_boundary1 == "100fm_010107.csv" &
           lon_boundary2 == "200fm_petrale_010107.csv"))
```

Once we have defined the updated instructions, we will apply v4.2 for all RCAs of interest.

```{r}
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v4.2.R"))
```

```{r}
# Initialize list to store results
results <- list()
results_df <- data.frame(date = character(), area = character(), execution = logical(), stringsAsFactors = FALSE)

# Loop that evaluates each instruction line and applies v4.2 to it
for (i in 1:nrow(instructions_sample)) {
    # For each row in instructions_sample, extract the boundary names
    lat_boundary1_name <- instructions_sample$lat_boundary1[i]
    lat_boundary2_name <- instructions_sample$lat_boundary2[i]

    lon_boundary1_name <- instructions_sample$lon_boundary1[i]
    lon_boundary2_name <- instructions_sample$lon_boundary2[i] 

    # Select latitude lines
    selected_latitude_lines <- lat_boundary[lat_boundary$boundary_name == lat_boundary1_name, ] %>% 
      rbind(lat_boundary[lat_boundary$boundary_name == lat_boundary2_name, ])
    
    # Select longitude lines
    selected_longitude_lines <- lon_boundary[lon_boundary$boundary_name == lon_boundary1_name, ] %>% 
      rbind(lon_boundary[lon_boundary$boundary_name == lon_boundary2_name, ])
    
    # Process the selected lines to create polygons
    result <- suppressMessages(
      rca_lines_to_polygons_v4.2(selected_longitude_lines, selected_latitude_lines,eez_poly)
    )
    
    # Extracting boundary_name from each
    boundary_name_longitude1 = selected_longitude_lines$boundary_name[1] 
    boundary_name_longitude2 = selected_longitude_lines$boundary_name[2] 
    boundary_name_latitude1 = selected_latitude_lines$boundary_name[1] 
    boundary_name_latitude2 = selected_latitude_lines$boundary_name[2] 
    
    # Constructing the string with `glue`
    final_string <- glue("{lon_boundary1_name}-{lon_boundary2_name}-{lat_boundary1_name}-{lat_boundary2_name}")
    final_string <- gsub(" ", "", final_string)
    
    if (is.null(result) || all(st_is_empty(result))) {
        execution_status <- "empty geometry"
    } else {
        execution_status <- "successful"
    }
    
    print(paste0(as.character(instructions_sample$year_month[i]),"-", final_string, ": ",i,"/",nrow(instructions_sample),"...", execution_status))
    # Append to the results dataframe
    results_df <- rbind(results_df, data.frame(date = instructions_sample$year_month[i], area = final_string, execution = execution_status))
    
    # Combine polygons into a multipolygons and assign the instructions df variable levels
    combined_sf <- result %>% 
      st_combine() %>% 
      st_sf() %>% 
      cbind(instructions_sample[i,])
    
    # Store each result in the results list
    results[[i]] <- combined_sf
}

# Summary results
table(results_df$execution)
# Combine resulting list into a single sf object
combined_results_sf <- do.call(rbind, results)
# Export as a geopackage 
st_write(combined_results_sf, here("RCA_data_exploration","outputs","rca_poly","inner_rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```

Additionally, to visually explore the validity of the generated polygons, we can extract the unique polygons, significantly reducing the manual effort involved.


```{r}
# Initialize a logical vector to mark duplicates; FALSE means no duplicate found yet
is_duplicate <- rep(FALSE, length(combined_results_sf))

# Loop over all geometries
for (i in 1:length(combined_results_sf$geometry)) {
  # Skip if this geometry has already been marked as a duplicate
  if (!is_duplicate[i]) {
    # Compare the current geometry with all others
    duplicates = sapply(combined_results_sf$geometry, function(x) identical(x, combined_results_sf$geometry[[i]]))
    # Mark duplicates, but keep the first occurrence
    is_duplicate <- is_duplicate | (duplicates & !is_duplicate)
    is_duplicate[i] <- FALSE  # Ensure the first instance is not marked as duplicate
  }
}

# Filter out duplicates
unique_geometries <- combined_results_sf[!is_duplicate, ]
```


```{r}
st_write(unique_geometries, here("RCA_data_exploration","outputs","rca_poly","unique_inner_rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```

## Running for border RCAs


Select border RCAs

```{r}
instructions_sample <- polygon_instructions_df %>% 
  filter(lat_boundary1 == "U.S. EEZ Boundary North" |
         lat_boundary2 == "U.S. EEZ Boundary South")
```

```{r}
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.R"))
```


### Testing with shoreline RCAs

```{r}
instructions_sample <- instructions_sample %>% 
  filter(lon_boundary1 == "Shoreline")
```

```{r}
# Initialize list to store results
results <- list()
results_df <- data.frame(date = character(), area = character(), execution = logical(), stringsAsFactors = FALSE)

# Loop that evaluates each instruction line and applies v4.2 to it
for (i in 1:nrow(instructions_sample)) {
    # For each row in instructions_sample, extract the boundary names
    lat_boundary1_name <- instructions_sample$lat_boundary1[i]
    lat_boundary2_name <- instructions_sample$lat_boundary2[i]

    lon_boundary1_name <- instructions_sample$lon_boundary1[i]
    lon_boundary2_name <- instructions_sample$lon_boundary2[i] 

    # Select latitude lines
    selected_latitude_lines <- lat_boundary[lat_boundary$boundary_name == lat_boundary1_name, ] %>% 
      rbind(lat_boundary[lat_boundary$boundary_name == lat_boundary2_name, ])
    
    # Select longitude lines
    selected_longitude_lines <- lon_boundary[lon_boundary$boundary_name == lon_boundary1_name, ] %>% 
      rbind(lon_boundary[lon_boundary$boundary_name == lon_boundary2_name, ])
    
    # Process the selected lines to create polygons
    result <- suppressMessages(
      rca_lines_to_polygons_v5(selected_longitude_lines, selected_latitude_lines,eez_poly)
    )
    
  
    
    # Constructing the string with `glue`
    final_string <- glue("{lon_boundary1_name}-{lon_boundary2_name}-{lat_boundary1_name}-{lat_boundary2_name}")
    final_string <- gsub(" ", "", final_string)
    
    if (is.null(result) || all(st_is_empty(result))) {
        execution_status <- "empty geometry"
    } else {
        execution_status <- "successful"
    }
    
    print(paste0(as.character(instructions_sample$year_month[i]),"-", final_string, ": ",i,"/",nrow(instructions_sample),"...", execution_status))
    # Append to the results dataframe
    results_df <- rbind(results_df, data.frame(date = instructions_sample$year_month[i], area = final_string, execution = execution_status))
    
    # Combine polygons into a multipolygons and assign the instructions df variable levels
    combined_sf <- result %>% 
      st_combine() %>% 
      st_sf() %>% 
      cbind(instructions_sample[i,])
    
    # Store each result in the results list
    results[[i]] <- combined_sf
}

# Summary results
table(results_df$execution)
```

```{r}
# Combine resulting list into a single sf object
combined_results_sf <- do.call(rbind, results)
# Export as a geopackage 
st_write(combined_results_sf, here("RCA_data_exploration","outputs","rca_poly","border_rca_polygons_shoreline_test.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```

```{r}
combined_results_sf$geometry_wkt <- st_as_text(combined_results_sf$geometry)

unique_geometries_sf <- combined_results_sf %>%
  distinct(geometry_wkt, .keep_all = TRUE) %>%
  select(-geometry_wkt) %>% 
  st_as_sf()
```

```{r}
st_write(unique_geometries_sf, here("RCA_data_exploration","outputs","rca_poly","unique_border_rca_polygons_shoreline.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```

### Apply to all Border RCAs

```{r}
instructions_sample <- polygon_instructions_df %>% 
  filter(lat_boundary1 == "U.S. EEZ Boundary North" |
         lat_boundary2 == "U.S. EEZ Boundary South") 
```
697
```{r}
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.R"))
```

```{r}
library(parallel)
library(doParallel)
library(foreach)
library(dplyr)
library(sf)
library(glue)

# Register parallel backend to use multiple cores
numCores <- detectCores() -1
registerDoParallel(cores = numCores)

# Assuming 'instructions_sample', 'lat_boundary', 'lon_boundary', and necessary functions are already defined

# Initialize list to store results from each iteration
results <- list()

# Parallel loop using foreach. Note the changes in the loop's structure
results <- foreach(i = 1:nrow(instructions_sample), .packages = c("dplyr", "sf", "glue")) %dopar% {
  tryCatch({
  # Extracting boundary names
  lat_boundary1_name <- instructions_sample$lat_boundary1[i]
  lat_boundary2_name <- instructions_sample$lat_boundary2[i]
  lon_boundary1_name <- instructions_sample$lon_boundary1[i]
  lon_boundary2_name <- instructions_sample$lon_boundary2[i]

  # Selecting latitude and longitude lines
  selected_latitude_lines <- lat_boundary[lat_boundary$boundary_name == lat_boundary1_name, ] %>% 
    rbind(lat_boundary[lat_boundary$boundary_name == lat_boundary2_name, ])
  selected_longitude_lines <- lon_boundary[lon_boundary$boundary_name == lon_boundary1_name, ] %>% 
    rbind(lon_boundary[lon_boundary$boundary_name == lon_boundary2_name, ])

  # Process to create polygons (assuming rca_lines_to_polygons_v5 is a predefined function)
  result <- suppressMessages(
    rca_lines_to_polygons_v5(selected_longitude_lines, selected_latitude_lines, eez_poly)
  )
  
  combined_sf <- result %>% 
      st_combine() %>% 
      st_sf() %>% 
      cbind(instructions_sample[i,])

  # Return the sf object directly
  combined_sf
  
  }, error = function(e) {
      # Log or return the error along with the iteration number
      list(error = e, iteration = i)
    })
}

# Don't forget to stop the cluster if you're done with parallel operations
stopImplicitCluster()

```


```{r}
results_clean <- Filter(function(x) !is.list(x$error), results)

# Extract errors and their iterations into a list
errors_list <- lapply(results, function(x) {
  if (is.list(x) && !is.null(x$error)) {
    return(list(error_message = as.character(x$error$message), iteration = x$iteration))
  } else {
    return(NULL)
  }
})

# Remove NULL elements
errors_list <- Filter(Negate(is.null), errors_list)

iterations_vector <- sapply(errors_list, function(x) x$iteration)

# Check the objects
instructions_sample[iterations_vector,]

```
errors in 698, 699 and 700

```{r}
# Combine resulting list into a single sf object
combined_results_sf <- do.call(rbind, results_clean)
# Export as a geopackage 
st_write(combined_results_sf, here("RCA_data_exploration","outputs","rca_poly","border_rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```


```{r}
# Initialize a logical vector to mark duplicates; FALSE means no duplicate found yet
is_duplicate <- rep(FALSE, length(combined_results_sf))

# Loop over all geometries
for (i in 1:length(combined_results_sf$geometry)) {
  # Skip if this geometry has already been marked as a duplicate
  if (!is_duplicate[i]) {
    # Compare the current geometry with all others
    duplicates = sapply(combined_results_sf$geometry, function(x) identical(x, combined_results_sf$geometry[[i]]))
    # Mark duplicates, but keep the first occurrence
    is_duplicate <- is_duplicate | (duplicates & !is_duplicate)
    is_duplicate[i] <- FALSE  # Ensure the first instance is not marked as duplicate
  }
}

# Filter out duplicates
unique_geometries <- combined_results_sf[!is_duplicate, ]
```

```{r}
st_write(unique_geometries, here("RCA_data_exploration","outputs","rca_poly","unique_border_rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```


## Running for all

```{r}
instructions_sample <- polygon_instructions_df
```
697
```{r}
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.R"))
```


```{r}
# Register parallel backend to use multiple cores
numCores <- detectCores() -1
registerDoParallel(cores = numCores)

# Assuming 'instructions_sample', 'lat_boundary', 'lon_boundary', and necessary functions are already defined

# Initialize list to store results from each iteration
results <- list()

# Parallel loop using foreach. Note the changes in the loop's structure
results <- foreach(i = 1:nrow(instructions_sample), .packages = c("dplyr", "sf", "glue")) %dopar% {
  tryCatch({
  # Extracting boundary names
  lat_boundary1_name <- instructions_sample$lat_boundary1[i]
  lat_boundary2_name <- instructions_sample$lat_boundary2[i]
  lon_boundary1_name <- instructions_sample$lon_boundary1[i]
  lon_boundary2_name <- instructions_sample$lon_boundary2[i]

  # Selecting latitude and longitude lines
  selected_latitude_lines <- lat_boundary[lat_boundary$boundary_name == lat_boundary1_name, ] %>% 
    rbind(lat_boundary[lat_boundary$boundary_name == lat_boundary2_name, ])
  selected_longitude_lines <- lon_boundary[lon_boundary$boundary_name == lon_boundary1_name, ] %>% 
    rbind(lon_boundary[lon_boundary$boundary_name == lon_boundary2_name, ])

  # Process to create polygons (assuming rca_lines_to_polygons_v5 is a predefined function)
  result <- suppressMessages(
    rca_lines_to_polygons_v5(selected_longitude_lines, selected_latitude_lines, eez_poly)
  )
  
  combined_sf <- result %>% 
      st_combine() %>% 
      st_sf() %>% 
      cbind(instructions_sample[i,])

  # Return the sf object directly
  combined_sf
  
  }, error = function(e) {
      # Log or return the error along with the iteration number
      list(error = e, iteration = i)
    })
}

# Don't forget to stop the cluster if you're done with parallel operations
stopImplicitCluster()

```


```{r}
results_clean <- Filter(function(x) !is.list(x$error), results)

# Extract errors and their iterations into a list
errors_list <- lapply(results, function(x) {
  if (is.list(x) && !is.null(x$error)) {
    return(list(error_message = as.character(x$error$message), iteration = x$iteration))
  } else {
    return(NULL)
  }
})

# Remove NULL elements
errors_list <- Filter(Negate(is.null), errors_list)

iterations_vector <- sapply(errors_list, function(x) x$iteration)

# Check the objects
instructions_sample[iterations_vector,]

incorrect_lines <- instructions_sample[iterations_vector,] %>%
  group_by(land_ref, lat_boundary1, lat_boundary2, lon_boundary1, lon_boundary2) %>%
  slice(1) %>%
  ungroup()
```

```{r}
# Combine resulting list into a single sf object
combined_results_sf <- do.call(rbind, results_clean)
# Export as a geopackage 
st_write(combined_results_sf, here("RCA_data_exploration","outputs","rca_poly","rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```


```{r}
# Initialize a logical vector to mark duplicates; FALSE means no duplicate found yet
is_duplicate <- rep(FALSE, length(combined_results_sf))

# Loop over all geometries
for (i in 1:length(combined_results_sf$geometry)) {
  # Skip if this geometry has already been marked as a duplicate
  if (!is_duplicate[i]) {
    # Compare the current geometry with all others
    duplicates = sapply(combined_results_sf$geometry, function(x) identical(x, combined_results_sf$geometry[[i]]))
    # Mark duplicates, but keep the first occurrence
    is_duplicate <- is_duplicate | (duplicates & !is_duplicate)
    is_duplicate[i] <- FALSE  # Ensure the first instance is not marked as duplicate
  }
}

# Filter out duplicates
unique_geometries <- combined_results_sf[!is_duplicate, ]
```

```{r}
st_write(unique_geometries, here("RCA_data_exploration","outputs","rca_poly","unique_rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```



### Testing errors

```{r}
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.2.R"))
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.R"))

```

```{r}
# instructions_sample <- polygon_instructions_df %>%
#   filter(lat_boundary1 == "U.S. EEZ Boundary North" &
#            lat_boundary2 == "40 10.00' N" &
#            lon_boundary1 == "Shoreline" &
#            lon_boundary2 == "200fm_petrale_102403.csv")

# instructions_sample <- polygon_instructions_df %>%
#   filter(lat_boundary1 == "34 27.00' N" &
#            lat_boundary2 == "U.S. EEZ Boundary South" &
#            lon_boundary1 == "Shoreline" &
#            lon_boundary2 == "200fm_petrale_102403.csv")%>% .[1,]

# instructions_sample <- polygon_instructions_df %>%
#   filter(lat_boundary1 == "U.S. EEZ Boundary North" &
#            lat_boundary2 == "48 10.00' N" &
#            lon_boundary1 == "Shoreline" &
#            lon_boundary2 == "150fm_010113.csv") %>% .[1,]


## additional error using v5.2

instructions_sample <- polygon_instructions_df %>%
  filter(lat_boundary1 == "U.S. EEZ Boundary North" &
           lat_boundary2 == "40 10.00' N" &
           lon_boundary1 == "Shoreline" &
           lon_boundary2 == "250fm_091002.csv")

lat_boundary1_name <- instructions_sample$lat_boundary1
lat_boundary2_name <- instructions_sample$lat_boundary2
# 
# lat_boundary1_name <- "U.S. EEZ Boundary North"
# lat_boundary2_name <- "48 10.00' N"

lon_boundary1_name <- instructions_sample$lon_boundary1
lon_boundary2_name <- instructions_sample$lon_boundary2

# Select latitude lines
selected_latitude_lines <- lat_boundary[lat_boundary$boundary_name == lat_boundary1_name, ] %>% 
  rbind(lat_boundary[lat_boundary$boundary_name == lat_boundary2_name, ])

# Select longitude lines
selected_longitude_lines <- lon_boundary[lon_boundary$boundary_name == lon_boundary1_name, ] %>% 
  rbind(lon_boundary[lon_boundary$boundary_name == lon_boundary2_name, ])

# Process the selected lines to create polygons
result <- suppressMessages(
  rca_lines_to_polygons_v5(selected_longitude_lines, selected_latitude_lines,eez_poly)
)
```


```{r}
longitude_lines <- selected_longitude_lines
latitude_lines <- selected_latitude_lines

# st_write(longitude_lines, here("RCA_data_exploration","outputs","rca_poly","longitude_lines.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
# 
# st_write(latitude_lines, here("RCA_data_exploration","outputs","rca_poly","latitude_lines.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
  
  
geometries <- st_geometry(latitude_lines)

# Initialize an empty vector to store max latitudes
max_latitudes <- numeric(length(geometries))

# Loop through each geometry to find the max latitude
for (i in seq_along(geometries)) {
  # Extract coordinates for each geometry
  coords <- st_coordinates(geometries[[i]])
  # The Y coordinates (latitude) are in the second column
  latitudes <- coords[, "Y"]
  # Find the maximum latitude for this geometry
  max_latitudes[i] <- max(latitudes)
}

# You can then add these max latitudes back to your original data frame, if needed
# latitude_lines$max_latitude <- max_latitudes

boundary_condition_s <- any(latitude_lines$boundary_name == "U.S. EEZ Boundary South")
# Set min_latitude based on the condition
min_latitude <- ifelse(boundary_condition_s, 30, min(max_latitudes))

boundary_condition_n <- any(latitude_lines$boundary_name == "U.S. EEZ Boundary Nouth")
max_latitude <- ifelse(boundary_condition_n, 48.6, max(max_latitudes))

# min_latitude = min(max_latitudes)
  # max_latitude = max(max_latitudes)
  ## Create a bbox that will intersect the RCA lines.
  bbox <- st_as_sfc(st_bbox(c(xmin = -130, xmax = -115, 
                              ymin = min_latitude, ymax = max_latitude), 
                            crs = st_crs(longitude_lines)))
  



  # Clip RCA boundary lines based on latitude delimitation lines.
  ## Find min and max latitude values from latitude lines.
  # coords = st_coordinates(st_geometry(latitude_lines))
  # latitudes = coords[,2] # The latitude values are in the second column of 'coords'
  # min_latitude = min(latitudes)
  # max_latitude = max(latitudes)
  # ## Create a bbox that will intersect the RCA lines.
  # bbox <- st_as_sfc(st_bbox(c(xmin = -130, xmax = -115, 
  #                             ymin = min_latitude, ymax = max_latitude), 
  #                           crs = st_crs(longitude_lines)))
  
  # eez_poly <- st_polygonize(shoreline[2,]) %>% 
  #   st_collection_extract("POLYGON")
  
  # difference <- st_intersection(eez_poly,bbox)
  # 
  # clipped_lines <- st_intersection(longitude_lines, difference)
  
  ### Patch -----
  # This is a bit redundant but seems to work
  difference <- st_intersection(eez_poly,bbox)
  pre_clipped_lines <- st_intersection(longitude_lines, bbox)
  clipped_lines <- st_intersection(pre_clipped_lines, difference)
  ### Patch -----
  

       # st_write(coastline_intersect, here("RCA_data_exploration","outputs","rca_poly","coastline_intersect.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
  
  
  # MultilineFromIntersections <- function(lat_line, clipped_lines) {
    # Perform intersection
    coastline_intersect <- st_intersection(latitude_lines, longitude_lines)
    
    # Extract points from intersection geometries
    # print("Extracting points from intersection geometries")
    extract_points <- function(coastline_intersect) {
      # Extract points from intersection geometries
      all_points_list <- lapply(1:length(coastline_intersect$geometry), function(i) {
        geom <- coastline_intersect$geometry[i]
        # Extract coordinates depending on geometry type
        coords <- st_coordinates(geom)
        # Select only the X and Y columns
        coords_df <- data.frame(X = coords[, "X"], Y = coords[, "Y"])
        # Create an sf object of points for each geometry
        st_as_sf(x = coords_df, coords = c("X", "Y"), crs = st_crs(coastline_intersect))
      })
      
      points_sf <- do.call(rbind, all_points_list)
      return(points_sf)
    }
    
    # Combine all sf objects into one
    points_sf <- extract_points(coastline_intersect)
    
    
    ## Extract latitudes
    latitudes <- st_coordinates(points_sf)[,2]
    
    if (length(latitudes) %% 2 != 0 | !any(duplicated(latitudes))) {
      lat_counts <- table(latitudes)
      odd_even <- ifelse(lat_counts %% 2 == 1, "odd", "even")
      unique_lats <- unique(latitudes)
      ## Identify max and min latitude
      max_lat <- max(unique_lats)
      min_lat <- min(unique_lats)
      ## Check if max and/or min latitude have odd occurrences
      max_lat_odd <- odd_even[as.character(max_lat)] == "odd"
      min_lat_odd <- odd_even[as.character(min_lat)] == "odd"
      ## Get latitude border presenting the problem
      find_matching_latitude_indices <- function(sf_object, latitude) {
        
        row_indices <- points_sf %>%
          st_coordinates() %>%
          {which(.[, "Y"] == latitude, arr.ind = TRUE)}
        
        point_to_fix <- points_sf[row_indices,]
        
        matching_indices <- st_intersects(st_buffer(point_to_fix, 1e-6),sf_object) %>% 
          as.numeric()
        
        return(matching_indices)
      }
      
      # Below we solve the intersection issue on the border presenting the problem by searching the
      # nearest points between the lines
      # print("Lack of intersections detected. Solving problem...")
      process_latitude_lines <- function(latitude_lines, latitude) {
        ## Selecting latitude line affected
        matching_indices <- find_matching_latitude_indices(latitude_lines, latitude)
        selected_row <- latitude_lines[matching_indices,]
        ## Searching closest lines for all objects
        nearest_points <- st_nearest_points(longitude_lines,selected_row) %>%
          st_as_sf()
        
        lengths <- as.vector(st_length(nearest_points))
        # Filter out zero-length lines
        non_zero_lengths <- lengths[lengths > 0]
        # Find the shortest non-zero length
        shortest_non_zero_length <- min(non_zero_lengths)
        # Find the index(es) of the LINESTRING(s) with the shortest non-zero length
        shortest_index <- which(lengths == shortest_non_zero_length)
        # Select the shortest non-zero length LINESTRING from the collection
        shortest_line <- nearest_points[shortest_index, ]
        
        ## Add shortest line to our latitude line so intersection occurs
        latitude_intersect <- selected_row %>%
          st_union(shortest_line)
        ## Update latitude lines
        latitude_lines <- rbind(latitude_lines[-matching_indices,],
                                latitude_intersect %>% st_cast("LINESTRING"))
        return(latitude_lines)
      }
      
      
      
      # Now, we will evaluate the affected latitude lines and apply the fuctions defined above
      if (max_lat_odd & min_lat_odd) {
        # Both the maximum and minimum latitudes have an odd number of points
        updated_max_latitude_lines <- process_latitude_lines(latitude_lines, max_lat)
        
        is_max_lat_in_line <- function(line, max_lat) {
          coords <- st_coordinates(line)
          lat_min <- min(coords[,2])
          lat_max <- max(coords[,2])
          return(max_lat >= lat_min && max_lat <= lat_max)
        }
        
        # Apply the function to filter rows
        updated_max_latitude_lines_filtered <- updated_max_latitude_lines %>%
          filter(sapply(geometry, is_max_lat_in_line, max_lat = max_lat))
        
        
        updated_min_latitude_lines <- process_latitude_lines(latitude_lines, min_lat)
        
        is_min_lat_in_line <- function(line, min_lat) {
          coords <- st_coordinates(line)
          lat_min <- min(coords[,2])
          return(min_lat >= lat_min)
        }
        
        # Apply the function to filter rows
        updated_min_latitude_lines_filtered <- updated_min_latitude_lines %>%
          filter(sapply(geometry, is_min_lat_in_line, min_lat = min_lat)) 
        
        updated_latitude_lines <- rbind(updated_min_latitude_lines_filtered,
                                        updated_max_latitude_lines_filtered)
        
        ## Regenerate points_sf
        coastline_intersect <- st_intersection(updated_latitude_lines, clipped_lines)
        points_sf <- extract_points(coastline_intersect)
        
        
      } else if (max_lat_odd == TRUE & min_lat_odd == FALSE) { # The maximum latitude has an odd number of points
        updated_latitude_lines <- process_latitude_lines(latitude_lines, max_lat)
        ## Regenerate points_sf
        coastline_intersect <- st_intersection(updated_latitude_lines, clipped_lines)
        points_sf <- extract_points(coastline_intersect)
        
      } else if (min_lat_odd == TRUE & max_lat_odd == FALSE) { # The minimum latitude has an odd number of points.
        updated_latitude_lines <- process_latitude_lines(latitude_lines, min_lat)
        ## Regenerate points_sf
        coastline_intersect <- st_intersection(updated_latitude_lines, clipped_lines)
        points_sf <- extract_points(coastline_intersect)
        
      } else {
        # Do nothing if both counts are even
      }
    }
    
    
    # Once we have the intersection points in the latitude borders, we can transform them into lines
    # print("Transforming points into lines")
    ## Sort points by longitude to guaranty they construct according to the vertices to fill
    coords <- st_coordinates(points_sf)
    sorted_coords <- coords[order(coords[, 'X']), ]
    sorted_coords <- sorted_coords[order(sorted_coords[, 'Y']), ] # Get X sorting by each latitude value
    ## Recreate sorted points as an sf object
    sorted_points_sf <- st_sf(geometry = st_sfc(lapply(1:nrow(sorted_coords), function(i) {
      st_point(sorted_coords[i, ])
    }), crs = st_crs(points_sf)))
    ## Get updated coordinates after sorting
    coords <- st_coordinates(sorted_points_sf)
    ## Create LINESTRINGs from pairs of sorted points
    lines_list <- vector("list", length = nrow(sorted_points_sf) / 2) # Initialize
    for (i in seq(1, nrow(sorted_points_sf), by = 2)) {
      if (i < nrow(sorted_points_sf)) {
        lines_list[[i]] <- st_linestring(coords[i:(i+1), ])
      }
    }
    lines_list <- lines_list[!sapply(lines_list, is.null)]  # Filter out any NULL elements
    ## Combine into a single MULTILINESTRING
    multiline <- st_sfc(lines_list, crs = st_crs(points_sf))
    multiline_sf <- st_sf(geometry = multiline)
    
  #   return(multiline_sf)
  # }
  
  # st_write(clipped_lines, here("RCA_data_exploration","outputs","rca_poly","clipped_lines.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
  # st_write(multiline_sf, here("RCA_data_exploration","outputs","rca_poly","multiline_sf.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
  
  # lat_shorelines <- MultilineFromIntersections(latitude_lines, clipped_lines)
    lat_shorelines <- multiline_sf
  # Create polygon from lines
  # print("Creating polygons from lines")
  ## Combine into a MULTILINESTRING
  multilinestring <- st_union(lat_shorelines$geometry)
  target_geometry <- clipped_lines %>% 
    # filter(area_name == "mainland" & land_ref == "mainland") %>%
    .$geometry 
  combined_geometry <- st_union(target_geometry, multilinestring)
  ## Update the geometry with the combined geometry
  # clipped_lines$geometry[clipped_lines$area_name == "mainland" & clipped_lines$land_ref == "mainland"] <- combined_geometry
  ## Polygonize the combined MULTILINESTRINGs
  polygon_sf <- st_combine(st_union(combined_geometry)) %>% 
    st_polygonize() %>% 
    st_collection_extract("POLYGON") %>% 
    st_as_sf() %>% 
    rename(geometry = x) %>% 
    mutate(id = row_number(),.before=geometry)
  
  # # Clip out any inner polygon
  # print("First inner polygons clip out")
  # # To do it we will evaluate relationships between polygons based on whether they intersect and then exclude the smaller polygons within those associations
  # ## Get information on intersection polygons
  # intersections <- st_intersects(polygon_sf, sparse = TRUE)
  # ## Get areas
  # print("1")
  # areas <- st_area(polygon_sf)
  # print("2")
  # area_df <- data.frame(area = areas)
  # print("3")
  # 
  # # area_df$id <- 1:nrow(area_df)
  # area_df$id <- as.numeric(rownames(area_df))
  # print("4")
  # 
  # keep_ids <- numeric()
  # print("5")
  # ## For each polygon, find the one with the biggest area among those it intersects with
  # for (i in 1:length(intersections)) {
  #   if(length(intersections[[i]]) > 0) {
  #     # Find the intersecting polygons and their areas
  #     intersecting_areas <- area_df[area_df$id %in% intersections[[i]], ]
  #     # Find the polygon(s) with the maximum area
  #     max_area_id <- intersecting_areas[which.max(intersecting_areas$area), "id"]
  #     # Add to keep_ids
  #     keep_ids <- unique(c(keep_ids, max_area_id))
  #   }
  # }
  # print("6")
  # ## Keep only the polygons with the largest area in their intersection groups
  # rca_coastline_polygons_filtered <- polygon_sf[keep_ids, ]
  
 leaflet() %>%
    addTiles() %>%
    addPolygons(data = polygon_sf, color = "red", weight=1) %>%
    # addPolylines(data = selected_latitude_lines, color = "blue", weight=2) %>%
    addPolylines(data = clipped_lines, color = "orange", weight=2)

 
```

line issue

```{r, echo = FALSE}
source(here("RCA_data_exploration/scripts/generate_rca_lines.R"))
filtered_rca_lines_sf <- rca_lines_sf %>%
  filter(boundary_name == "50fm_052803.csv")

filtered_rca_noaa_lines_sf <- new_isolines %>%
  filter(boundary_name == "50fm_052803.csv")
```

```{r, echo = FALSE}
leaflet() %>%
     addTiles() %>%
     addPolylines(data = filtered_rca_noaa_lines_sf, color = "orange", weight=2, group = "NOAA RCA line") %>%
     addPolylines(data = filtered_rca_lines_sf, color = "blue", weight=2, group = "emLab RCA line")%>%
  fitBounds(lng1 = -123.57, lat1 = 38.14, 
                    lng2 = -123.33, lat2 = 37.89) %>%
          addLegend(position = "topright", 
                    title = "100fm_010107.csv", 
                    opacity = 0, 
                    labels = "", 
                    colors = "transparent") %>% 
          addLayersControl(overlayGroups = c( "emLab RCA line", "NOAA RCA line"))
```

##### TESTING UPDATES

```{r}
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.5.R"))
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.4.R"))
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.3.R"))
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.2.R"))
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.R"))

```

```{r}
instructions_sample <- polygon_instructions_df %>% 
  filter(lat_boundary1 == "U.S. EEZ Boundary North" |
         lat_boundary2 == "U.S. EEZ Boundary South")

# instructions_sample <- instructions_sample %>% 
#   filter(lon_boundary1 == "Shoreline")
```

```{r}

# Register parallel backend to use multiple cores
numCores <- detectCores() -1
registerDoParallel(cores = numCores)

# Assuming 'instructions_sample', 'lat_boundary', 'lon_boundary', and necessary functions are already defined

# Initialize list to store results from each iteration
results <- list()

# Parallel loop using foreach. Note the changes in the loop's structure
results <- foreach(i = 1:nrow(instructions_sample), .packages = c("dplyr", "sf", "glue")) %dopar% {
  tryCatch({
  # Extracting boundary names
  lat_boundary1_name <- instructions_sample$lat_boundary1[i]
  lat_boundary2_name <- instructions_sample$lat_boundary2[i]
  lon_boundary1_name <- instructions_sample$lon_boundary1[i]
  lon_boundary2_name <- instructions_sample$lon_boundary2[i]

  # Selecting latitude and longitude lines
  selected_latitude_lines <- lat_boundary[lat_boundary$boundary_name == lat_boundary1_name, ] %>% 
    rbind(lat_boundary[lat_boundary$boundary_name == lat_boundary2_name, ])
  selected_longitude_lines <- lon_boundary[lon_boundary$boundary_name == lon_boundary1_name, ] %>% 
    rbind(lon_boundary[lon_boundary$boundary_name == lon_boundary2_name, ])

  # Process to create polygons (assuming rca_lines_to_polygons_v5 is a predefined function)
  result <- suppressMessages(
    rca_lines_to_polygons_v5.5(selected_longitude_lines, selected_latitude_lines, eez_poly)
  )
  
  combined_sf <- result %>% 
      st_combine() %>% 
      st_sf() %>% 
      cbind(instructions_sample[i,])

  # Return the sf object directly
  combined_sf
  
  }, error = function(e) {
      # Log or return the error along with the iteration number
      list(error = e, iteration = i)
    })
}

# Don't forget to stop the cluster if you're done with parallel operations
stopImplicitCluster()

```

```{r}
results_clean <- Filter(function(x) !is.list(x$error), results)

# Extract errors and their iterations into a list
errors_list <- lapply(results, function(x) {
  if (is.list(x) && !is.null(x$error)) {
    return(list(error_message = as.character(x$error$message), iteration = x$iteration))
  } else {
    return(NULL)
  }
})

# Remove NULL elements
errors_list <- Filter(Negate(is.null), errors_list)

iterations_vector <- sapply(errors_list, function(x) x$iteration)

# Check the objects
instructions_sample[iterations_vector,]
# 
incorrect_lines <- instructions_sample[iterations_vector,] %>%
  group_by(land_ref, lat_boundary1, lat_boundary2, lon_boundary1, lon_boundary2) %>%
  slice(1) %>%
  ungroup()

incorrect_lines
```


```{r}
# Combine resulting list into a single sf object
combined_results_sf <- do.call(rbind, results_clean)

```

```{r}
# Initialize a logical vector to mark duplicates; FALSE means no duplicate found yet
is_duplicate <- rep(FALSE, length(combined_results_sf))

# Loop over all geometries
for (i in 1:length(combined_results_sf$geometry)) {
  # Skip if this geometry has already been marked as a duplicate
  if (!is_duplicate[i]) {
    # Compare the current geometry with all others
    duplicates = sapply(combined_results_sf$geometry, function(x) identical(x, combined_results_sf$geometry[[i]]))
    # Mark duplicates, but keep the first occurrence
    is_duplicate <- is_duplicate | (duplicates & !is_duplicate)
    is_duplicate[i] <- FALSE  # Ensure the first instance is not marked as duplicate
  }
}

# Filter out duplicates
unique_geometries <- combined_results_sf[!is_duplicate, ]
```

```{r}
st_write(unique_geometries, here("RCA_data_exploration","outputs","rca_poly","unique_border_rca_polygons.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
```




## Fixing border contour from v5.2

```{r}
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.5.R"))

source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.4.R"))
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.3.R"))
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.2.R"))
source(here("RCA_data_exploration/scripts/rca_lines_to_poly_v5.R"))


```

```{r}
# ## not working
## LAST ONE TO BE FIXED
instructions_sample <- polygon_instructions_df %>%
  filter(lat_boundary1 == "34 27.00' N" &
           lat_boundary2 == "U.S. EEZ Boundary South" &
           lon_boundary1 == "100fm_010103.csv" &
           lon_boundary2 == "150fm_010103.csv")%>% .[2,]

# instructions_sample <- polygon_instructions_df %>%
#   filter(lat_boundary1 == "34 27.00' N" &
#            lat_boundary2 == "U.S. EEZ Boundary South" &
#            lon_boundary1 == "50fm_010105.csv" &
#            lon_boundary2 == "200fm_040105.csv") %>% .[3,]

# instructions_sample <- incorrect_lines[1,]

lat_boundary1_name <- instructions_sample$lat_boundary1
lat_boundary2_name <- instructions_sample$lat_boundary2


lon_boundary1_name <- instructions_sample$lon_boundary1
lon_boundary2_name <- instructions_sample$lon_boundary2

# Select latitude lines
selected_latitude_lines <- lat_boundary[lat_boundary$boundary_name == lat_boundary1_name, ] %>% 
  rbind(lat_boundary[lat_boundary$boundary_name == lat_boundary2_name, ])

# Select longitude lines
selected_longitude_lines <- lon_boundary[lon_boundary$boundary_name == lon_boundary1_name, ] %>% 
  rbind(lon_boundary[lon_boundary$boundary_name == lon_boundary2_name, ])

# # Process the selected lines to create polygons
result <- suppressMessages(
  rca_lines_to_polygons_v5.5(selected_longitude_lines, selected_latitude_lines,eez_poly)
)
```

```{r}


longitude_lines <- selected_longitude_lines
latitude_lines <- selected_latitude_lines
  # Clip RCA boundary lines based on latitude delimitation lines.
  
  geometries <- st_geometry(latitude_lines)
  
  # Initialize an empty vector to store max latitudes
  max_latitudes <- numeric(length(geometries))
  
  # Loop through each geometry to find the max latitude
  for (i in seq_along(geometries)) {
    # Extract coordinates for each geometry
    coords <- st_coordinates(geometries[[i]])
    # The Y coordinates (latitude) are in the second column
    latitudes <- coords[, "Y"]
    # Find the maximum latitude for this geometry
    max_latitudes[i] <- max(latitudes)
  }
  
  # You can then add these max latitudes back to your original data frame, if needed
  # latitude_lines$max_latitude <- max_latitudes
  
  boundary_condition_s <- any(latitude_lines$boundary_name == "U.S. EEZ Boundary South")
  # Set min_latitude based on the condition
  min_latitude <- ifelse(boundary_condition_s, 30, min(max_latitudes))
  
  boundary_condition_n <- any(latitude_lines$boundary_name == "U.S. EEZ Boundary Nouth")
  max_latitude <- ifelse(boundary_condition_n, 48.6, max(max_latitudes))
  
  # min_latitude = min(max_latitudes)
  # max_latitude = max(max_latitudes)
  ## Create a bbox that will intersect the RCA lines.
  bbox <- st_as_sfc(st_bbox(c(xmin = -130, xmax = -115, 
                              ymin = min_latitude, ymax = max_latitude), 
                            crs = st_crs(longitude_lines)))
  
  
  ### Patch -----
  # This is a bit redundant but seems to work
  if (any(latitude_lines$boundary_name == "U.S. EEZ Boundary South")){
    difference <- st_intersection(eez_poly,bbox)
    pre_clipped_lines <- st_intersection(longitude_lines, bbox)
    clipped_lines <- st_intersection(pre_clipped_lines, difference)
  } else {
  #   difference <- st_intersection(eez_poly,bbox)
  # pre_clipped_lines <- st_intersection(longitude_lines, bbox)
    clipped_lines <- st_intersection(longitude_lines, bbox)
  }
  
  ### Patch -----
  
  

  
  # MultilineFromIntersections <- function(lat_line, clipped_lines) {
    # Perform intersection
    coastline_intersect <- st_intersection(latitude_lines, longitude_lines)
    
    # Extract points from intersection geometries
    # print("Extracting points from intersection geometries")
    extract_points <- function(coastline_intersect) {
      # Extract points from intersection geometries
      all_points_list <- lapply(1:length(coastline_intersect$geometry), function(i) {
        geom <- coastline_intersect$geometry[i]
        # Extract coordinates depending on geometry type
        coords <- st_coordinates(geom)
        # Select only the X and Y columns
        coords_df <- data.frame(X = coords[, "X"], Y = coords[, "Y"])
        # Create an sf object of points for each geometry
        st_as_sf(x = coords_df, coords = c("X", "Y"), crs = st_crs(coastline_intersect))
      })
      
      points_sf <- do.call(rbind, all_points_list)
      return(points_sf)
    }
    
    # Combine all sf objects into one
    points_sf <- extract_points(coastline_intersect)
    
    
    ## Extract latitudes
    latitudes <- st_coordinates(points_sf)[,2]
    
    if (length(latitudes) %% 2 != 0 | !any(duplicated(latitudes)) | length(unique(latitudes)) == 1) {
      
      # latitudes_rounded <- ceiling(latitudes * 10) / 10 # Define tolerance
      modified_latitudes <- ifelse(latitudes > 48.16668, 48.3, 
                             ifelse(latitudes < 34.44999, 32.4, latitudes))
      #34.45000
      lat_counts <- table(modified_latitudes)
      odd_even <- ifelse(lat_counts %% 2 == 1, "odd", "even")
      unique_lats <- unique(modified_latitudes)
      ## Identify max and min latitude
      max_lat <- max(unique_lats)
      min_lat <- min(unique_lats)
      ## Check if max and/or min latitude have odd occurrences
      max_lat_odd <- odd_even[as.character(max_lat)] == "odd"
      min_lat_odd <- odd_even[as.character(min_lat)] == "odd"
      ## Get latitude border presenting the problem
      find_matching_latitude_indices <- function(sf_object, latitude) {
        
        row_indices <- points_sf %>%
          st_coordinates() %>%
          {which(.[, "Y"] == latitude, arr.ind = TRUE)}
        
        point_to_fix <- points_sf[row_indices,]
        
        matching_indices <- st_intersects(st_buffer(point_to_fix, 1e-6),sf_object) %>% 
          as.numeric()
        
        return(matching_indices)
      }
      
      # Below we solve the intersection issue on the border presenting the problem by searching the
      # nearest points between the lines
      # print("Lack of intersections detected. Solving problem...")
      process_latitude_lines <- function(latitude_lines, latitude) {
        ## Selecting latitude line affected
        matching_indices <- find_matching_latitude_indices(latitude_lines, latitude)
        selected_row <- latitude_lines[matching_indices,]
        ## Searching closest lines for all objects
        nearest_points <- st_nearest_points(clipped_lines,selected_row) %>%
          st_as_sf()
        
        lengths <- as.vector(st_length(nearest_points))
        # Filter out zero-length lines
        non_zero_lengths <- lengths[lengths > 0]
        # Find the shortest non-zero length
        shortest_non_zero_length <- min(non_zero_lengths)
        # Find the index(es) of the LINESTRING(s) with the shortest non-zero length
        shortest_index <- which(lengths == shortest_non_zero_length)
        # Select the shortest non-zero length LINESTRING from the collection
        shortest_line <- nearest_points[shortest_index, ]
        ## Add shortest line to our latitude line so intersection occurs
        latitude_intersect <- selected_row %>%
          st_union(shortest_line)
        ## Update latitude lines
        latitude_lines <- rbind(latitude_lines[-matching_indices,],
                                latitude_intersect %>% st_cast("LINESTRING"))
        return(latitude_lines)
      }
      
      
      
      # Now, we will evaluate the affected latitude lines and apply the fuctions defined above
      if (max_lat_odd & min_lat_odd) {
        # Both the maximum and minimum latitudes have an odd number of points
        updated_max_latitude_lines <- process_latitude_lines(latitude_lines, max(unique(latitudes)))
        
        is_max_lat_in_line <- function(line, max_lat) {
          coords <- st_coordinates(line)
          lat_min <- min(coords[,2])
          lat_max <- max(coords[,2])
          return(max_lat >= lat_min && max_lat <= lat_max)
        }
        
        # Apply the function to filter rows
        updated_max_latitude_lines_filtered <- updated_max_latitude_lines %>%
          filter(sapply(geometry, is_max_lat_in_line, max_lat = max_lat))
        
        
        updated_min_latitude_lines <- process_latitude_lines(latitude_lines, min(unique(latitudes)))
        
        is_min_lat_in_line <- function(line, min_lat) {
          coords <- st_coordinates(line)
          lat_min <- min(coords[,2])
          return(min_lat >= lat_min)
        }
        
        # Apply the function to filter rows
        updated_min_latitude_lines_filtered <- updated_min_latitude_lines %>%
          filter(sapply(geometry, is_min_lat_in_line, min_lat = min_lat)) 
        
        updated_latitude_lines <- rbind(updated_min_latitude_lines_filtered,
                                        updated_max_latitude_lines_filtered)
        
        ## Regenerate points_sf
        coastline_intersect <- st_intersection(updated_latitude_lines, clipped_lines)
        points_sf <- extract_points(coastline_intersect)
        
        
      } else if (max_lat_odd == TRUE & min_lat_odd == FALSE) { # The maximum latitude has an odd number of points
        updated_latitude_lines <- process_latitude_lines(latitude_lines, max(unique(latitudes)))
        ## Regenerate points_sf
        coastline_intersect <- st_intersection(updated_latitude_lines, clipped_lines)
        points_sf <- extract_points(coastline_intersect)
        
      } else if (min_lat_odd == TRUE & max_lat_odd == FALSE) { # The minimum latitude has an odd number of points.
        updated_latitude_lines <- process_latitude_lines(latitude_lines, min(unique(latitudes)))

        coastline_intersect <- st_intersection(updated_latitude_lines, clipped_lines)
        points_sf <- extract_points(coastline_intersect)


        
      } else if (max_lat == min_lat){
        
         lats <- sapply(st_geometry(latitude_lines), function(geom) {
        median(st_coordinates(geom)[, "Y"])
      })
         
      matching_indices <- which(lats == max(unique(latitudes)))

        selected_row <- latitude_lines[-matching_indices,]
        ## Searching closest lines for all objects
        nearest_points <- st_nearest_points(clipped_lines,selected_row) %>%
          st_as_sf()
        
        lengths <- as.vector(st_length(nearest_points))
        
        # Select the  non-zero length LINESTRINGs from the collection
        new_lines <- nearest_points[which(lengths > 0),] 
        
        ## Add shortest line to our latitude line so intersection occurs
        latitude_intersect <- st_union(selected_row, new_lines)
          
        ## Update latitude lines
        updated_latitude_lines <- rbind(latitude_lines[matching_indices,],
                                latitude_intersect %>% st_cast("LINESTRING"))
        coastline_intersect <- st_intersection(updated_latitude_lines, clipped_lines)
        points_sf <- extract_points(coastline_intersect)
      }
    } else {
        updated_latitude_lines <- latitude_lines
      }
    
    
    # Once we have the intersection points in the latitude borders, we can transform them into lines
    # print("Transforming points into lines")
    ## Sort points by longitude to guaranty they construct according to the vertices to fill
    coords <- st_coordinates(points_sf)
    sorted_coords <- coords[order(coords[, 'X']), ]
    sorted_coords <- sorted_coords[order(sorted_coords[, 'Y']), ] # Get X sorting by each latitude value
    ## Recreate sorted points as an sf object
    sorted_points_sf <- st_sf(geometry = st_sfc(lapply(1:nrow(sorted_coords), function(i) {
      st_point(sorted_coords[i, ])
    }), crs = st_crs(points_sf)))
    ## Get updated coordinates after sorting
    coords <- st_coordinates(sorted_points_sf)
    ## Create LINESTRINGs from pairs of sorted points
    lines_list <- vector("list", length = nrow(sorted_points_sf) / 2) # Initialize
    for (i in seq(1, nrow(sorted_points_sf), by = 2)) {
      if (i < nrow(sorted_points_sf)) {
        lines_list[[i]] <- st_linestring(coords[i:(i+1), ])
      }
    }
    lines_list <- lines_list[!sapply(lines_list, is.null)]  # Filter out any NULL elements
    ## Combine into a single MULTILINESTRING
    multiline <- st_sfc(lines_list, crs = st_crs(points_sf))
    multiline_sf <- st_sf(geometry = multiline)
    
    # 
    if(any(latitude_lines$boundary_name == "U.S. EEZ Boundary North")) {



      # Find the index of the geometry with the maximum latitude
      min_lats <- sapply(st_geometry(multiline_sf), function(geom) {
        min(st_coordinates(geom)[, "Y"])
      })

      overall_min_lat <- min(min_lats)
      min_lat_idx <- which(min_lats == overall_min_lat)


      # Creating a bounding box and modifying it
      bbox_mul <- st_bbox(multiline_sf[-min_lat_idx, ])
      bbox_mul["ymin"] <- min_latitude  # min_latitude is defined above
      bbox_mul["ymax"] <- max_latitude  # max_latitude is defined above
      bbox_mul_sf <- st_as_sfc(bbox_mul)

      # Intersecting with the north EEZ line

      north_eez_line <- filter(updated_latitude_lines, boundary_name == "U.S. EEZ Boundary North")

      intersections <- st_intersects(bbox_mul_sf,north_eez_line)
      intersecting_rows <- north_eez_line[unlist(intersections), ] %>%
        st_union() %>%
        st_sf()

      # Replace the geometry in multiline_sf
      multiline_sf[-min_lat_idx, ] <- intersecting_rows


    } else if (any(latitude_lines$boundary_name == "U.S. EEZ Boundary South")) {

      # Find the index of the geometry with the maximum latitude
      max_lats <- sapply(st_geometry(multiline_sf), function(geom) {
        max(st_coordinates(geom)[, "Y"])
      })

      overall_max_lat <- max(max_lats)
      max_lat_idx <- which(max_lats == overall_max_lat)


      # Creating a bounding box and modifying it
      bbox_mul <- st_bbox(multiline_sf[-max_lat_idx, ])
      bbox_mul["ymin"] <- min_latitude  # min_latitude is defined above
      bbox_mul["ymax"] <- max_latitude  # max_latitude is defined above
      bbox_mul_sf <- st_as_sfc(bbox_mul)

      # Intersecting with the north EEZ line

      south_eez_line <- filter(updated_latitude_lines, boundary_name == "U.S. EEZ Boundary South")

      # intersections <- st_intersects(bbox_mul_sf,south_eez_line)
      # intersecting_rows <- south_eez_line[unlist(intersections), ] %>%
      #   st_union() %>%
      #   st_sf()
      # 
      # # Replace the geometry in multiline_sf
      # multiline_sf[-max_lat_idx, ] <- intersecting_rows
      # 
      
      ezz_intersections <- st_intersects(south_eez_line)
      
      # Check if any geometry only intersects with itself
      only_self_intersects <- sapply(1:length(ezz_intersections), function(i) {
        length(ezz_intersections[[i]]) == 1 && ezz_intersections[[i]] == i
      })
      
      # Condition to return FALSE if any geometry only intersects with itself
      if(any(only_self_intersects)) {
        
      } else {
        
        intersections <- st_intersects(bbox_mul_sf, south_eez_line)
        intersecting_rows <- south_eez_line[unlist(intersections), ] %>%
          st_union() %>%
          st_sf()
        
        # Replace the geometry in multiline_sf
        multiline_sf[-max_lat_idx, ] <- st_combine(intersecting_rows) %>% st_sf()
      }
      
      
    }

  #   return(multiline_sf)
  # }
  # 
  # 
  # multiline_sf <- MultilineFromIntersections(latitude_lines, clipped_lines)
  
  
 
  # Create polygon from lines
  # print("Creating polygons from lines")
  ## Combine into a MULTILINESTRING
  multilinestring <- st_union(multiline_sf$geometry)
  target_geometry <- clipped_lines %>% 
    .$geometry 
  combined_geometry <- st_union(target_geometry, multilinestring)
  ## Polygonize the combined MULTILINESTRINGs
  polygon_sf <- st_combine(st_union(combined_geometry)) %>% 
    st_polygonize() %>% 
    st_collection_extract("POLYGON") %>% 
    st_as_sf() %>% 
    rename(geometry = x) %>% 
    mutate(id = row_number(),.before=geometry)
  
  
 leaflet() %>%
    addTiles() %>%
    addPolygons(data = polygon_sf, color = "red", weight=1) %>%
    addPolylines(data = selected_latitude_lines, color = "blue", weight=2) %>%
    addPolylines(data = clipped_lines, color = "orange", weight=2)

```



```{r}


longitude_lines <- selected_longitude_lines
latitude_lines <- selected_latitude_lines

# st_write(longitude_lines, here("RCA_data_exploration","outputs","rca_poly","longitude_lines.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
# 
# st_write(latitude_lines, here("RCA_data_exploration","outputs","rca_poly","latitude_lines.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
  
  
geometries <- st_geometry(latitude_lines)

# Initialize an empty vector to store max latitudes
max_latitudes <- numeric(length(geometries))

# Loop through each geometry to find the max latitude
for (i in seq_along(geometries)) {
  # Extract coordinates for each geometry
  coords <- st_coordinates(geometries[[i]])
  # The Y coordinates (latitude) are in the second column
  latitudes <- coords[, "Y"]
  # Find the maximum latitude for this geometry
  max_latitudes[i] <- max(latitudes)
}

# You can then add these max latitudes back to your original data frame, if needed
# latitude_lines$max_latitude <- max_latitudes

boundary_condition_s <- any(latitude_lines$boundary_name == "U.S. EEZ Boundary South")
# Set min_latitude based on the condition
min_latitude <- ifelse(boundary_condition_s, 32, min(max_latitudes))

# ifelse(boundary_condition_s, 
#                        32.57,
#                        min(max_latitudes))

boundary_condition_n <- any(latitude_lines$boundary_name == "U.S. EEZ Boundary Nouth")
max_latitude <- ifelse(boundary_condition_n, 48.6, max(max_latitudes))

# min_latitude = min(max_latitudes)
  # max_latitude = max(max_latitudes)
  ## Create a bbox that will intersect the RCA lines.
  bbox <- st_as_sfc(st_bbox(c(xmin = -130, xmax = -115, 
                              ymin = min_latitude, ymax = max_latitude), 
                            crs = st_crs(longitude_lines)))


  # Clip RCA boundary lines based on latitude delimitation lines.
  ## Find min and max latitude values from latitude lines.
  # coords = st_coordinates(st_geometry(latitude_lines))
  # latitudes = coords[,2] # The latitude values are in the second column of 'coords'
  # min_latitude = min(latitudes)
  # max_latitude = max(latitudes)
  # ## Create a bbox that will intersect the RCA lines.
  # bbox <- st_as_sfc(st_bbox(c(xmin = -130, xmax = -115, 
  #                             ymin = min_latitude, ymax = max_latitude), 
  #                           crs = st_crs(longitude_lines)))
  
  # eez_poly <- st_polygonize(shoreline[2,]) %>% 
  #   st_collection_extract("POLYGON")
  
  # difference <- st_intersection(eez_poly,bbox)
  # 
  # clipped_lines <- st_intersection(longitude_lines, difference)
  
  ### Patch -----
  # This is a bit redundant but seems to work
  difference <- st_intersection(eez_poly,bbox)
  pre_clipped_lines <- st_intersection(longitude_lines, bbox)
  clipped_lines <- st_intersection(pre_clipped_lines, bbox)
  ### Patch -----
    # leaflet() %>%
    # addTiles() %>%
    # addPolygons(data = bbox, color = "blue", weight=1) %>%
    # addPolygons(data = difference, color = "red", weight=1) %>%
    # addPolylines(data = longitude_lines, color = "orange", weight=2)
    # 
    #     st_write(clipped_lines %>% st_combine(), here("RCA_data_exploration","outputs","rca_poly","coastline_intersect.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
  
  
  # MultilineFromIntersections <- function(lat_line, clipped_lines) {
    # Perform intersection
    coastline_intersect <- st_intersection(latitude_lines, clipped_lines)
    
    # Extract points from intersection geometries
    # print("Extracting points from intersection geometries")
    extract_points <- function(coastline_intersect) {
      # Extract points from intersection geometries
      all_points_list <- lapply(1:length(coastline_intersect$geometry), function(i) {
        geom <- coastline_intersect$geometry[i]
        # Extract coordinates depending on geometry type
        coords <- st_coordinates(geom)
        # Select only the X and Y columns
        coords_df <- data.frame(X = coords[, "X"], Y = coords[, "Y"])
        # Create an sf object of points for each geometry
        st_as_sf(x = coords_df, coords = c("X", "Y"), crs = st_crs(coastline_intersect))
      })
      
      points_sf <- do.call(rbind, all_points_list)
      return(points_sf)
    }
    
    # Combine all sf objects into one
    points_sf <- extract_points(coastline_intersect)
    
  
     leaflet() %>%
    addTiles() %>%
    # addPolygons(data = bbox_mul_sf, color = "red", weight=1) %>%
    # addPolylines(data = selected_latitude_lines, color = "blue", weight=2) %>%
    addPolylines(data = longitude_lines, color = "orange", weight=2) %>%
         addPolylines(data = latitude_lines, color = "green", weight=2) %>%
     addCircles(data=points_sf,color="red")
    
    
    
    ## Extract latitudes
    latitudes <- st_coordinates(points_sf)[,2]
    
    if (length(latitudes) %% 2 != 0 | !any(duplicated(latitudes)) | length(unique(latitudes)) == 1) {
      
      # latitudes_rounded <- ceiling(latitudes * 10) / 10 # Define tolerance
      modified_latitudes <- ifelse(latitudes > 48.16668, 48.3, 
                             ifelse(latitudes < 34.44999, 32.4, latitudes))
      #34.45000
      lat_counts <- table(modified_latitudes)
      odd_even <- ifelse(lat_counts %% 2 == 1, "odd", "even")
      unique_lats <- unique(modified_latitudes)
      ## Identify max and min latitude
      max_lat <- max(unique_lats)
      min_lat <- min(unique_lats)
      ## Check if max and/or min latitude have odd occurrences
      max_lat_odd <- odd_even[as.character(max_lat)] == "odd"
      min_lat_odd <- odd_even[as.character(min_lat)] == "odd"
      ## Get latitude border presenting the problem
      find_matching_latitude_indices <- function(sf_object, latitude) {
        
        row_indices <- points_sf %>%
          st_coordinates() %>%
          {which(.[, "Y"] == latitude, arr.ind = TRUE)}
        
        point_to_fix <- points_sf[row_indices,]
        
        matching_indices <- st_intersects(st_buffer(point_to_fix, 1e-6),sf_object) %>% 
          as.numeric()
        
        return(matching_indices)
      }
      
      # Below we solve the intersection issue on the border presenting the problem by searching the
      # nearest points between the lines
      # print("Lack of intersections detected. Solving problem...")
      process_latitude_lines <- function(latitude_lines, latitude) {
        ## Selecting latitude line affected
        matching_indices <- find_matching_latitude_indices(latitude_lines, latitude)
        selected_row <- latitude_lines[matching_indices,]
        ## Searching closest lines for all objects
        nearest_points <- st_nearest_points(clipped_lines,selected_row) %>%
          st_as_sf()
        
        lengths <- as.vector(st_length(nearest_points))
        # Filter out zero-length lines
        non_zero_lengths <- lengths[lengths > 0]
        # Find the shortest non-zero length
        shortest_non_zero_length <- min(non_zero_lengths)
        # Find the index(es) of the LINESTRING(s) with the shortest non-zero length
        shortest_index <- which(lengths == shortest_non_zero_length)
        # Select the shortest non-zero length LINESTRING from the collection
        shortest_line <- nearest_points[shortest_index, ]
        ## Add shortest line to our latitude line so intersection occurs
        latitude_intersect <- selected_row %>%
          st_union(shortest_line)
        ## Update latitude lines
        latitude_lines <- rbind(latitude_lines[-matching_indices,],
                                latitude_intersect %>% st_cast("LINESTRING"))
        return(latitude_lines)
      }
      
      
      
      # Now, we will evaluate the affected latitude lines and apply the fuctions defined above
      if (max_lat_odd & min_lat_odd) {
        # Both the maximum and minimum latitudes have an odd number of points
        updated_max_latitude_lines <- process_latitude_lines(latitude_lines, max(unique(latitudes)))
        
        is_max_lat_in_line <- function(line, max_lat) {
          coords <- st_coordinates(line)
          lat_min <- min(coords[,2])
          lat_max <- max(coords[,2])
          return(max_lat >= lat_min && max_lat <= lat_max)
        }
        
        # Apply the function to filter rows
        updated_max_latitude_lines_filtered <- updated_max_latitude_lines %>%
          filter(sapply(geometry, is_max_lat_in_line, max_lat = max_lat))
        
        
        updated_min_latitude_lines <- process_latitude_lines(latitude_lines, min(unique(latitudes)))
        
        is_min_lat_in_line <- function(line, min_lat) {
          coords <- st_coordinates(line)
          lat_min <- min(coords[,2])
          return(min_lat >= lat_min)
        }
        
        # Apply the function to filter rows
        updated_min_latitude_lines_filtered <- updated_min_latitude_lines %>%
          filter(sapply(geometry, is_min_lat_in_line, min_lat = min_lat)) 
        
        updated_latitude_lines <- rbind(updated_min_latitude_lines_filtered,
                                        updated_max_latitude_lines_filtered)
        
        ## Regenerate points_sf
        coastline_intersect <- st_intersection(updated_latitude_lines, clipped_lines)
        points_sf <- extract_points(coastline_intersect)
        
        
      } else if (max_lat_odd == TRUE & min_lat_odd == FALSE) { # The maximum latitude has an odd number of points
        updated_latitude_lines <- process_latitude_lines(latitude_lines, max(unique(latitudes)))
        ## Regenerate points_sf
        coastline_intersect <- st_intersection(updated_latitude_lines, clipped_lines)
        points_sf <- extract_points(coastline_intersect)
        
      } else if (min_lat_odd == TRUE & max_lat_odd == FALSE) { # The minimum latitude has an odd number of points.
        updated_latitude_lines <- process_latitude_lines(latitude_lines, min(unique(latitudes)))

        coastline_intersect <- st_intersection(updated_latitude_lines, clipped_lines)
        points_sf <- extract_points(coastline_intersect)


        
      } else if (max_lat == min_lat){
        
         lats <- sapply(st_geometry(latitude_lines), function(geom) {
        median(st_coordinates(geom)[, "Y"])
      })
         
      matching_indices <- which(lats == max(unique(latitudes)))

        selected_row <- latitude_lines[-matching_indices,]
        ## Searching closest lines for all objects
        nearest_points <- st_nearest_points(clipped_lines,selected_row) %>%
          st_as_sf()
        
        lengths <- as.vector(st_length(nearest_points))
        
        # Select the  non-zero length LINESTRINGs from the collection
        new_lines <- nearest_points[which(lengths > 0),] 
        
        ## Add shortest line to our latitude line so intersection occurs
        latitude_intersect <- st_union(selected_row, new_lines)
          
        ## Update latitude lines
        updated_latitude_lines <- rbind(latitude_lines[matching_indices,],
                                latitude_intersect %>% st_cast("LINESTRING"))
        coastline_intersect <- st_intersection(updated_latitude_lines, clipped_lines)
        points_sf <- extract_points(coastline_intersect)
      }
    } else {
        updated_latitude_lines <- latitude_lines
      }
    
      
    # Once we have the intersection points in the latitude borders, we can transform them into lines
    # print("Transforming points into lines")
    ## Sort points by longitude to guaranty they construct according to the vertices to fill
    coords <- st_coordinates(points_sf)
    sorted_coords <- coords[order(coords[, 'X']), ]
    sorted_coords <- sorted_coords[order(sorted_coords[, 'Y']), ] # Get X sorting by each latitude value
    ## Recreate sorted points as an sf object
    sorted_points_sf <- st_sf(geometry = st_sfc(lapply(1:nrow(sorted_coords), function(i) {
      st_point(sorted_coords[i, ])
    }), crs = st_crs(points_sf)))
    ## Get updated coordinates after sorting
    coords <- st_coordinates(sorted_points_sf)
    ## Create LINESTRINGs from pairs of sorted points
    lines_list <- vector("list", length = nrow(sorted_points_sf) / 2) # Initialize
    for (i in seq(1, nrow(sorted_points_sf), by = 2)) {
      if (i < nrow(sorted_points_sf)) {
        lines_list[[i]] <- st_linestring(coords[i:(i+1), ])
      }
    }
    lines_list <- lines_list[!sapply(lines_list, is.null)]  # Filter out any NULL elements
    ## Combine into a single MULTILINESTRING
    multiline <- st_sfc(lines_list, crs = st_crs(points_sf))
    multiline_sf <- st_sf(geometry = multiline)
    
     leaflet() %>%
    addTiles() %>%
    # addPolygons(data = bbox_mul_sf, color = "red", weight=1) %>%
    # addPolylines(data = selected_latitude_lines, color = "blue", weight=2) %>%
    addPolylines(data = longitude_lines, color = "orange", weight=2) %>%
         addPolylines(data = multiline_sf, color = "green", weight=2) %>%
     addCircles(data=points_sf,color="red")
   
    
  #   if(any(latitude_lines$boundary_name == "U.S. EEZ Boundary North")){
  #     
  #     geometries_mul <- st_geometry(multiline_sf)
  # 
  #     max_lat_mul <- numeric(length(geometries_mul))
  # 
  #     # Loop through each geometry to find the max latitude
  #     for (i in seq_along(geometries_mul)) {
  #       # Extract coordinates for each geometry
  #       coords <- st_coordinates(geometries_mul[[i]])
  #       # The Y coordinates (latitude) are in the second column
  #       latitudes <- coords[, "Y"]
  #       # Find the maximum latitude for this geometry
  #       max_lat_mul[i] <- max(latitudes)
  #     }
  #     
  #     
  #     which.max(max_lat_mul)
  # 
  #           # You can then add these max latitudes back to your original data frame, if needed
  #     multiline_sf_1 <- multiline_sf
  #     bbox_mul <- st_bbox(multiline_sf_1[which.max(max_lat_mul),])
  #     bbox_mul["ymin"] <- min_latitude
  #     bbox_mul["ymax"] <- max_latitude
  #     bbox_mul_sf <- st_as_sfc(bbox_mul)
  #     
  #     north_eez_line <- latitude_lines[which(latitude_lines$boundary_name == "U.S. EEZ Boundary North"),]
  #     
  #     
  #     intersection_geometry <- st_intersection(north_eez_line, bbox_mul_sf) %>%
  # st_geometry() %>%  st_sf( )
  # 
  #     
  #     multiline_sf[which.max(max_lat_mul),] <- intersection_geometry
  #     
  # 
  #   }
    
    if(any(latitude_lines$boundary_name == "U.S. EEZ Boundary North" 
           )) {
      
      
      # Find the index of the geometry with the maximum latitude
      min_lats <- sapply(st_geometry(multiline_sf), function(geom) {
        min(st_coordinates(geom)[, "Y"])
      })

      overall_min_lat <- min(min_lats)
      min_lat_idx <- which(min_lats == overall_min_lat)


      # Creating a bounding box and modifying it
      bbox_mul <- st_bbox(multiline_sf[-min_lat_idx, ])
      bbox_mul["ymin"] <- min_latitude  # min_latitude is defined above
      bbox_mul["ymax"] <- max_latitude  # max_latitude is defined above
      bbox_mul_sf <- st_as_sfc(bbox_mul)

      # Intersecting with the north EEZ line
      
      north_eez_line <- filter(updated_latitude_lines, boundary_name == "U.S. EEZ Boundary North")
   
      intersections <- st_intersects(bbox_mul_sf,north_eez_line)
      intersecting_rows <- north_eez_line[unlist(intersections), ] %>%
        st_union() %>%
        st_sf()
      
      # intersecting_rows <- st_intersection(north_eez_line, bbox_mul_sf) %>%
      #   st_geometry() %>%  st_sf( )

      # Replace the geometry in multiline_sf
      multiline_sf[-min_lat_idx, ] <- intersecting_rows
      
      
      leaflet() %>%
    addTiles() %>%
    # addPolygons(data = bbox_mul_sf, color = "red", weight=1) %>%
    # addPolylines(data = selected_latitude_lines, color = "blue", weight=2) %>%
    addPolylines(data = clipped_lines, color = "orange", weight=2) %>%
         addPolylines(data = multiline_sf, color = "green", weight=2) %>%
     addCircles(data=points_sf,color="red")

      
      # 
      # 
      # # Find the index of the geometry with the maximum latitude
      # max_lat_idx <- which.max(sapply(st_geometry(multiline_sf), function(geom) {
      #   max(st_coordinates(geom)[, "Y"])
      # }))
      # 
      # # Creating a bounding box and modifying it
      # bbox_mul <- st_bbox(multiline_sf[max_lat_idx, ])
      # bbox_mul["ymin"] <- min_latitude  # min_latitude is defined above
      # bbox_mul["ymax"] <- max_latitude  # max_latitude is defined above
      # bbox_mul_sf <- st_as_sfc(bbox_mul)
      # 
      # # Intersecting with the north EEZ line
      # north_eez_line <- filter(updated_latitude_lines, boundary_name == "U.S. EEZ Boundary North")
      # intersection_geometry <- st_intersection(north_eez_line, bbox_mul_sf) %>% 
      #   st_geometry() %>%
      #   st_sf()
      # 
      # # Replace the geometry in multiline_sf
      # multiline_sf[max_lat_idx, ] <- intersection_geometry
      
    } else if (any(latitude_lines$boundary_name == "U.S. EEZ Boundary South" )) {

      # Find the index of the geometry with the maximum latitude
      max_lats <- sapply(st_geometry(multiline_sf), function(geom) {
        max(st_coordinates(geom)[, "Y"])
      })

      overall_max_lat <- max(max_lats)
      max_lat_idx <- which(max_lats == overall_max_lat)


      # Creating a bounding box and modifying it
      bbox_mul <- st_bbox(multiline_sf[-max_lat_idx, ])
      bbox_mul["ymin"] <- min_latitude  # min_latitude is defined above
      bbox_mul["ymax"] <- max_latitude  # max_latitude is defined above
      bbox_mul_sf <- st_as_sfc(bbox_mul)

      # Intersecting with the north EEZ line
      
      south_eez_line <- filter(updated_latitude_lines, boundary_name == "U.S. EEZ Boundary South")
      
      
      ezz_intersections <- st_intersects(south_eez_line)

      # Check if any geometry only intersects with itself
      only_self_intersects <- sapply(1:length(ezz_intersections), function(i) {
        length(ezz_intersections[[i]]) == 1 && ezz_intersections[[i]] == i
      })
      
      # Condition to return FALSE if any geometry only intersects with itself
      if(any(only_self_intersects)) {
        
      } else {
        
      intersections <- st_intersects(bbox_mul_sf, south_eez_line)
      intersecting_rows <- south_eez_line[unlist(intersections), ] %>%
        st_union() %>%
        st_sf()

      # Replace the geometry in multiline_sf
      multiline_sf[-max_lat_idx, ] <- st_combine(intersecting_rows) %>% st_sf()
      }
      
      

    }

    #
    #
    
 

  #   return(multiline_sf)
  # }
  
    #  st_write(multiline_sf %>% st_cast("LINESTRING") %>% .[2,], here("RCA_data_exploration","outputs","rca_poly","multiline_sf2.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
    # st_write(clipped_lines, here("RCA_data_exploration","outputs","rca_poly","clipped_lines.gpkg"), layer = "polygons_layer", driver = "GPKG", delete_layer = TRUE)
  
  # lat_shorelines <- MultilineFromIntersections(latitude_lines, clipped_lines)
    lat_shorelines <- multiline_sf
  # Create polygon from lines
  # print("Creating polygons from lines")
  ## Combine into a MULTILINESTRING
  multilinestring <- st_union(lat_shorelines$geometry)
  target_geometry <- clipped_lines %>% 
    # filter(area_name == "mainland" & land_ref == "mainland") %>%
    .$geometry 
  combined_geometry <- st_union(target_geometry, multilinestring)
  ## Update the geometry with the combined geometry
  # clipped_lines$geometry[clipped_lines$area_name == "mainland" & clipped_lines$land_ref == "mainland"] <- combined_geometry
  ## Polygonize the combined MULTILINESTRINGs
  polygon_sf <- st_combine(st_union(combined_geometry)) %>% 
    st_polygonize() %>% 
    st_collection_extract("POLYGON") %>% 
    st_as_sf() %>% 
    rename(geometry = x) %>% 
    mutate(id = row_number(),.before=geometry)
  
  # # Clip out any inner polygon
  # print("First inner polygons clip out")
  # # To do it we will evaluate relationships between polygons based on whether they intersect and then exclude the smaller polygons within those associations
  # ## Get information on intersection polygons
  # intersections <- st_intersects(polygon_sf, sparse = TRUE)
  # ## Get areas
  # print("1")
  # areas <- st_area(polygon_sf)
  # print("2")
  # area_df <- data.frame(area = areas)
  # print("3")
  # 
  # # area_df$id <- 1:nrow(area_df)
  # area_df$id <- as.numeric(rownames(area_df))
  # print("4")
  # 
  # keep_ids <- numeric()
  # print("5")
  # ## For each polygon, find the one with the biggest area among those it intersects with
  # for (i in 1:length(intersections)) {
  #   if(length(intersections[[i]]) > 0) {
  #     # Find the intersecting polygons and their areas
  #     intersecting_areas <- area_df[area_df$id %in% intersections[[i]], ]
  #     # Find the polygon(s) with the maximum area
  #     max_area_id <- intersecting_areas[which.max(intersecting_areas$area), "id"]
  #     # Add to keep_ids
  #     keep_ids <- unique(c(keep_ids, max_area_id))
  #   }
  # }
  # print("6")
  # ## Keep only the polygons with the largest area in their intersection groups
  # rca_coastline_polygons_filtered <- polygon_sf[keep_ids, ]
  
 leaflet() %>%
    addTiles() %>%
    addPolygons(data = polygon_sf, color = "red", weight=1) %>%
    # addPolylines(data = selected_latitude_lines, color = "blue", weight=2) %>%
    addPolylines(data = clipped_lines, color = "orange", weight=2)

 
```
