---
title: "Construct Data for GLORYS-based SDMs"
output: html_document
date: "2023-10-11"
---

```{r setup, include=FALSE}
# remotes::install_github("pbs-assess/sdmTMB",ref="stacking")
library(sdmTMB)
library(nwfscSurvey)
library(tidyverse)
library(lubridate)
library(sf)
library(nngeo)
library(marmap)
library(here)
library(rnaturalearth)
library(viridis)
library(cowplot)
library(RANN)
library(tictoc)
library(CopernicusMarine)
library(tidync)

knitr::opts_chunk$set(echo = TRUE)
options(dplyr.summarise.inform=FALSE)
```

```{r plottheme}
# ggplot theme
plot_theme <-   theme_minimal()+
  theme(text=element_text(family="sans",size=10,color="black"),
        legend.text = element_text(size=14),
        axis.title=element_text(family="sans",size=14,color="black"),
        axis.text=element_text(family="sans",size=8,color="black"),
        panel.grid.major = element_line(color="gray50",linetype=3))
theme_set(plot_theme)
```

```{r}
# spatial background map
# load west cost land for mapping
coast <- ne_states(country='United States of America',returnclass = 'sf') %>% 
  filter(name %in% c('California','Oregon','Washington','Nevada')) %>%
  st_transform(crs = "+proj=utm +zone=10 +datum=WGS84 +units=km")

```

# Purpose

Prepare species and environmental covariate data for use in `sdmTMB` model fitting and for species distribution projections. In this iteration of the analysis, we use GLORYS data from Mercator Ocean. We will download, clean, and organize the GLORYS data, and then attach it to the NWFSC bottom trawl survey data.

# Build GLORYS data

In this section, we download and clean the GLORYS data.

## Download GLORYS

This obviously takes a while to download, so don't run it every time

```{r, eval=F}
# Script to download GLORYS data directly from Copernicus Servers
# Requires a Copernicus marine service account
# to browse around datasets, you can use copernicus_products_list()

#Set directories
home_dir = here()
out_dir = here('gf sdms',"data","GLORYS")

#Specify lat/lon/depth bounds
REGION = c(-138,26,-114,51)
VERT_RANGE =  c(0, 5000) 
```

Download temperature

```{r, eval=F}
copernicus_product_details(product       = "GLOBAL_MULTIYEAR_PHY_001_030",
                           layer         = "cmems_mod_glo_phy_my_0.083_P1M-m",
                           variable = "thetao")

copernicus_download_motu(
  username = "",
  password = "",
  destination   = paste0(out_dir,'/GLORYS-Monthly-2003-2020_thetao.nc'),
  product       = "GLOBAL_MULTIYEAR_PHY_001_030",
  layer         = "cmems_mod_glo_phy_my_0.083_P1M-m",
  variable      = "sea_water_velocity",
  output        = "netcdf",
  region        = REGION,
  timerange     = c("2003-01-01", "2020-12-16"),
  sub_variables = 'thetao',
  verticalrange = VERT_RANGE,
  overwrite=TRUE
)
```

Download oxygen

```{r oxygen,eval=F}
copernicus_product_details(product       = "GLOBAL_MULTIYEAR_BGC_001_029",
                           layer         = "cmems_mod_glo_bgc_my_0.25_P1M-m",
                           variable = "o2")

copernicus_download_motu(
  username = "oliu",
  password = "*********************",
  destination   = paste0(out_dir,'/GLORYS-Monthly-2003-2020_o2.nc'),
  product       = "GLOBAL_MULTIYEAR_BGC_001_029",
  layer         = "cmems_mod_glo_bgc_my_0.25_P1M-m",
  variable      = "o2",
  output        = "netcdf",
  region        = REGION,
  timerange     = c("2003-01-01", "2020-12-16"),
  sub_variables = 'o2',
  verticalrange = VERT_RANGE,
  overwrite=TRUE
)
```

## Find Bottom Depth

Find the bottom depths of each GLORYS cell to facilitate matching to trawl data

```{r}
# take the first year of each model
glorys_phy_bot <- tidync(here('gf sdms','data','GLORYS','GLORYS-Monthly-2003-2020_thetao.nc')) %>% 
  hyper_filter(time=index==1) %>% 
  hyper_tibble() %>% 
  group_by(longitude,latitude) %>% 
  summarise(bot=last(depth)) %>% 
  ungroup()

# visualize
glorys_phy_bot %>% filter(longitude>-130) %>% ggplot(aes(longitude,latitude,color=bot))+geom_point()+coord_equal()
glorys_phy_bot %>% filter(longitude>-130) %>% ggplot(aes(bot))+geom_density()

# for the BGC model
glorys_bgc_bot <- tidync(here('gf sdms','data','GLORYS','GLORYS-Monthly-2003-2020_o2.nc')) %>% 
  hyper_filter(time=index==1) %>% 
  hyper_tibble() %>% 
  group_by(longitude,latitude) %>% 
  summarise(bot=last(depth)) %>% 
  ungroup()

# visualize
glorys_bgc_bot %>% filter(longitude>-130) %>% ggplot(aes(longitude,latitude,color=bot))+geom_point()+coord_equal()
glorys_bgc_bot %>% filter(longitude>-130) %>% ggplot(aes(bot))+geom_density()

```

## Build Grid IDs

For each version of GLORYS (1/12 deg and 1/4 deg), build a grid identifier to facilitate matching to trawl data

```{r}
glorys_phy_grid <- glorys_phy_bot %>%
  st_as_sf(coords=c('longitude','latitude'),crs=4326,remove = F) %>%  
  st_transform(crs = "+proj=utm +zone=10 +datum=WGS84 +units=km") %>% 
  mutate(gridID_phy=row_number()) %>% 
  mutate(lonUTM=st_coordinates(.)[,1],latUTM=st_coordinates(.)[,2]) %>% 
  st_set_geometry(NULL)

glorys_bgc_grid <- glorys_bgc_bot %>%
  st_as_sf(coords=c('longitude','latitude'),crs=4326,remove = F) %>%  
  st_transform(crs = "+proj=utm +zone=10 +datum=WGS84 +units=km") %>% 
  mutate(gridID_bgc=row_number()) %>% 
  mutate(lonUTM=st_coordinates(.)[,1],latUTM=st_coordinates(.)[,2])%>% 
  st_set_geometry(NULL)
```

Also, we can build a matching key to help translate between grids

```{r}
bgc_locs <- glorys_bgc_grid %>% 
  st_as_sf(coords=c('lonUTM','latUTM'),crs = "+proj=utm +zone=10 +datum=WGS84 +units=km")
phy_locs <- glorys_phy_grid %>% 
  st_as_sf(coords=c('lonUTM','latUTM'),crs = "+proj=utm +zone=10 +datum=WGS84 +units=km")

# nearest neighbors, PHY-->BGC
phy_nn <- nngeo::st_nn(phy_locs,bgc_locs) %>% unlist()

glorys_phy_grid <- glorys_phy_grid %>% 
  mutate(gridID_bgc_match=bgc_locs$gridID_bgc[phy_nn])

```


# Build Trawl Data

Using package `nwfscSurvey`, download and organize WCBTS data for species of interest

```{r, eval=F}
# species
# species list
# spp.list <- list.files(here('model output','climate novelty','roms'))
available_spp <- PullSpp.fn()
# match
# fill in missing cells if we can. problem species are Dover sole, english sole, pacific grenadier, pacific ocean perch, pacifific sanddab, pacific spiny dogfish
# corrections <- c("Dover sole","English sole","Pacific grenadier","Pacific ocean perch","Pacific sanddab","Pacific spiny dogfish")

spp.list <- c("arrowtooth flounder","aurora rockfish","big skate","bocaccio","canary rockfish","chilipepper","curlfin sole","darkblotched rockfish","Dover sole","English sole","greenstriped rockfish","lingcod","longnose skate","longspine thornyhead","Pacific grenadier","Pacific hake","Pacific ocean perch","Pacific sanddab","Pacific spiny dogfish","petrale sole","rex sole","sablefish","sharpchin rockfish","shortbelly rockfish","shortraker rockfish","shortspine thornyhead","slender sole","splitnose rockfish","spotted ratfish","stripetail rockfish","widow rockfish","yelloweye rockfish","yellowtail rockfish")

# make sure these match to records in the survey list
spp_trawl_match <- tibble(lower=spp.list) %>% 
  left_join(available_spp,by=c("lower"="common"))

# pull the data
trawl <- PullCatch.fn(Name=spp.list,YearRange=c(2003,2020),SurveyName = "NWFSC.Combo")
# organize and rename some variables
trawl <- trawl %>% 
  # convert date from character to date
  mutate(date=as_date(Date),
         Trawl_id=as.numeric(Trawl_id)) %>% 
  # clean up some other columns to be consistent
  mutate(species=tolower(Common_name)) %>% 
  rename(year=Year,depth_trawl=Depth_m,area_swept_ha=Area_Swept_ha)

# save raw
write_rds(trawl,here('gf sdms','data','nwfsc_trawl_data_Nov2023.rds'))
```
# Substrate Data

```{r}
substrate <- read_rds(here('gf sdms','data','substrate','substrate_by_trawlID.rds'))
substrate_thin <- substrate %>% 
  dplyr::select(TRAWL_ID,prop_hard_mixed)
```


# Spatial Matching

We need to join trawl locations to their nearest GLORYS grid cell

## Trawl Locations

Import trawl data
```{r}
trawl <- read_rds(here('gf sdms','data','nwfsc_trawl_data_Nov2023.rds'))
```

Get locations

```{r}
trawl_locs <- trawl %>% 
  distinct(Longitude_dd,Latitude_dd,.keep_all = T) %>% 
  # select the variable we'll use to match
  dplyr::select(date,Longitude_dd,Latitude_dd,depth_trawl) %>% 
  # convert to UTM10
  st_as_sf(coords=c('Longitude_dd','Latitude_dd'),crs=4326,remove = F) %>%  
  st_transform(crs = "+proj=utm +zone=10 +datum=WGS84 +units=km") %>%
  mutate(lontrawlUTM=st_coordinates(.)[,1],lattrawlUTM=st_coordinates(.)[,2])%>% 
  st_set_geometry(NULL)
```

## Grid Match

Here are the datasets we are trying to match
```{r}
ggplot()+
  geom_point(data=glorys_phy_grid %>% filter(lonUTM>200),aes(lonUTM,latUTM,color=bot))+
  geom_point(data=trawl_locs,aes(lontrawlUTM,lattrawlUTM),color='red',size=0.5)+
  coord_equal()
```

Find nearest neighbor matches between trawl and GLORYS

```{r}
trawlxy <- trawl_locs %>% dplyr::select(lontrawlUTM,lattrawlUTM)
glorys_phy_xy <- glorys_phy_grid %>% dplyr::select(lonUTM,latUTM)
glorys_bgc_xy <- glorys_bgc_grid %>% dplyr::select(lonUTM,latUTM)

# each trawl location matched to its nearest neighbor from GLORYS physics
trawl_glorys_phy_nn <- nn2(glorys_phy_xy,trawlxy,k=1)[[1]]

# each trawl location matched to its nearest neighbor from GLORYS biogeochemistry
trawl_glorys_bgc_nn <- nn2(glorys_bgc_xy,trawlxy,k=1)[[1]]

# add these identifiers to the trawl locations datasets
trawl_glorys_match <- trawl_locs %>% 
  mutate(glorys_match_phy=as.integer(trawl_glorys_phy_nn),
         glorys_match_bgc=as.integer(trawl_glorys_bgc_nn))
```


# Join to Trawl Data

## Match to Substrate

```{r}
trawl <- trawl %>% 
  # Join substrate by just trawl ID number
  left_join(substrate_thin,by=c("Trawl_id"="TRAWL_ID")) %>% 
  left_join(trawl_glorys_match,by=c("date"="date","Longitude_dd","Latitude_dd","depth_trawl")) %>% 
  # thin columns to just the ones we (may) need for SDMs
  dplyr::select(date,year,species,cpue_kg_km2,lattrawlUTM,lontrawlUTM,depth_trawl,area_swept_ha,glorys_match_bgc,glorys_match_phy,prop_hard_mixed)

# check
trawl %>%
  filter(year%in%c(2003:2005)) %>% 
  ggplot(aes(lontrawlUTM,lattrawlUTM,color=prop_hard_mixed))+
  geom_point(size=0.5)+
  coord_equal()+
  scale_color_viridis()
```

## Join

The last thing we need is GLORYS time conversion. According to the GLORYS metadata, time is in "hours since 1950-01-01".

```{r}
glorys_times <- tidync(here('gf sdms','data','GLORYS','GLORYS-Monthly-2003-2020_thetao.nc')) %>% 
  activate("D0") %>% 
  hyper_tibble() %>% 
  # make a match from GLORYS time to a normal date-time string
  mutate(glorys_dttm=as_datetime("1950-01-01 00:00:00")+hours(time)) %>% 
  mutate(year=year(glorys_dttm),mth=month(glorys_dttm))

glimpse(glorys_times)
range(glorys_times$year)
# ncdf4::nc_open(here('data','GLORYS','GLORYS-Monthly-2003-2020_thetao.nc'))
```

Short function to join one year of data at a time (so the import from the .nc file isn't too onerous)
```{r}
join_glorys_trawl <- function(yr){
  trawl_yr <- trawl %>% 
    filter(year==yr) %>% 
    # month identifier
    mutate(mth=month(date))
  times_we_need <- glorys_times %>% 
    filter(year==yr) %>% 
    pull(time)
  tstart <- min(times_we_need); tstop <- max(times_we_need)
  
  glorys_yr_phy <- tidync(here('gf sdms','data','GLORYS','GLORYS-Monthly-2003-2020_thetao.nc')) %>% 
    # pre-filter for the correct year
    hyper_filter(time=time>=tstart&time<=tstop,longitude=longitude>-130) %>% 
    hyper_tibble() %>% 
    group_by(longitude,latitude) %>% 
    slice_max(depth) %>% 
    ungroup() %>% 
    # join grid identifier
    left_join(glorys_phy_grid,by=c('longitude','latitude')) %>% 
    # join time identifier
    left_join(glorys_times,by='time') %>% 
    mutate(mth=month(glorys_dttm))
  
  glorys_yr_bgc <- tidync(here('gf sdms','data','GLORYS','GLORYS-Monthly-2003-2020_o2.nc')) %>% 
    hyper_filter(time=time>=tstart&time<=tstop,longitude=longitude>-130) %>% 
    hyper_tibble() %>% 
    group_by(longitude,latitude) %>% 
    slice_max(depth) %>% 
    ungroup() %>% 
    left_join(glorys_bgc_grid,by=c('longitude','latitude')) %>% 
    # join time identifier
    left_join(glorys_times,by='time') %>% 
    mutate(mth=month(glorys_dttm)) %>% 
    dplyr::select(o2,mth,year,gridID_bgc)
  
  # left_join glorys to trawl for year 'yr'
  trawl_glorys_yr <- trawl_yr %>% 
    left_join(glorys_yr_phy,by=c("glorys_match_phy"="gridID_phy","mth","year")) %>% 
    left_join(glorys_yr_bgc,by=c("glorys_match_bgc"="gridID_bgc","mth","year"))
  
  # clean up columns and finish
  out <- trawl_glorys_yr %>% 
    dplyr::select(date_trawl=date,year,species,cpue_kg_km2,lattrawlUTM,lontrawlUTM,depth_trawl,glorys_dttm,
                  depth_glorys=depth,glorys_time=time,longlorysUTM=lonUTM,latglorysUTM=latUTM,prop_hard_mixed,thetao,o2)
  out
}
```

Test this for one year
```{r}
trawl_glorys_2003 <- join_glorys_trawl(yr=2003)
glimpse(trawl_glorys_2003)

# How well do the depths match?
depth_trawl_vs_glorys <- trawl_glorys_2003 %>% 
  ggplot(aes(depth_trawl,depth_glorys))+
  geom_point(size=0.5)+
  geom_smooth(method='lm')+
  geom_smooth(color='red')+
  labs(x="Depth of Trawl",y="Depth from GLORYS")
depth_trawl_vs_glorys

depth_trawl_vs_glorys_diff <- trawl_glorys_2003 %>% 
  mutate(depthdiff=depth_trawl-depth_glorys) %>% 
  ggplot(aes(depth_trawl,depthdiff))+
  geom_point(size=0.5)+
  geom_hline(yintercept=0)+
  geom_smooth()+
  labs(x="Depth of Trawl",y="Trawl Minus GLORYS")
depth_trawl_vs_glorys_diff
```

Do the join for all years

```{r}
trawl_glorys_joined <- purrr::map_df(2003:2020,join_glorys_trawl)
# for some reason this didn't run with all years at once (maybe memory hole), so just row bind
# trawl_glorys_2018 <- join_glorys_trawl(2018)
# trawl_glorys_joined <- trawl_glorys_joined %>% 
#   bind_rows(trawl_glorys_2018)
```

## Save
```{r}
write_rds(trawl_glorys_joined,here('gf sdms','data','trawl_glorys_joined.rds'))
```

# Hindcast Grid

Also make a version of this that is for projection. For now, make only 1 annual prediction, so use August conditions


```{r}
make_glorys_proj_grid<- function(yr){

  times_we_need <- glorys_times %>% 
    filter(year==yr,mth==8) %>% 
    pull(time)
  tstart <- min(times_we_need); tstop <- max(times_we_need)
  
  # Physical vars
  glorys_yr_phy <- tidync(here('gf sdms','data','GLORYS','GLORYS-Monthly-2003-2020_thetao.nc')) %>% 
    # pre-filter for the correct year
    hyper_filter(time=time>=tstart&time<=tstop,longitude=longitude>-130) %>% 
    hyper_tibble() %>% 
    group_by(longitude,latitude) %>% 
    slice_max(depth) %>% 
    ungroup() %>% 
    # join grid identifier
    left_join(glorys_phy_grid,by=c('longitude','latitude')) %>% 
    # join time identifier
    left_join(glorys_times,by='time') %>% 
    mutate(mth=month(glorys_dttm))
  
  # BGC vars (O2)
  glorys_yr_bgc <- tidync(here('gf sdms','data','GLORYS','GLORYS-Monthly-2003-2020_o2.nc')) %>% 
    hyper_filter(time=time>=tstart&time<=tstop,longitude=longitude>-130) %>% 
    hyper_tibble() %>% 
    group_by(longitude,latitude) %>% 
    slice_max(depth) %>% 
    ungroup() %>% 
    left_join(glorys_bgc_grid,by=c('longitude','latitude')) %>% 
    # join time identifier
    left_join(glorys_times,by='time') %>% 
    mutate(mth=month(glorys_dttm)) %>% 
    dplyr::select(year,mth,gridID_bgc,o2)
  
  #join BGC to PHY
  glorys_yr_proj <- glorys_yr_phy %>% left_join(glorys_yr_bgc,by=join_by(year,mth,gridID_bgc_match==gridID_bgc))
  
  # clean up columns and finish
  out <- glorys_yr_proj %>% 
    drop_na()
    
  out
}
```

Apply

```{r}
glorys_pred_grid <- purrr::map(2003:2020,make_glorys_proj_grid) %>% list_rbind()
```

Visualize

```{r}
glorys_pred_grid %>% filter(year==2003) %>% ggplot(aes(lonUTM,latUTM,color=thetao))+geom_point()+coord_equal()+scale_color_viridis()
```

Save

```{r}
write_rds(glorys_pred_grid,here('gf sdms','data',"GLORYS",'glorys_hindcast_grid.rds'))
```

# RCA Grid

For this project, we also want to make a higher-resolution grid that focuses on the RCA footprint

```{r}
# FROM BLAKE 10.23.2024
# Corner,Easting_m,Northing_m
# UL,293407.62,5374166.82
# UR,1052172.05,5374166.82
# LR,1052172.05,3613572.88
# LL,293407.62,3613572.88
# EPSG: 26910
library(stars)
rca_cent <- read_csv(here('gf sdms','data','Overlay_200m_gridcell_centroid_pts_xy_UTM.csv'))
test<- rca_cent %>% st_as_sf(coords = c("Easting_m","Northing_m"),crs=26910)

# test with just the empty raster
tic("rasterizing:")
testrast <- st_rasterize(test)
toc()
# write_stars(testrast,dsn=here('gf sdms','data','test_raster.tif'))
```




Function to extract from GLORYS to this high-resolution grid. We'll do this with nearest neighbors, as before

```{r}
# find nearest neighbors
t1 <- rca_cent %>% sample_n(10000) %>% ggplot()+geom_point(aes(Easting_m/1000,Northing_m/1000),color='red')+coord_equal()
t1+geom_point(data=glorys_pred_grid %>% sample_n(10000),aes(lonUTM,latUTM),shape=1)
# looks like they line up

glorys_pred_sf <- glorys_pred_grid %>% 
  distinct(gridID_phy,lonUTM,latUTM) %>% 
  mutate(lonUTM_m=lonUTM*1000,latUTM_m=latUTM*1000) %>% 
  st_as_sf(coords=c("lonUTM_m","latUTM_m"),crs=26910)

rca_pred_sf <- rca_cent %>% 
  st_as_sf(coords=c("Easting_m","Northing_m"),crs=26910)

rca_glorys_nn <- st_nn(rca_pred_sf,glorys_pred_sf) %>% unlist()

# baseline RCA grid with glorys grid match we just calculated
rca_base_grid <- rca_cent %>% mutate(gridID_glorys_match=glorys_pred_grid$gridID_phy[rca_glorys_nn])

# baseline GLORYS grid for matching to RCA (i.e., filtered to only grid cells that overlap RCA grid)
glorys_rca_base_grid <- glorys_pred_grid %>% 
  filter(gridID_phy%in% unique(rca_base_grid$gridID_glorys_match)) %>% 
  dplyr::select(year,mth,gridID_phy,thetao,o2)
```

## Bathymetry

Add depth to the RCA layer.

```{r}
### Go get bathymetric data from NOAA to overlay on the samples
limits.for.map <- rca_pred_sf %>%
  st_transform(4326) %>% 
  st_bbox()+c(-1,-1,1,1) #add an extra degree on each side for buffer

xy <- rca_pred_sf %>% st_transform(4326) %>% st_coordinates()

b = getNOAA.bathy(lon1 = limits.for.map["xmin"],
          lon2 = limits.for.map[ "xmax" ],
          lat1 = limits.for.map["ymin"],
          lat2 = limits.for.map["ymax"],
          resolution = 1,keep = TRUE)

# We can pull depth from each sample point
stations.bathy <- get.depth(b,xy,locator=F) %>% 
  rename(bathy=depth)

rca_base_grid <- rca_base_grid %>% 
  mutate(bathy=stations.bathy$bathy)

# did this work?
tic("rasterizing bathy:")
rca_bathy <- rca_base_grid %>% dplyr::select(Easting_m,Northing_m,bathy)%>% st_as_sf(coords = c("Easting_m","Northing_m"),crs=26910)
testbathy <- st_rasterize(rca_bathy)
toc()

# write_stars(testbathy,dsn=here('gf sdms','data','test_bathy_raster.tif'))
library(terra)
br <- rast(testbathy)
plot(br)
```


```{r}
# Use the matching key above to build the prediction tibble for RCA

build_rca_grid_yr <- function(yr){
  g <- glorys_rca_base_grid %>% filter(year==yr)
  out <- rca_base_grid
}

```

