---
title: "Custom functions for use in species distribution modeling"
author: "Owen Liu"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup2, include=FALSE}
# devtools::install_github("pbs-assess/sdmTMB")
library(sdmTMB)
library(tidyverse)
library(lubridate)
library(sf)
library(stars)
library(terra)
library(here)
library(Hmisc)
library(visreg)
knitr::opts_chunk$set(echo = TRUE)
options(dplyr.summarise.inform=FALSE)
```

# Purpose

Write functions utilizing `sdmTMB` to fit and project models for west coast groundfish based on hindcast GLORYS oceanographic data.

*Note: All the data required for running the functions here have been produced in the `sdmTMB-data-construction-glorys-rcas.Rmd` script.

```{r, message=F,eval=F, echo=F, include=F}
rmarkdown::render(here::here('gf sdms','code','sdmTMB-data-construction-glorys-rcas.Rmd'),quiet=TRUE)
```

# Functions for Fitting

## Prepare Species' Data

This function selects a species' data from the trawl survey data, normalizes/scales the environmental data

```{r}
prepare_species <- function(dat,spp){
  dat_sub <- dat %>% 
    dplyr::filter(species==spp) %>% 
    
    # rescale depth, oxygen, and temp to be N(0,1)
    mutate(across(c(depth_trawl,thetao,o2),~(scale(.) %>% as.vector()),.names="{.col}_norm"))
  dat_sub
}
```

## sdmTMB Model Function

Write a function that runs sdmTMB to fit a single model. It will call the previous `prepare_species` function to make the appropriate species data. For now, the environmental variable names are not generic (always `thetao` and `o2` for fitting to the GLORYS data).

```{r}
run_sdmTMB <- function(dat,spp,use_depth=F,time_vary=F,spatial_field=T,env_spline=F,spline_k=3){
  # filter data for species
  modeldat <- prepare_species(dat,spp=spp)
  
  # make spde
  spde <- make_mesh(modeldat,xy_cols = c('lontrawl_km','lattrawl_km'), 
                   cutoff = 40)
  
  # model formula
  formula <- paste0("cpue_kg_km2 ~ ")
  
  # make the environmental effects
  enviro <- paste("thetao_norm + I(thetao_norm^2) + o2_norm + I(o2_norm^2)")
  # wiggly environmental relationships?
  enviro <- ifelse(env_spline, paste0("s(thetao_norm,k=",spline_k,") + ",
                                      "s(o2_norm,k=",spline_k,")"),
                   enviro)
  # if depth effect, add to model formla
  if(use_depth) {
    formula = paste0(formula, " + depth_trawl_norm + I(depth_trawl_norm^2)")
  }
  
  time_formula = "~ -1"
  if(time_vary) {
    time_formula = paste0(time_formula," + ", enviro)
    time_varying = as.formula(time_formula)
    time = "year"
  } else {
    formula = paste0(formula,"+", enviro)
    time_varying = NULL
    time = "year"
  }
  
  # fit model
  # set.seed(41389) # for reproducibility
  print('running model.')
  m <- try( sdmTMB(
    formula = as.formula(formula),
    time_varying = time_varying,
    mesh = spde,
    time = time,
    family = tweedie(link = "log"),
    data = modeldat,
    spatiotemporal = 'off',
    anisotropy = FALSE,
    spatial = spatial_field),
    #extra_time argument necessary for prediction?
    # extra_time=1980:2100),
  silent=F)

  if(class(m)=="try-error"){
    print(paste("Error."))
  }else{
    print(paste("Model for",spp,"complete."))
  }

  # return(m)
  return(m)

}
```

## Cross Validation Function

Similar to the function above, this function implements 2-fold cross-validation in order to return the CV log-likelihood for use in model stacking and model ensembles.

```{r}
run_sdmTMB_cv <- function(dat,spp,nknots=400,use_depth=F,time_vary=F,spatial_field=T,env_spline=F,spline_k=3,return_what='loglik'){
  # filter data for species
  modeldat <- prepare_species(dat,spp=spp)
  
  # make spde
  spde <- make_mesh(modeldat,xy_cols = c('lontrawl_km','lattrawl_km'), 
                   cutoff = 40)
  
  # model formula
  formula <- paste0("cpue_kg_km2 ~ ")
  
  # make the environmental effects
  enviro <- paste("thetao_norm + I(thetao_norm^2) + o2_norm + I(o2_norm^2)")
  # wiggly environmental relationships?
  enviro <- ifelse(env_spline, paste0("s(thetao_norm,k=",spline_k,") + ",
                                      "s(o2_norm,k=",spline_k,")"),
                   enviro)
  # if depth effect, add to model formla
  if(use_depth) {
    formula = paste0(formula, " + depth_trawl_norm + I(depth_trawl_norm^2)")
  }
  
  time_formula = "~ -1"
  if(time_vary) {
    time_formula = paste0(time_formula, " + ", enviro)
    time_varying = as.formula(time_formula)
    time = "year"
  } else {
    formula = paste0(formula, " + ", enviro)
    time_varying = NULL
    time = "year"
  }
  
  # fit model. EW commented out quadratic roots, since those are still experimental and won't work for all spp. Also turned
  set.seed(41389) # for reproducibility
  test_set = sample(1:nrow(modeldat), size = round(0.2*nrow(modeldat)), replace=FALSE)
  modeldat$fold = 1
  modeldat$fold[test_set] = 2 
  
  # print('running 2-fold CV.')
  
  m_cv <- try( sdmTMB_cv( 
    formula = as.formula(formula),
    k_folds=2,
    parallel = TRUE,
    fold_ids = modeldat$fold,
    time_varying = time_varying,
    spatiotemporal='off',
    mesh = spde,
    time = time,
    family = tweedie(link = "log"),
    data = modeldat,
    anisotropy = FALSE,
    spatial = spatial_field
  ),
  silent=T)
  if(class(m_cv)=='try-error'){
    # print(paste('Error.'))
    return(NA)
  } else{
    # tem <- m_cv %>% pluck('data')
    # print(paste('data is class',class(tem)))
    total_pred_ll = m_cv %>% 
      pluck('data') %>% 
      dplyr::filter(cv_fold==2) %>% 
      pluck('cv_loglik') %>% 
      sum()
    if(return_what=='model') return(m_cv)
    else return(total_pred_ll)
  }
}
```


## Multiple Model Comparisons

Finally, a function that runs a set of models with varying covariate structures, and returns their cross-validation log-likelihood for use in model selection

```{r}
model_species <- function(spp,data){

    models_to_run <-crossing(spp,spatial_field=c(F,T),env_spline=c(F,T),use_depth=c(F,T)) %>%
      mutate(model_num=row_number())
    
    out <- models_to_run %>% 
      # mutate(model=purrr::pmap(list(spp=spp,spatial_field=spatial_field,env_spline=env_spline,include_substrate=include_substrate),run_sdmTMB,dat=data)) %>%
      mutate(model_ll=purrr::pmap_dbl(list(spp=spp,spatial_field=spatial_field,env_spline=env_spline,use_depth=use_depth),run_sdmTMB_cv,dat=data,return_what="log_lik"))
    
    out
    
    best <- out %>%
      filter(model_ll==max(model_ll,na.rm=T)) %>% 
      slice(1L)

    best <- run_sdmTMB(dat = data,spp=spp,spatial_field=best$spatial_field,env_spline=best$env_spline,use_depth=best$use_depth)
    
    return(list(cv_ll=out,best_model=best))
      
}
```


# Model Fit Statistics and Visualization

Functions to visualize and save model fits.


## Model Table

Report the results of running a suite of models for each species (`model_species` above)

```{r}
# report_model_table <- function(model_df){
#   model_table <- model_df %>% dplyr::select(-model,-model_cv,-include_substrate,-model_num)
#   convergence <- purrr::map_int(model_df$model,function(m){m$model$convergence})
#   model_table$Convergence <- convergence
#   range_params <- purrr::map_dbl(model_df$model,function(m){
#     tidy(m,effects='ran_pars') %>% slice(1) %>% pull(estimate)
#   })
#   model_table$sumloglik <- purrr::map_dbl(model_df$model_cv,pluck("sum_loglik"))
#   model_table$Matern_range <- range_params
#   model_table
# }
```

## Pred/Obs

```{r}
make_pred_obs_plot <- function(m){
  sppdat <- predict(m)%>% mutate(logcpue=log(cpue_kg_km2))
  spp <- tools::toTitleCase(unique(sppdat$species))
  po <- ggplot(sppdat,aes(est,logcpue))+
    geom_point()+
    geom_smooth(se=F)+
    labs(x="Predicted Log CPUE",y="Observed Log CPUE")+
    coord_equal()+
    scale_x_continuous(limits=c(-5,NA))+
    theme_minimal()+
    labs(title=paste0("Predictions vs. Observations:\n",spp))+
    theme(panel.background = element_rect(color='black'))
  # maybe a presence-absence distribution of observations?
  po2 <- sppdat %>% 
    mutate(obs_zero=ifelse(cpue_kg_km2==0,"Zero","Non-Zero")) %>% 
    ggplot(aes(est,fill=factor(obs_zero)))+
    geom_density(alpha=0.7)+
    scale_x_continuous(limits=c(-10,NA))+
    theme_minimal()+
    labs(title="Distribution of Estimates for \nZero vs. Non-zero Observations",fill="Observed",x="Log CPUE")+
    theme(panel.background = element_rect(color='black'))
  cowplot::plot_grid(po,po2,nrow=1)
}
```


## Normal QQ plot

```{r}
make_qq_plot <- function(m){
  sppdat <- predict(m)
  resd <- residuals(m)
  spp <- tools::toTitleCase(unique(sppdat$species))
  resids <- sppdat %>% mutate(resid=resd)
  qq <- ggplot(resids,aes(sample=resid))+stat_qq()+stat_qq_line()+
    labs(x="Expected",y="Observed")+coord_equal()+
    theme_minimal()+
    theme(panel.background = element_rect(color='black'))
  qq
}
```

## Spatial Residuals

```{r}
spatial_residuals_plot <- function(m){
  sppdat <- predict(m)
  resd <- residuals(m)
  
  spp <- tools::toTitleCase(unique(sppdat$species))
  
  # coast sections to zoom better
  sppdat <- sppdat %>% 
    mutate(section=cut(lattrawlUTM,4))%>% 
    mutate(resids=resd,dev=abs(resd)) %>% 
    mutate(posneg=ifelse(resids>0,"Positive","Negative"))
  
  ggplot(sppdat, aes(lontrawlUTM/1000, lattrawlUTM/1000, size = dev,shape=factor(posneg),col=factor(posneg))) +
    # scale_colour_gradient2() +
    scale_color_manual(values=c("gray50","red"))+
    scale_shape_manual(values=c(6,4))+
    scale_size_continuous(range=c(0.1,10),trans='exp')+
    geom_point() +
    facet_wrap(~year,nrow=2)+
    guides(shape="none")+
    # facet_grid(section~year,scales='free_y') +
    coord_equal()+
    labs(x="lon",y="lat",color="Residual",title=paste0("Spatiotemporal Residuals:\n",spp))+
    theme(panel.border = element_rect(fill=NA,color='black'),
          panel.grid=element_blank(),panel.grid.major=element_blank(),
          panel.background = element_rect(fill='gray90'))
}
```



# Functions for Prediction

## Single Model Prediction

Functions to make generic predictions for one model on to a new, projected grid (e.g., the high-resolution RCA grid, or the lower-resolution but broader-scale GLORYS grid). The covariate data we use to build the projction grids uses environmental data from the "midpoint" of the trawl survey season for each year (i.e., August GLORYS conditions)

```{r}
# give the function a model object from sdmTMB
make_predictions <- function(modelobj,nd){

  original_model_data <- modelobj$data
  # need to use the original (hindcast) environmental data to appropriately scale the new data
  mean_t <- mean(original_model_data$thetao,na.rm=T)
  sd_t <- sd(original_model_data$thetao,na.rm=T)
  mean_oxy <- mean(original_model_data$o2,na.rm=T)
  sd_oxy <- sd(original_model_data$o2,na.rm=T)
  mean_depth <- mean(original_model_data$depth_trawl,na.rm=T)
  sd_depth <- sd(original_model_data$depth_trawl,na.rm=T)
  
  newdata <- nd %>% 
    mutate(thetao_norm=(thetao-mean_t)/sd_t) %>% 
    mutate(o2_norm=(o2-mean_oxy)/sd_oxy) %>% 
    mutate(depth_trawl_norm=(depth_trawl-mean_depth)/sd_depth) 

  # now we can make the predictions
  predicted_cpue_km2 <- predict(modelobj,newdata,return_tmb_object=F)
  
  # add the species name
  spp <- unique(original_model_data$species)
  predicted_cpue_km2 %>% mutate(species=spp)
}
```

## Maps

Using the output of the `make_predictions` function, make maps. These maps will project predictions into a raster format. As default inputs, these functions use the predictions from the above function, as well as a template raster (produced previously), and a tabular matching key to match predictions to grid cells.

```{r}
make_map_rca <- function(rca_preds,r=rca_proj_rast,rastkey=rca_rast_key){
  
  df <- rca_preds %>%
    dplyr::select(Grid_ID,est)%>%
    left_join(rastkey,by=join_by(Grid_ID))
  
  # fill the template raster with predicted values
  outrast <- setValues(r,NA)
  outrast[df$rca_rastID] <- df$est
  
  # max for plotting scale
  maxval <- max(values(outrast),na.rm=T)
  
  spp <- tools::toTitleCase(unique(rca_preds$species))
  
  plot(outrast,col=viridis_pal()(50),range=c(-5,round(maxval)),colNA='gray80',
       main=paste0("RCA Predictions: \n",spp),cex.main=0.5)
  return(outrast)
}

make_map_glorys <- function(glorys_preds,r=glorys_proj_rast,rastkey=glorys_rast_key){
  
  df <- glorys_preds %>%
    dplyr::select(gridID_phy,est)%>%
    left_join(rastkey,by = join_by(gridID_phy)) %>% 
    filter(!is.na(glorys_rastID))
  
  # fill the template raster with predicted values
  outrast <- setValues(r,NA)
  outrast[df$glorys_rastID] <- df$est
  
  # max for plotting scale
  maxval <- max(values(outrast),na.rm=T)
  
  spp <- tools::toTitleCase(unique(glorys_preds$species))
  
  plot(outrast,col=viridis_pal()(50),range=c(-5,round(maxval)),colNA='gray80',
       main=paste0("GLORYS Predictions:  \n",spp),cex.main=0.5)
  return(outrast)
}
```

